---
title: "Manuscript Plots"
output: html_document
date: "2023-03-09"
---



# ---------------------------------------
# Setup
## Loading Packages
```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstan)
library(hBayesDM)
library(bayesplot)
library(foreach)
library(tidybayes)
library(patchwork)
library(abind)
library(zoo)
library(here)
library(ggpubr)
library(egg)
library(grid)
library(tidyverse)
library(lemon)
library(ggpp)
library(stringi)
library(ggh4x)
library(hBayesDM)
```


## Path
```{r}
GSU_path = "C:/Users/jmh31/OneDrive/Application & Professional Materials/Jobs/(interview) 2024 - Georgia Southern/"
```


# -------------------------------------------
# Bandit Example
## Load & Process Data
```{r}
# LOAD DATA
stan_data = readRDS(here("1_TADS_Parents_PP", "Data", "1_Stan",
                         "design_T1_parent_Anx_Dep_SUD_Female_IGT.RDS"))

# OBSERVED DATA
deck_B = stan_data$choice[stan_data$X[,5,] == 0, stan_data$card[1,,1] == 2, 1]
deck_B = ifelse(deck_B == 1, 1, 0)
deck_D = stan_data$choice[stan_data$X[,5,] == 0, stan_data$card[1,,1] == 4, 1]
deck_D = ifelse(deck_D == 1, 1, 0)
observed_data = data.frame(ID = 1:77,
                           prob_B = apply(deck_B, 1, mean),
                           prob_D = apply(deck_D, 1, mean)) %>% 
  reframe(M.prob_B = mean(prob_B),
          M.prob_D = mean(prob_D),
          SD.prob_B = sd(prob_B),
          SD.prob_D = sd(prob_D)) %>% 
  pivot_longer(everything(), names_to = c("metric", "deck"), names_sep = "\\.",
               values_to = "value") %>% 
  pivot_wider(names_from = "metric", values_from = "value")

# -------------------------------------------
# PREP DATA
victoria_PPCs = 
  readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
               "Covariate_Joint_ORL_Bias",
               paste("T1_parent_Anx_Dep_SUD_Female", "Covariate_Joint_ORL_Bias", "Male_PPCs.rds", sep = "_"))) %>%
  filter(deck == "B" | deck == "D") %>% 
  mutate(deck = case_when(deck == "B" ~ "Option 1", T ~ "Option 2")) %>% 
  group_by(deck) %>% 
  mutate(overall_mu = mean(observed)) %>% 
  group_by(trial, deck, overall_mu) %>% 
  
  # FULL DATA
  reframe(observed = mean(observed), mu = mean(mu),
          lower50 = mean(lower50), upper50 = mean(upper50),
          lower95 = mean(lower95), upper95 = mean(upper95))
  
  # SUBSET CHOICE DATA
  # reframe(observed = mean(observed), mu = NA_real_,
  #         lower50 = NA_real_, upper50 = NA_real_,
  #         lower95 = NA_real_, upper95 = NA_real_)

  # SUBSET everything DATA
  # reframe(observed = NA_real_, mu = NA_real_,
  #         lower50 = NA_real_, upper50 = NA_real_,
  #         lower95 = NA_real_, upper95 = NA_real_)
```


## Bar Plot
```{r}
tiff(paste0(GSU_path, "Plots/Bar_Plot.tiff"),
     width = 8, height = 5.75, units = "in", res = 300)
  # PPC PLOTS
  observed_data %>% 
    ggplot(aes(x = deck, fill = deck, color = deck)) +
      # geoms
      geom_bar(aes(y = M), stat = "identity", color = "black", linewidth = 1.5) +
      # geom_errorbar(aes(ymin = M-SD, ymax = M+SD), color = "black", linewidth = 1.5, width = .75) +
      # geom_linerange(aes(ymin = M-SD, ymax = M+SD), color = "black", linewidth = 1.5) +
      # scales
      scale_x_discrete(labels = c("Option 1", "Option 2")) +
      scale_y_continuous(limits = c(0,1), expand = c(0, 0),
                         breaks = seq(0,1,.25)) +
      scale_color_manual(values = c("#E69F00", "#0070C0"), labels = c("Option 1", "Option 2")) +
      scale_fill_manual(values = c("#E69F00", "#0070C0"), labels = c("Option 1", "Option 2")) +
      # theme
      labs(y = "Proportion Play") +
      theme_classic() +
      theme(#axis elements
            axis.line = element_line(size = 1.5),
            axis.ticks.length = unit(.1, "in"),
            axis.ticks = element_line(size = 1.5, color = "black", length),
            axis.text = element_text(size = 24, color = "black"),
            axis.title.y = element_text(size = 28),
            axis.title.x = element_blank(),
            # legend elements
            legend.background = element_rect(fill = "transparent", colour = "transparent",
                                             color = "transparent"),
            legend.position = "none",
            # plot elements
            plot.margin = margin(t = .25, r = .3, unit = 'in'))
dev.off()
```


## Trial-Level Plot
```{r}
tiff(paste0(GSU_path, "Plots/Trial_Level_Plot.tiff"),
     width = 8, height = 5.75, units = "in", res = 300)
  # PPC PLOTS
  victoria_PPCs %>% 
    ggplot(aes(x = trial)) +
      # geoms
      geom_ribbon(aes(ymin = lower95, ymax = upper95, fill = deck),
                 # show.legend = F,
                  color = "transparent", alpha = .25) +
      geom_ribbon(aes(ymin = lower50, ymax = upper50, fill = deck),
                 # show.legend = F,
                  color = "transparent", alpha = .5) +
      geom_line(aes(y = mu, color = deck), linewidth = 1.5) +
      geom_point(aes(y = observed, fill = deck), color = "black",
                 show.legend = F,
                 shape = 21, stroke = 1.75, size = 3) +
      # geom_hline(aes(yintercept = overall_mu, color = deck), linewidth = 1.5) +
      # scales
      scale_y_continuous(limits = c(.48,1.02),
                         breaks = seq(0,1,.25)) +
      scale_color_manual(values = c("#E69F00", "#0070C0")) +
      scale_fill_manual(values = c("#E69F00", "#0070C0")) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(#axis elements
            axis.line = element_line(size = 1.5),
            axis.ticks.length = unit(.1, "in"),
            axis.ticks = element_line(size = 1.5, color = "black", length),
            axis.text = element_text(size = 24, color = "black"),
            axis.title = element_text(size = 28),
            # legend elements
            legend.background = element_rect(fill = "transparent", colour = "transparent",
                                             color = "transparent"),
            legend.direction = "horizontal",
            legend.position = c(.35, .95),
            legend.title = element_blank(),
            legend.key.size = unit(.5, "in"),
            legend.key.spacing.y = unit(.25, "in"),
            legend.text = element_text(size = 24),
            # plot elements
            plot.margin = margin(t = .25, r = .3, unit = 'in'))
dev.off()
```


# -------------------------------------------
# Study 1
## Load Data
```{r include=FALSE}
orl_posteriors = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL_Bias",
                              "Joint_ORL_Bias_posteriors.rds"))
```


## Functions
```{r}
# MAKE A FANCY LABEL FOR PLOTS
estimate_CI_label = function(estimate, lower, upper){
  
  estimate = round(estimate,2)
  estimate_lab = paste(ifelse(sign(estimate)==1," ","-"), stri_pad_right(str_remove(abs(estimate), "^0+"),
                                                           width = 3, pad = "0"),sep="")
  lower = round(as.numeric(str_remove(lower, "\\(")),2)
  upper = round(as.numeric(str_remove(upper, "\\)")),2)
  
  lower_lab = paste(ifelse(sign(lower)==1,"","-"), stri_pad_right(str_remove(abs(lower), "^0+"),
                                                                  width = 3, pad = "0"),sep="")
  
  upper_lab = paste(ifelse(sign(upper)==1,"","-"), stri_pad_right(str_remove(abs(upper), "^0+"),
                                                                  width = 3, pad = "0"),sep="")
  estimate_CI = paste("=",estimate_lab," [",lower_lab,",",upper_lab,"]",sep="")
  
  return(estimate_CI)
}
```


## Absolute Reliability
```{r}
group_data =
  data.frame(session = c(1, 2),
             Arew_mu = apply(orl_posteriors$mu_Arew, 2, mean),
             Apun_mu = apply(orl_posteriors$mu_Apun, 2, mean),
             betaF_mu = apply(orl_posteriors$mu_betaF, 2, mean),
             betaB_mu = apply(orl_posteriors$mu_betaB, 2, mean),
             CI_Arew = t(apply(orl_posteriors$mu_Arew, 2, HDIofMCMC)),
             CI_Apun = t(apply(orl_posteriors$mu_Apun, 2, HDIofMCMC)),
             CI_betaF = t(apply(orl_posteriors$mu_betaF, 2, HDIofMCMC)),
             CI_betaB = t(apply(orl_posteriors$mu_betaB, 2, HDIofMCMC))) %>% 
  pivot_longer(ends_with(c(".1", ".2")), names_to = "limit", values_to = "CI") %>% 
  mutate(limit = str_remove(limit, "CI_"),
         limit = str_replace(limit, ".1", "_lower"),
         limit = str_replace(limit, ".2", "_upper")) %>% 
  pivot_wider(names_from = "limit", values_from = "CI") %>% 
  pivot_longer(ends_with(c("mu", "lower", "upper")), 
               names_to = "parameter", values_to = "estimate") %>% 
  separate(col = "parameter", into = c("parameter", "type")) %>% 
  pivot_wider(names_from = "type", values_from = "estimate") %>% 
  mutate(session = factor(session),
         parameter = factor(parameter, ordered = T,
                            levels = c("Arew", "Apun", "betaF", "betaB")))


tiff(paste0(GSU_path, "Plots/Study 1 - ORL Absolute Reliability.tiff"),
     width = 8.5, height = 7.5, units = "in", res = 300)

  data.frame(participant = 1:49,
             Arew  = apply(orl_posteriors$Arew, c(2,3), mean),
             Apun  = apply(orl_posteriors$Apun, c(2,3), mean),
             betaF = apply(orl_posteriors$betaF, c(2,3), mean),
             betaB = apply(orl_posteriors$betaB, c(2,3), mean)) %>% 
    pivot_longer(starts_with(c("Arew", "Apun", "betaF", "betaB")), values_to = "estimate", 
                 names_to = c("parameter", "session"), names_sep = "\\.") %>% 
    mutate(session = factor(session),
           parameter = factor(parameter, ordered = T,
                              levels = c("Arew", "Apun", "betaF", "betaB"))) %>% 
  # plot
  ggplot(aes(x = session, y = estimate, fill = session)) +
    # geoms
    # geom_crossbar(data = group_data, aes(y = mu, ymin = mu, ymax = mu), linewidth = .5, fatten = 0) +
    geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1.25, stroke = 2,
                 position = position_dodge(width = .8)) +
    geom_pointrange(data = group_data, aes(y = mu, ymin = lower, ymax = upper),
                    color = "red", size = 1, linewidth = 1.5,
                    position = position_dodge(width = .8)) +
    # scales
    # scale_y_continuous(limits = c(0, 1), expand = c(.01, .01), breaks = seq(0, 1, .25)) +
    scale_fill_manual(values = c("gray25", "gray75"),
                      labels = c("Session 1", "Session 2")) +
    # themes
    labs(x = "Session", y = "Estimate") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text = element_text(color = "black", size = 24),
          axis.ticks = element_line(linewidth = 1.25, color = "black"),
          axis.line = element_line(linewidth = 1.25),
          axis.ticks.length = unit(.1, "in"),
          axis.title = element_text(size = 36),
          strip.text = element_blank(),
          panel.spacing.x = unit(.25, "in"),
          panel.spacing.y = unit(.25, "in"),
          plot.margin = unit(c(.25,.25,.25,.25), "in"),
          legend.position = "none") +
    facet_rep_wrap(.~parameter, scales = "free")

dev.off()
```



## Relative Reliability
```{r}
tiff(paste0(GSU_path, "Plots/Study 1 - ORL Relative Reliability.tiff"),
     width = 7.5, height = 7.5, units = "in", res = 300)

  data.frame(participant = 1:49,
             Arew  = apply(orl_posteriors$Arew, c(2,3), mean),
             Apun  = apply(orl_posteriors$Apun, c(2,3), mean),
             betaF = apply(orl_posteriors$betaF, c(2,3), mean),
             betaB = apply(orl_posteriors$betaB, c(2,3), mean)) %>% 
    pivot_longer(starts_with(c("Arew", "Apun", "betaF", "betaB")), values_to = "estimate", 
                 names_to = c("parameter", "session"), names_sep = "\\.") %>% 
    pivot_wider(values_from = "estimate", 
                names_from = "session", names_prefix = "session_") %>% 
  group_by(parameter) %>% 
  mutate(session_1 = (session_1 - mean(session_1)) / sd(session_1),
         session_2 = (session_2 - mean(session_2)) / sd(session_2),
         parameter = factor(parameter, ordered = T,
                            levels = c("Arew", "Apun", "betaF", "betaB"))) %>% 
    ggplot(aes(x = session_1, y = session_2)) +
      # geoms
      geom_point(size = 3, shape = 21, color = "black", fill = "gray50") +
      geom_smooth(method = "lm", formula = "y ~ x", color = "black", se = F, linewidth = 1.5,
                  fullrange = T) +
      # scales
      scale_x_continuous(n.breaks = 3) +
      scale_y_continuous(n.breaks = 3) +
      # themes
      labs(x = "Session 1", y = "Session 2") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text = element_text(color = "black", size = 24),
            axis.title = element_text(size = 36),
            axis.ticks = element_line(linewidth = 1.25, color = "black"),
            axis.line = element_line(linewidth = 1.25),
            axis.ticks.length = unit(.1, "in"),
            # strip.text = element_blank(),
            panel.spacing = unit(.35, units = "in"),
            plot.margin = unit(c(-2, .25, -2, .1), "in"),
            aspect.ratio = 1) +
      facet_rep_wrap(.~parameter, scales = "free")

dev.off()
```



# -------------------------------------------
# Study 2
## Load Data
```{r}
groups = c("Female", "Anx", "Dep", "SUD")
model_name = "Covariate_Joint_ORL_Bias"
sample = "T1_parent_Anx_Dep_SUD_Female"

# read in posteriors
orl_posteriors = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                              model_name,
                              paste(sample, model_name, "posteriors.rds", sep = "_")))

```


## Calculate Diag Differences
```{r}
orl_diag_parameters = data.frame(
  iteration = 1:16000,
  # get non-diag posteriors by averaging across men/women posteriors
  Arew_mu.0 = (orl_posteriors$mu_Arew[,,1] + orl_posteriors$mu_Arew[,,5])/2,
  Apun_mu.0 = (orl_posteriors$mu_Apun[,,1] + orl_posteriors$mu_Apun[,,5])/2,
  betaF_mu.0 = (orl_posteriors$mu_betaF[,,1] + orl_posteriors$mu_betaF[,,5])/2,
  betaB_mu.0 = (orl_posteriors$mu_betaB[,,1] + orl_posteriors$mu_betaB[,,5])/2,
  Arew_mu = orl_posteriors$mu_Arew[,,2:4],
  Apun_mu = orl_posteriors$mu_Apun[,,2:4],
  betaF_mu = orl_posteriors$mu_betaF[,,2:4],
  betaB_mu = orl_posteriors$mu_betaB[,,2:4],
  # get betas for diagnostic variables
  Arew_beta = orl_posteriors$beta_Arew[,2:4],
  Apun_beta = orl_posteriors$beta_Apun[,2:4],
  betaF_beta = orl_posteriors$beta_betaF[,2:4],
  betaB_beta = orl_posteriors$beta_betaB[,2:4]) %>% 
  pivot_longer(starts_with(c("Arew", "Apun", "betaF", "betaB")),
               names_to = c("orl_par", "group"),
               values_to = "estimate", names_sep = "\\.") %>% 
  mutate(grp_parameter = case_when(str_detect(orl_par, "mu") ~ "mu",
                                   str_detect(orl_par, "_beta") ~ "beta"),
         orl_parameter = str_remove(orl_par, "_mu|_beta")) %>% 
  select(-orl_par) %>% 
  mutate(group = case_when(group == 0 & grp_parameter == "mu" ~ "Con",
                           group == 1 & grp_parameter == "mu" ~ "Anx",
                           group == 2 & grp_parameter == "mu" ~ "Dep",
                           group == 3 & grp_parameter == "mu" ~ "SUD",
                           group == 1 & grp_parameter == "beta" ~ "Anx",
                           group == 2 & grp_parameter == "beta" ~ "Dep",
                           group == 3 & grp_parameter == "beta" ~ "SUD"),
         orl_parameter = factor(orl_parameter, ordered = T,
                                levels = c("Arew", "Apun", "betaF", "betaB")),
         grp_parameter = factor(grp_parameter, levels = c("mu", "beta"), ordered = T,
                         labels = c("Mu", "Beta")),
         group = factor(group, levels = c("Con", "Anx", "Dep", "SUD"),
                        ordered = T)) %>% 
  group_by(group, grp_parameter, orl_parameter) %>% 
  summarise(mu = mean(estimate),
            lower = HDIofMCMC(estimate)[1],
            upper = HDIofMCMC(estimate)[2]) %>% 
  filter(grp_parameter != "Beta")
```



## Plot Diag Differences
```{r}
tiff(paste0(GSU_path, "Plots/Study 2 - Diag Differences.tiff"),
     width = 11, height = 7.5, units = "in", res = 300)

  orl_diag_parameters %>% 
    mutate(group = factor(group, ordered = T,
                          levels = c("Con", "Anx", "Dep", "SUD"),
                          labels = c("HC", "Anx", "Dep", "SUD"))) %>% 
  # plot
  ggplot(aes(x = group, y = mu, fill = group)) +
    # geoms
    geom_bar(stat = "identity", color = "black", linewidth = 1.25) +
    geom_errorbar(aes(ymin = lower, ymax = upper), linewidth = 1.25, width = .75) +
    # scales
    scale_y_continuous(limits = c(0, NA), n.breaks = 4,
                       expand = expansion(mult = c(0, 0.1))) +
    scale_fill_manual(values = c("gray75", "#1E88E5", "#FFC107", "#D81B60")) +
    # themes
    labs(y = "Estimate") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text = element_text(color = "black", size = 24),
          axis.ticks = element_line(linewidth = 1.25, color = "black"),
          axis.line = element_line(linewidth = 1.25),
          axis.ticks.length = unit(.1, "in"),
          axis.title.x = element_blank(),
          axis.title.y = element_text(size = 36),
          strip.text = element_blank(),
          panel.spacing.x = unit(.25, "in"),
          panel.spacing.y = unit(.75, "in"),
          plot.margin = unit(c(.25,.25,.25,.25), "in"),
          legend.position = "none") +
    facet_rep_wrap(.~orl_parameter, scales = "free")

dev.off()
```



## Calculate Sex Differences
```{r}
orl_sex_parameters = data.frame(
  iteration = 1:16000,
  Arew_mu_male = orl_posteriors$mu_Arew[,,1],
  Apun_mu_male = orl_posteriors$mu_Apun[,,1],
  betaF_mu_male = orl_posteriors$mu_betaF[,,1],
  betaB_mu_male = orl_posteriors$mu_betaB[,,1],
  Arew_mu_female = orl_posteriors$mu_Arew[,,5],
  Apun_mu_female = orl_posteriors$mu_Apun[,,5],
  betaF_mu_female = orl_posteriors$mu_betaF[,,5],
  betaB_mu_female = orl_posteriors$mu_betaB[,,5],
  # get betas for diagnostic variables
  Arew_beta_female = orl_posteriors$beta_Arew[,5],
  Apun_beta_female = orl_posteriors$beta_Apun[,5],
  betaF_beta_female = orl_posteriors$beta_betaF[,5],
  betaB_beta_female = orl_posteriors$beta_betaB[,5]) %>% 
  pivot_longer(starts_with(c("Arew", "Apun", "betaF", "betaB")),
               names_to = c("orl_parameter", "grp_parameter", "sex"),
               values_to = "estimate", names_sep = "_") %>% 
  mutate(orl_parameter = factor(orl_parameter, ordered = T,
                                levels = c("Arew", "Apun", "betaF", "betaB")),
         grp_parameter = factor(grp_parameter, levels = c("mu", "beta"), ordered = T,
                                labels = c("Mu", "Beta")),
         sex = factor(sex, levels = c("male", "female"), labels = c("Men", "Women"),
                      ordered = T)) %>% 
  group_by(sex, grp_parameter, orl_parameter) %>% 
  summarise(mu = mean(estimate),
            lower = HDIofMCMC(estimate)[1],
            upper = HDIofMCMC(estimate)[2]) %>% 
  filter(grp_parameter != "Beta")
```



## Plot Sex Differences
```{r}
tiff(paste0(GSU_path, "Plots/Study 2 - Sex Differences.tiff"),
     width = 8, height = 7.5, units = "in", res = 300)

  orl_sex_parameters %>% 
  # plot
  ggplot(aes(x = sex, y = mu, fill = sex)) +
    # geoms
    geom_bar(stat = "identity", color = "black", linewidth = 1.25) +
    geom_errorbar(aes(ymin = lower, ymax = upper), linewidth = 1.25, width = .75) +
    # scales
    scale_y_continuous(limits = c(0, NA), n.breaks = 4,
                       expand = expansion(mult = c(0, 0.1))) +
    scale_fill_manual(values = c("gray75", "gray25")) +
    # themes
    labs(y = "Estimate") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text = element_text(color = "black", size = 24),
          axis.ticks = element_line(linewidth = 1.25, color = "black"),
          axis.line = element_line(linewidth = 1.25),
          axis.ticks.length = unit(.1, "in"),
          axis.title.x = element_blank(),
          axis.title.y = element_text(size = 36),
          strip.text = element_blank(),
          panel.spacing.x = unit(.25, "in"),
          panel.spacing.y = unit(.75, "in"),
          plot.margin = unit(c(.25,.25,.25,.25), "in"),
          legend.position = "none") +
    facet_rep_wrap(.~orl_parameter, scales = "free")

dev.off()
```



# -------------------------------------------
# Study 3
## Import Models
```{r}
conditions  = c("neg.beta_neg.cor", "neg.beta_neu.cor", "neg.beta_pos.cor",
                "neu.beta_neg.cor", "neu.beta_neu.cor", "neu.beta_pos.cor",
                "pos.beta_neg.cor", "pos.beta_neu.cor", "pos.beta_pos.cor")
conditions_labs = c("-.3 Beta & -.3 r", "-.3 Beta & 0 r", "-.3 Beta & +.3 r",
                    "0 Beta & -.3 r", "0 Beta & 0 r", "0 Beta & +.3 r",
                    "+.3 Beta & -.3 r", "+.3 Beta & 0 r", "+.3 Beta & +.3 r")
sim_numbers = 1:100

characteristics = data.frame()
diagnostics     = data.frame()
simulations     = data.frame()

for(condition in conditions){
  for(sim in sim_numbers){
    characteristics = bind_rows(characteristics,
                                readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                             paste0("RL_Characteristics_", sim, ".RDS"))),
                                readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                             paste0("HLCM_Characteristics_", sim, ".RDS"))))
    diagnostics = bind_rows(diagnostics,
                            readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                         paste0("RL_Diagnostics_", sim, ".RDS"))),
                            readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                         paste0("HLCM_Diagnostics_", sim, ".RDS")))) %>% 
      filter(!str_detect(parameter, "RL1|RL2|RL3"))
    simulations = bind_rows(simulations,
                            readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                         paste0("RL_Simulation_", sim, ".RDS"))),
                            readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                         paste0("HLCM_Simulation_", sim, ".RDS")))) %>% 
      filter(!str_detect(parameter, "RL1|RL2|RL3"))
  }
}
```



## Proportion in HDI 1 Condition
```{r}
tiff(paste0(GSU_path, "Plots/Study 3 - Growth Percent in HDIs (1 Condition).tiff"),
     width = 7, height = 5.25, units = "in", res = 300)

  simulations %>% 
    filter(parameter_type != "group") %>%
    group_by(condition, parameter, hypermodel) %>% 
    summarise(true_in_HDI95 = mean(true_in_HDI95)*100) %>% 
    filter(parameter %in% c("A", "slope", "intercept") & condition == "pos.beta_neg.cor") %>% 
    mutate(hypermodel = factor(hypermodel, levels = c("RL", "HLCM"),
                               labels = c("Two-Stage", "HLCM"), ordered = T),
           parameter = factor(parameter, ordered = T,
                              levels = c("intercept", "slope", "A"),
                              labels = c("Intercept", "Slope", "Learning\nRate")),
           condition = factor(condition, ordered = T,
                              levels = c("LoB_LoR", "HiB_LoR", "LoB_HiR", "HiB_HiR"),
                              labels = c("Low Slope\nLow Cor", "Mod Slope\nLow Cor",
                                         "Low Slope\nMod Cor", "Mod Slope\nMod Cor"))) %>% 
    ggplot(aes(x = parameter, y = true_in_HDI95, fill = hypermodel, group = hypermodel)) +
      # GEOMS
      geom_bar(color = "black", linewidth = 1, stat = "identity",
               position = position_dodge(width = .75), width = .75) +
      geom_text(aes(label = paste0(round(true_in_HDI95), "%")),
                vjust = .5, hjust = -.125, size = 8, angle = 90,
                position = position_dodge(width = .8)) +
      # SCALES
      scale_y_continuous(limits = c(0,100), expand = c(0,0), 
                         breaks = seq(0, 100, 25), labels = c("0%", "25%", "50%", "75%", "100%")) +
      scale_fill_manual(values = c("goldenrod3", "dodgerblue3")) +
      # THEMES
      # labs(y = "Parameters\nRecovered") +
      labs(y = "Coverage") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black", size = 24),
            axis.text.y = element_text(color = "black", size = 24),
            axis.ticks = element_line(linewidth = 1.25, color = "black"),
            axis.line = element_line(linewidth = 1.25),
            axis.ticks.length = unit(.1, "in"),
            axis.title.x = element_blank(),
            axis.title.y = element_text(size = 30),
            strip.text = element_blank(),
            panel.spacing.x = unit(.25, "in"),
            panel.spacing.y = unit(.75, "in"),
            plot.margin = unit(c(1.5,.25,.25,.25), "in"),
            legend.title = element_blank(),
            legend.key.size = unit(1.5, "cm"),
            legend.text = element_text(size = 20),
            legend.position = c(.5, 1.4),
            legend.direction = "horizontal") +
      facet_rep_grid(condition~., scales = "free")

dev.off()
```



## Proportion in HDI All Conditions
```{r}
tiff(paste0(GSU_path, "Plots/Study 3 - Growth Percent in HDIs (All Conditions).tiff"),
     width = 9, height = 9, units = "in", res = 300)

  simulations %>% 
    filter(parameter_type != "group" & parameter %in% c("A", "slope", "intercept")) %>% 
    group_by(condition, parameter, hypermodel) %>% 
    summarise(true_in_HDI95 = mean(true_in_HDI95)*100) %>%
    mutate(hypermodel = factor(hypermodel, levels = c("RL", "HLCM"),
                               labels = c("Two-Stage", "HLCM"), ordered = T),
           parameter = factor(parameter, ordered = T,
                              levels = c("intercept", "slope", "A"),
                              labels = c("Intercept", "Slope", "Learning\nRate")),
           gamma10 = factor(condition, levels = c("neg.beta_neg.cor", "neg.beta_neu.cor", "neg.beta_pos.cor",
                                                  "neu.beta_neg.cor", "neu.beta_neu.cor", "neu.beta_pos.cor",
                                                  "pos.beta_neg.cor", "pos.beta_neu.cor", "pos.beta_pos.cor"),
                            labels = c(expression("\u03B3"["10"]*"=-.3"), expression("\u03B3"["10"]*"=-.3"), expression("\u03B3"["10"]*"=-.3"),
                                       expression("\u03B3"["10"]*"=0"), expression("\u03B3"["10"]*"=0"), expression("\u03B3"["10"]*"=0"),
                                       expression("\u03B3"["10"]*"=+.3"), expression("\u03B3"["10"]*"=+.3"), expression("\u03B3"["10"]*"=+.3"))),
           rho = factor(condition, levels = c("neg.beta_neg.cor", "neg.beta_neu.cor", "neg.beta_pos.cor",
                                              "neu.beta_neg.cor", "neu.beta_neu.cor", "neu.beta_pos.cor",
                                              "pos.beta_neg.cor", "pos.beta_neu.cor", "pos.beta_pos.cor"),
                        labels = c(expression("\u03c1"*"=-.3"), expression("\u03c1"*"=0"), expression("\u03c1"*"=+.3"),
                                   expression("\u03c1"*"=-.3"), expression("\u03c1"*"=0"), expression("\u03c1"*"=+.3"),
                                   expression("\u03c1"*"=-.3"), expression("\u03c1"*"=0"), expression("\u03c1"*"=+.3")))
                              ) %>% 
    ggplot(aes(x = parameter, y = true_in_HDI95, fill = hypermodel)) +
      # GEOMS
      geom_bar(color = "black", linewidth = .75, stat = "identity", position = position_dodge(width = .85),
               width = .75) +
      geom_text(aes(label = paste0(round(true_in_HDI95), "%")),
                vjust = .5, hjust = -.125, size = 4.5, angle = 90, position = position_dodge(width = .85)) +
      # SCALES
      scale_y_continuous(limits = c(0,100), expand = c(0,0), 
                         breaks = seq(0, 100, 25), labels = c("0%", "25%", "50%", "75%", "100%")) +
      scale_fill_manual(values = c("goldenrod3", "dodgerblue3")) +
      # THEMES
      labs(y = "Coverage") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black", size = 16, angle = 90, vjust = .5, hjust = 1),
            axis.text.y = element_text(color = "black", size = 16),
            axis.ticks = element_line(color = "black", linewidth = .75),
            axis.line = element_line(linewidth = .75),
            axis.title.y = element_text(size = 20),
            axis.title.x = element_blank(),
            legend.title = element_blank(),
            legend.key.size = unit(1.5, "cm"),
            legend.text = element_text(size = 16),
            legend.position = c(.5, 1.2),
            legend.direction = "horizontal",
            plot.margin = unit(c(3,.10, .1, .2), "cm"),
            panel.spacing.x = unit(1, "cm"),
            panel.spacing.y = unit(1, "cm"),
            strip.text.x = element_text(vjust = 7.25, size = 16),
            strip.text.y = element_text(angle = 0, size = 16),
            strip.clip = "off",
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_grid(rho~gamma10, labeller = label_parsed)

dev.off()
```



# -------------------------------------------
# Research Design & Analysis
## PPCs
```{r}
# -------------------------------------------
# PREP DATA
GSU_Full_PPCs = 
  readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
               "Covariate_Joint_ORL_Bias",
               paste("T1_parent_Anx_Dep_SUD_Female",
                     "Covariate_Joint_ORL_Bias",
                     "Male_PPCs.rds", sep = "_"))) %>%
  group_by(deck) %>% 
  mutate(overall_mu = mean(observed)) %>% 
  group_by(trial, deck, overall_mu) %>% 
  
  # FULL DATA
  reframe(observed = mean(observed), mu = mean(mu),
          lower50 = mean(lower50), upper50 = mean(upper50),
          lower95 = mean(lower95), upper95 = mean(upper95))


# -------------------------------------------
# Create Plot
tiff(paste0(GSU_path, "Plots/IGT_Plot.tiff"),
     width = 5, height = 4, units = "in", res = 300)
  # PPC PLOTS
  GSU_Full_PPCs %>% 
    ggplot(aes(x = trial)) +
      # geoms
      geom_ribbon(aes(ymin = lower95, ymax = upper95, fill = deck),
                 # show.legend = F,
                  color = "transparent", alpha = .25) +
      geom_ribbon(aes(ymin = lower50, ymax = upper50, fill = deck),
                 # show.legend = F,
                  color = "transparent", alpha = .5) +
      geom_line(aes(y = mu, color = deck), linewidth = 1.5) +
      geom_point(aes(y = observed, fill = deck), color = "black",
                 show.legend = F,
                 shape = 21, stroke = 1.75, size = 3) +
      # scales
      scale_y_continuous(limits = c(.48,1.02),
                         breaks = seq(0,1,.25)) +
      scale_color_manual(values = c("#999999", "#E69F00", "#56B4E9", "#009E73")) +
      scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9", "#009E73")) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(#axis elements
            axis.line = element_line(size = 1.5),
            axis.ticks.length = unit(.1, "in"),
            axis.ticks = element_line(size = 1.5, color = "black", length),
            axis.text = element_text(size = 24, color = "black"),
            axis.title = element_text(size = 28),
            # legend elements
            legend.background = element_rect(fill = "transparent", colour = "transparent",
                                             color = "transparent"),
            legend.direction = "horizontal",
            legend.position = c(.525, 1.075),
            legend.title = element_blank(),
            legend.key.size = unit(.5, "in"),
            legend.key.spacing.y = unit(.25, "in"),
            legend.text = element_text(size = 24),
            # plot elements
            plot.margin = margin(t = .5, r = .25, l = .15, unit = 'in'))
dev.off()
```


## Discounting
```{r}
data = data.frame(delay = seq(0, 1, .01)) %>% 
  mutate(V = 1 / (1 + 14 * delay)*100,
         delay = delay*365)


tiff(paste0(GSU_path, "Plots/DD_Plot.tiff"),
     width = 5, height = 3.75, units = "in", res = 300)

ggplot(data, aes(x = delay, y = V)) +
  geom_line(linewidth = 1) +
  scale_y_continuous(limits = c(0, 100), expand = c(0, 0), breaks = c(0, 50, 100),
                     labels = c("$0", "$50", "$100")) +
  scale_x_continuous(limits = c(0, 365), expand = c(0, 0), breaks = c(1, 180, 365),
                     labels = c("1 day", "6 months", "1 year")) +
  labs(x = "Delay", y = "Discounted Value") +
  theme_classic() +
  theme(#axis elements
    axis.line = element_line(size = 1.5),
    axis.ticks.length = unit(.1, "in"),
    axis.ticks = element_line(size = 1.5, color = "black", length),
    axis.text = element_text(size = 24, color = "black"),
    axis.title = element_text(size = 28),
    # legend elements
    legend.background = element_rect(fill = "transparent", colour = "transparent",
                                     color = "transparent"),
    legend.direction = "horizontal",
    legend.position = c(.525, 1.075),
    legend.title = element_blank(),
    legend.key.size = unit(.5, "in"),
    legend.key.spacing.y = unit(.25, "in"),
    legend.text = element_text(size = 24),
    # plot elements
    plot.margin = margin(t = .5, r = .5, l = .15, unit = 'in'))

dev.off()
```





