---
title: "Fitting Binomial Model"
output: html_document
date: "2023-03-07"
---



# -------------------------------------------
# Setup
## Load Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggpubr)
library(ggh4x)
library(rstan)
library(hBayesDM)
library(bayesplot)
library(here)
library(miscTools)
library(cmdstanr)
library(stringi)
library(ggpp)
library(lemon)
library(grid)
library(egg)
# source(here("Code", "R", "3_Other", "helpful_functions.R"))
```



## RMD Setup
```{r}
sample = "T1_parent_SU_Dep_Anx"

stan_data = readRDS(here("1_TADS_Parents_PP", "Data", "1_Stan",
                         paste("design", sample, "Binomial", "IGT.RDS", sep = "_")))

model_name = "Covariate_Deck_Binomial"

focal_parameters = c(
  "mu_A", "mu_B", "mu_C", "mu_D",
  "sigma_A", "sigma_B", "sigma_C", "sigma_D",
  "tilde_A", "tilde_B", "tilde_C", "tilde_D",
  "mu_A_theta", "mu_B_theta", "mu_C_theta", "mu_D_theta",
  "A_theta", "B_theta", "C_theta", "D_theta"
)


group_parameters <- grep("mu|sigma", focal_parameters, value=TRUE)
person_parameters <- grep("mu|sigma", focal_parameters, value=TRUE, invert=TRUE)
```



# -------------------------------------------
# Model-Fitting
## Check Model
```{r, eval = F}
model_code = cmdstan_model(here("1_TADS_Parents_PP", "Code", "Stan", 
                                paste0(model_name, ".stan")), compile = F)

model_code$check_syntax(quiet = T)
```



## Fit Model
```{r, eval = F}
# Compile model
deck_model = stan_model(here("1_TADS_Parents_PP", "Code", "Stan",
                             paste0(model_name, ".stan")))


# -----------------------------------------------------------------------------------
# Fit model
deck_fit = sampling(deck_model, 
                    data   = stan_data, 
                    iter   = 5000, 
                    warmup = 1000, 
                    chains = 4, 
                    cores  = 4,
                    seed   = 43210,
                    save_warmup = F)
saveRDS(deck_fit, here("1_TADS_Parents_PP", "Data", "2_Fitted",
                       model_name,
                       paste(sample, model_name, "fit.rds", sep = "_")))

# -----------------------------------------------------------------------------------
# save posteriors
saveRDS(extract(deck_fit), here("1_TADS_Parents_PP", "Data", "2_Fitted",
                                model_name,
                                paste(sample, model_name, "posteriors.rds", sep = "_")))

# -----------------------------------------------------------------------------------
# save rhats
rhat(deck_fit, pars = focal_parameters) %>%
  data.frame() %>% mutate(parameter = rownames(.)) %>% 
  saveRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
               model_name,
               paste(sample, model_name, "rhats.rds", sep = "_")))
```



# -------------------------------------------
# Process Model Data
## Import Data
```{r}
# subset participant to exclude
sub_keep = stan_data$ID_participant[stan_data$X[,1] == 0]

model_name = "Covariate_Deck_Binomial"

# -----------------------------------------------------------------------------------
# read in model fit
deck_fit = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                        model_name,
                        paste(sample, model_name, "fit.rds", sep = "_")))

# -----------------------------------------------------------------------------------
# read in posteriors
deck_posteriors = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                               model_name,
                               paste(sample, model_name, "posteriors.rds", sep = "_")))

# -----------------------------------------------------------------------------------
# read in rhats
deck_rhats = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                          model_name,
                          paste(sample, model_name, "rhats.rds", sep = "_")))
```



## Prep Data
### Group-Level Data
```{r, eval = T}
deck_grp_thetas = data.frame(iteration = 1:((deck_fit@sim$iter -
                                               deck_fit@sim$warmup) *
                                              deck_fit@sim$chains),
                             A_mu = deck_posteriors$mu_A_theta,
                             A_beta = deck_posteriors$mu_A,
                             B_mu = deck_posteriors$mu_B_theta,
                             B_beta = deck_posteriors$mu_B,
                             C_mu = deck_posteriors$mu_C_theta,
                             C_beta = deck_posteriors$mu_C,
                             D_mu = deck_posteriors$mu_D_theta,
                             D_beta = deck_posteriors$mu_D) %>% 
  pivot_longer(starts_with(c("A", "B", "C", "D")), names_to = c("deck", "group"),
               values_to = "estimate", names_sep = "\\.") %>% 
  filter(!(str_detect(deck, "beta") & group == 1)) %>% 
  separate(col = "deck", into = c("deck", "parameter"), sep = "_") %>% 
  mutate(group = case_when(group == 1 & parameter == "mu" ~ "Con",
                           group == 2 & parameter == "mu" ~ "SU",
                           group == 3 & parameter == "mu" ~ "Dep",
                           group == 4 & parameter == "mu" ~ "Anx",
                           group == 2 & parameter == "beta" ~ "SU-Con",
                           group == 3 & parameter == "beta" ~ "Dep-Con",
                           group == 4 & parameter == "beta" ~ "Anx-Con")) %>% 
  group_by(deck, parameter, group) %>% 
  mutate(mu = mean(estimate),
         lower = HDIofMCMC(estimate)[1],
         upper = HDIofMCMC(estimate)[2],
         group = factor(group, levels = c("Con", "SU", "Dep", "Anx",
                                          "SU-Con", "Dep-Con", "Anx-Con")),
         group_mean = case_when(group %in% c("Con", "SU", "Dep", "Anx") ~ group,
                                T ~ "Comparison"),
         group_mean = factor(group_mean, ordered = T,
                             levels = c("Con", "SU", "Dep", "Anx", "Comparison")),
         comparison = case_when(group %in% c("Con", "SU", "Dep", "Anx") ~ "Group Mean",
                                T ~ group),
         comparison = factor(comparison, ordered = T,
                             levels = c("Group Mean", "SU-Con", "Dep-Con", "Anx-Con")))
```



### Individual-Subject Data
```{r, eval = T}
deck_ind_data = data.frame(ID = stan_data$ID_OG,
                           ID_participant = stan_data$ID_participant,
                           SU = stan_data$X[,2],
                           Dep = stan_data$X[,3],
                           Anx = stan_data$X[,4],
                           obs_A = stan_data$A_plays / stan_data$A_trials,
                           obs_B = stan_data$A_plays / stan_data$B_trials,
                           obs_C = stan_data$A_plays / stan_data$C_trials,
                           obs_D = stan_data$A_plays / stan_data$D_trials,
                           pred_A = apply(deck_posteriors$A_pred, 2, mean) / stan_data$A_trials,
                           pred_B = apply(deck_posteriors$B_pred, 2, mean) / stan_data$B_trials,
                           pred_C = apply(deck_posteriors$C_pred, 2, mean) / stan_data$C_trials,
                           pred_D = apply(deck_posteriors$D_pred, 2, mean) / stan_data$D_trials) %>% 
  pivot_longer(ends_with(c("_A", "_B", "_C", "_D")), names_to = c("type", "deck"),
               values_to = "estimate", names_sep = "_") %>% 
  pivot_wider(names_from = "type", values_from = "estimate")
```



# -------------------------------------------
# Traceplots
```{r, eval = F}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name,
          "group_traceplots.tiff"),
     width = 35, height = 25, units = "cm", res = 300)
traceplot(
  deck_fit,
  pars = group_parameters
)
dev.off()


for(i in person_parameters){
  tiff(here("1_TADS_Parents_PP", "Figs_Tables",
            model_name,
            "traceplots.tiff"),
       width = 100, height = 100, units = "cm", res = 300)
  traceplot(deck_fit,
            pars = i
  ) %>% print()
  dev.off()
}
```



# -------------------------------------------
# Distribution Plots
## Group-Level Posterior Distributions
```{r}
# build plot
deck_group_plot = deck_grp_thetas %>% 
  filter(comparison == "Group Mean") %>% 
  ggplot(aes(x = estimate, fill = group)) +
  # geoms
  geom_text_npc(data = data.frame(deck = factor(c("A", "B", "C", "D"),
                                                levels = c("A", "B", "C", "D"),
                                                ordered = T),
                                  lab_ = c("A", "B", "C", "D")),
                aes(label = lab_), npcx = 1, npcy = .5, size = 4, vjust = 1) +
  geom_density(alpha = .5, linewidth = .25) +
  geom_hline(yintercept = 0) +
  # scales
  scale_x_continuous(limits = c(.55,.95), expand = c(0, 0), breaks = seq(.6, .9, .1)) +
  scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
  scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9", "#009E73"),
                    limits = c("Con", "SU", "Dep", "Anx")) +
  # themes
  labs(x = "Estimate", y = "Density") +
  coord_cartesian(clip = "off") +
  theme_classic() +
  theme(axis.text.x = element_text(color = "black"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line.y = element_blank(),
        axis.title = element_blank(),
        legend.text = element_text(size = 6),
        legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.05, "lines"),
        legend.position = c(.2, .125),
        legend.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.title = element_blank(),
        plot.margin = unit(c(0, .2, 0, .1), "cm"),
        panel.spacing.x = unit(.5, "cm"),
        panel.spacing.y = unit(-.25, "cm"),
        strip.text = element_blank(),
        strip.background = element_rect(fill = "transparent", colour = "transparent"),
        panel.background = element_rect(fill = "transparent", colour = "transparent"),
        plot.background = element_rect(fill = "transparent", color = "transparent")) +
  facet_rep_grid(deck~., scales = "free")
```



## Make Person-Level Plots
```{r}
make_distribution_plot = function(data, grp_diag, grp_color = "gray45") {
  colnames(data)[colnames(data)==grp_diag] = "group"
  
  plot = data %>% 
    mutate(lab_ = case_when(deck == "A" ~ grp_diag, T ~ NA_character_)) %>%
    filter(group == 1) %>% 
    ggplot() +
    # geoms
    geom_text_npc(aes(label = lab_), npcx = 0, npcy = 1) +
    geom_histogram(aes(x = obs, y = ..density..), color = "black", fill = grp_color,
                   alpha = .5, linewidth = .25) +
    geom_density(aes(x = pred), fill = grp_color, linewidth = .5, alpha = .5) +
    # scales
    scale_x_continuous(limits = c(0, 1), expand = c(0, 0), breaks = seq(0, 1, .25),
                       labels = c("0", ".25", ".50", ".75", "1")) +
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05))) +
    # themes
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.x = element_line(color = "black"),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          axis.title = element_blank(),
          legend.text = element_text(size = 6),
          legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.1, "lines"),
          legend.position = c(.1, .945), legend.direction = "vertical",
          legend.background = element_rect(fill = "transparent", colour = "transparent"),
          legend.title = element_blank(),
          plot.margin = unit(c(0, .2, 0, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(-.25, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_grid(deck~., scales = "free")
  
  return(plot)
}
```



## Combine & Save Plots
```{r}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name,
          paste(sample, "Distribution Plots.tiff", sep = " ")),
     width = 14.6, height = 7, units = "cm", res = 300)

grid.newpage()
# main plot
pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
grid.draw(ggarrange(make_distribution_plot(deck_ind_data, "SU",  "#E69F00"),
                    make_distribution_plot(deck_ind_data, "Dep", "#56B4E9"),
                    make_distribution_plot(deck_ind_data, "Anx", "#009E73"),
                    deck_group_plot,
                    ncol = 4) %>% 
            annotate_figure(left = textGrob("Density", rot = 90, hjust = .25),
                            bottom = textGrob("Estimate")))

dev.off()
```



# -------------------------------------------
# Dot Plots
## Make Person-Level Plots
```{r}
make_dot_plot = function(ind_data, grp_data,
                         grp_diag, grp_color = "gray45") {
  colnames(ind_data)[colnames(ind_data)==grp_diag] = "group"
  mus = grp_data %>% filter(comparison == "Group Mean") %>% 
    filter(group %in% c("Con", grp_diag)) %>% 
    group_by(deck, group) %>%
    summarise(mu = mean(mu), lower = mean(lower), upper = mean(upper),
              group = case_when(group == "Con" ~ 0, T ~ 1),
              group = factor(group, levels = c(0, 1), labels = c("Con", grp_diag), ordered = T))
  
  plot = ind_data %>% 
    mutate(group = factor(group, levels = c(0, 1), labels = c("Con", grp_diag), ordered = T)) %>%
    ggplot() +
    # geoms
    geom_dotplot(aes(x = group, y = obs, fill = group, color = group),
                 binaxis = "y", stackdir = "center",
                 position = position_dodge(width = .8), alpha = .5) +
    geom_pointrange(data = mus, aes(x = group, y = mu, ymin = lower, ymax = upper),
                    color = "black", size = .05,
                    position = position_dodge(width = .8)) +
    # scales
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), breaks = seq(0, 1, .25),
                       labels = c("0", ".25", ".50", ".75", "1")) +
    scale_color_manual(values = c("gray45", grp_color)) +
    scale_fill_manual(values = c("gray45", grp_color)) +
    # themes
    labs(y = "Proportion of Plays") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.x = element_line(color = "black"),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          axis.title = element_blank(),
          legend.position = "none",
          plot.margin = unit(c(.2, .2, 0, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(-.25, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_grid(deck~., scales = "free")
  
  return(plot)
}
```



## Combine & Save Plots
```{r}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name,
          paste(sample, "Dot Plots.tiff", sep = " ")),
     width = 14.6, height = 7, units = "cm", res = 300)

grid.newpage()
# main plot
pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
grid.draw(ggarrange(make_dot_plot(deck_ind_data, deck_grp_thetas,
                                  "SU",  "#E69F00"),
                    make_dot_plot(deck_ind_data, deck_grp_thetas,
                                  "Dep", "#56B4E9"),
                    make_dot_plot(deck_ind_data, deck_grp_thetas,
                                  "Anx", "#009E73"),
                    deck_group_plot,
                    ncol = 4) %>% 
            annotate_figure(left = textGrob("Proportion Plays", rot = 90, hjust = .35),
                            bottom = textGrob("Estimate")))

dev.off()
```



# -------------------------------------------
# Beta Plots
## Make Person-Level Plots
```{r}
make_dot_plot = function(ind_data, grp_data,
                         grp_diag, grp_color = "gray45") {
  colnames(ind_data)[colnames(ind_data)==grp_diag] = "group"
  mus = grp_data %>% filter(comparison == "Group Mean") %>% 
    filter(group %in% c("Con", grp_diag)) %>% 
    group_by(deck, group) %>%
    summarise(mu = mean(mu), lower = mean(lower), upper = mean(upper),
              group = case_when(group == "Con" ~ 0, T ~ 1),
              group = factor(group, levels = c(0, 1), labels = c("Con", grp_diag), ordered = T))
  
  plot = ind_data %>% 
    mutate(group = factor(group, levels = c(0, 1), labels = c("Con", grp_diag), ordered = T)) %>%
    ggplot() +
    # geoms
    geom_dotplot(aes(x = group, y = obs, fill = group, color = group),
                 binaxis = "y", stackdir = "center",
                 position = position_dodge(width = .8), alpha = .5) +
    geom_pointrange(data = mus, aes(x = group, y = mu, ymin = lower, ymax = upper),
                    color = "black", size = .05,
                    position = position_dodge(width = .8)) +
    # scales
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), breaks = seq(0, 1, .25),
                       labels = c("0", ".25", ".50", ".75", "1")) +
    scale_color_manual(values = c("gray45", grp_color)) +
    scale_fill_manual(values = c("gray45", grp_color)) +
    # themes
    labs(y = "Proportion of Plays") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.x = element_line(color = "black"),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          axis.title = element_blank(),
          legend.position = "none",
          plot.margin = unit(c(.2, .2, 0, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(-.25, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_grid(deck~., scales = "free")
  
  return(plot)
}
```



## Combine & Save Plots
```{r}
# build plot
deck_beta_plot = deck_grp_thetas %>% 
  filter(comparison != "Group Mean") %>% 
  ggplot(aes(x = estimate, fill = group)) +
  # geoms
  geom_text_npc(data = data.frame(deck = factor(c("A", "B", "C", "D"),
                                                levels = c("A", "B", "C", "D"),
                                                ordered = T),
                                  lab_ = c("A", "B", "C", "D")),
                aes(label = lab_), npcx = 1, npcy = .5, size = 4, vjust = 1) +
  geom_density(alpha = .5, linewidth = .25) +
  geom_hline(yintercept = 0) +
  # scales
  scale_x_continuous(limits = c(-.75,.75), expand = c(0, 0), breaks = seq(-.5, .5, .25),
                     labels = c("-.5", "-.25", "0", ".25", ".5")) +
  scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
  scale_fill_manual(values = c("#E69F00", "#56B4E9", "#009E73"),
                    limits = c("SU-Con", "Dep-Con", "Anx-Con")) +
  # themes
  labs(x = "Estimate", y = "Density") +
  coord_cartesian(clip = "off") +
  theme_classic() +
  theme(axis.text.x = element_text(color = "black"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line.y = element_blank(),
        # axis.title = element_blank(),
        legend.text = element_text(size = 6),
        legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.05, "lines"),
        legend.position = c(.15, .935),
        legend.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.title = element_blank(),
        plot.margin = unit(c(0, .2, 0, .1), "cm"),
        panel.spacing.x = unit(.5, "cm"),
        panel.spacing.y = unit(-.25, "cm"),
        strip.text = element_blank(),
        strip.background = element_rect(fill = "transparent", colour = "transparent"),
        panel.background = element_rect(fill = "transparent", colour = "transparent"),
        plot.background = element_rect(fill = "transparent", color = "transparent")) +
  facet_rep_grid(deck~., scales = "free")


tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name,
          paste(sample, "Betas Distribution Plots.tiff", sep = " ")),
     width = 4, height = 7, units = "cm", res = 300)

grid.newpage()
# main plot
pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
grid.draw(deck_beta_plot)

dev.off()
```



# -------------------------------------------





































