---
title: "Parameter Recovery for Covariate ORL w/Bias"
output: html_document
---



# -------------------------------------------
# Setup
## Load Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rstan)
library(hBayesDM)
library(bayesplot)
library(here)
library(miscTools)
library(wBoot)
library(cmdstanr)
library(stringi)
library(ggpp)
library(lemon)
source(here("1_IGT_PP", "Code", "R", "3_other", "helpful_functions.R"))
library(MASS)
library(ggh4x)
library(grid)
```



## Load Outcomes & Sim Type
```{r}
outcomes = readRDS(here("1_IGT_PP", "Data","outcomes.RDS"))
sim_type = "Covariate_ORL_Bias"
parameter_names = c("Arew", "Apun", "betaF", "betaB")

groups = c("Anx", "Dep", "SUD")
model_name = "Covariate_Joint_ORL_Bias"
sample = "T1_parent_Anx_Dep_SUD"
```



## Functions
```{r, eval = T}
#------------------------------------------------------------------------------
# USE SOFTMAX TO OBTAIN CHOICE PROBABILITIES - USED IN SIMULATIONS
softmax = function(values){
  return(exp(values) / sum(exp(values)))
}


#------------------------------------------------------------------------------
# SIMULATION FUNCTION
simulate_orl = function(parameter_values, N, X, custom_seed = 20230928) {
  set.seed(seed = custom_seed)
  data = data.frame()
  
  for(i in 1:N){
    # parameters for sim
    Arew = filter(parameter_values, ID == i)$Arew
    Apun = filter(parameter_values, ID == i)$Apun
    betaF = filter(parameter_values, ID == i)$betaF
    betaB = filter(parameter_values, ID == i)$betaB
    
    utility = rep(0,4)
    ev = rep(0,4)
    ef = rep(0,4)
    
    ef_chosen = 0
    PEval = 0
    PEfreq = 0
    PEfreq_fic = rep(0,4)
    card_trial = rep(0,4)
    
    for(t in 1:120){
      outcome = outcomes$outcome[outcomes$trial == t]
      sign = outcomes$sign[outcomes$trial == t]
      card = outcomes$card[outcomes$trial == t]
      
      utility = ev + ef * betaF + betaB
      prob = softmax(c(utility[card], 0))
      curr_choice = sample(c(1,2), 1, prob = prob)
      
      if(curr_choice==1) {
        PEval = outcome - ev[card]
        PEfreq = sign - ef[card]
        PEfreq_fic = -1*sign/3 - ef
        ef_chosen = ef[card]
        
        if(outcome >= 0) {
          ef = ef + Apun * PEfreq_fic
          ef[card] = ef_chosen + Arew * PEfreq
          ev[card] = ev[card] + Arew * PEval
        } else {
          ef = ef + Arew * PEfreq_fic
          ef[card] = ef_chosen + Apun * PEfreq
          ev[card] = ev[card] + Apun * PEval
        }
      }
      
      card_trial[card] = card_trial[card] + 1
      data = data.frame(ID = i,
                        anx = X[i,2],
                        dep = X[i,3],
                        sud = X[i,4],
                        card = card,
                        trial = t,
                        outcome = outcome,
                        sign = sign,
                        card_trial = card_trial[card],
                        choice = curr_choice) %>% 
        bind_rows(data)
    }
  }
  data %>%
    return()
}
```



# -------------------------------------------
# Set Parameter Values
## Load Data & Posteriors
```{r, eval = T}
# -----------------------------------------------------------------------------------
# read in posteriors
orl_posteriors = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                              model_name,
                              paste(sample, model_name, "posteriors.rds", sep = "_")))


# -----------------------------------------------------------------------------------
# read in raw data
og_data = readRDS(here("1_TADS_Parents_PP", "Data", "1_Stan",
                       paste("design", sample, "IGT.RDS", sep = "_")))


# -----------------------------------------------------------------------------------
# subset participant to exclude
sub_keep = og_data$X[,1,] != 0

X = og_data$X[sub_keep,,]
```



# -------------------------------------------
# Simulate Parameters
## Set Mus
```{r, eval = T}
mus = data.frame(Arew_beta = apply(orl_posteriors$beta_Arew, 2, mean),
                 Apun_beta = apply(orl_posteriors$beta_Apun, 2, mean),
                 betaF_beta = apply(orl_posteriors$beta_betaF, 2, mean),
                 betaB_beta = apply(orl_posteriors$beta_betaB, 2, mean))


sigmas = data.frame(Arew_sigma = apply(orl_posteriors$sigma_Arew, 2, mean),
                    Apun_sigma = apply(orl_posteriors$sigma_Apun, 2, mean),
                    betaF_sigma = apply(orl_posteriors$sigma_betaF, 2, mean),
                    betaB_sigma = apply(orl_posteriors$sigma_betaB, 2, mean))
```


## Simulate Person-Level Parameters
```{r, eval = T}
set.seed(20240530)

parameters = data.frame(Arew_mu = rowSums(t(t(X) * mus[,"Arew_beta"])),
                        Apun_mu = rowSums(t(t(X) * mus[,"Apun_beta"])),
                        betaF_mu = rowSums(t(t(X) * mus[,"betaF_beta"])),
                        betaB_mu = rowSums(t(t(X) * mus[,"betaB_beta"])),
                        sigmas)

simulated_parameters = data.frame() 

for(i in 1:nrow(parameters)){
  simulated_parameters = data.frame(ID = i,
                                    Arew = pnorm(rnorm(n = 1, mean = parameters[i, "Arew_mu"],
                                                       sd = parameters[i, "Arew_sigma"])),
                                    Apun = pnorm(rnorm(n = 1, mean = parameters[i, "Apun_mu"],
                                                       sd = parameters[i, "Apun_sigma"])),
                                    betaF = rnorm(n = 1, mean = parameters[i, "betaF_mu"],
                                                  sd = parameters[i, "betaF_sigma"]),
                                    betaB = rnorm(n = 1, mean = parameters[i, "betaB_mu"],
                                                  sd = parameters[i, "betaB_sigma"])) %>% 
    bind_rows(simulated_parameters)
}
saveRDS(simulated_parameters, here("1_TADS_Parents_PP", "Data",
                                   "4_Parameter_Recovery", "simulated_parameters.RDS"))
```


#***************************************
# Side-work
```{r}
diag_parameters = data.frame(beta = t(mus)) %>% 
  mutate(Con = beta.1,
         Anx = beta.1 + beta.2,
         Anx_Dep = beta.1 + beta.2 + beta.3,
         Anx_SUD = beta.1 + beta.2 + beta.4,
         Anx_Dep_SUD = beta.1 + beta.2 + beta.3 + beta.4,
         Dep = beta.1 + beta.3,
         Dep_SUD = beta.1 + beta.3 + beta.4,
         SUD = beta.1 + beta.4) %>% 
  dplyr::select(-starts_with("beta"))



parameters = data.frame(Arew_mu = rowSums(t(t(X) * mus[,"Arew_beta"])),
                        Apun_mu = rowSums(t(t(X) * mus[,"Apun_beta"])),
                        betaF_mu = rowSums(t(t(X) * mus[,"betaF_beta"])),
                        betaB_mu = rowSums(t(t(X) * mus[,"betaB_beta"])),
                        sigmas)
X[1:2,]
t(mus[,"Arew_beta"] * t(X[1:2,]))
```


```{r}
betaF_betas = apply(orl_posteriors$beta_betaF, 2, mean)
paste("Con = ", betaF_betas[1])
paste("Anx = ", betaF_betas[1] + betaF_betas[2])
paste("Dep = ", betaF_betas[1] + betaF_betas[3])
paste("SUD = ", betaF_betas[1] + betaF_betas[4])
```


```{r}
print("Data")
paste("Anx =", round(mean(apply(orl_posteriors$betaF, 2, mean)*
                            ifelse(stan_data$X[,2,1] == 1, 1, NA), na.rm = T), 3))
paste("Dep =", round(mean(apply(orl_posteriors$betaF, 2, mean)*
                            ifelse(stan_data$X[,3,1] == 1, 1, NA), na.rm = T), 3))
paste(c("Con =", "Anx =", "Dep =", "SUD ="), round(apply(orl_posteriors$mu_betaF, 3, mean),3))

print("Simulated")
paste("Anx =", round(mean(apply(sim_orl_posteriors$betaF, 2, mean)*
                            ifelse(stan_data$X[,2,1] == 1, 1, NA), na.rm = T), 3))
paste("Dep =", round(mean(apply(sim_orl_posteriors$betaF, 2, mean)*
                            ifelse(stan_data$X[,3,1] == 1, 1, NA), na.rm = T), 3))
paste(c("Con =", "Anx =", "Dep =", "SUD ="), round(apply(sim_orl_posteriors$mu_betaF, 3, mean),3))
```

```{r}
temp_simulated_parameters = left_join(simulated_parameters, 
                                      data.frame(ID = 1:nrow(X), X))


paste("Con =", round(mean(temp_simulated_parameters$betaF*
                            ifelse(temp_simulated_parameters$X1 == 1, 1, NA), na.rm = T), 3))

paste("Anx =", round(mean(temp_simulated_parameters$betaF*
                            ifelse(temp_simulated_parameters$X2 == 1, 1, NA), na.rm = T), 3))

paste("Dep =", round(mean(temp_simulated_parameters$betaF*
                            ifelse(temp_simulated_parameters$X3 == 1, 1, NA), na.rm = T), 3))

paste("SUD =", round(mean(temp_simulated_parameters$betaF*
                            ifelse(temp_simulated_parameters$X4 == 1, 1, NA), na.rm = T), 3))

cohens_ds = data.frame(iteration = 1:nrow(orl_posteriors$sigma_Arew),
                       Arew = sweep(orl_posteriors$beta_Arew[,2:4], 1, 
                                    orl_posteriors$sigma_Arew, FUN = '/'),
                       Apun = sweep(orl_posteriors$beta_Apun[,2:4], 1, 
                                    orl_posteriors$sigma_Apun, FUN = '/'),
                       betaF = sweep(orl_posteriors$beta_betaF[,2:4], 1, 
                                     orl_posteriors$sigma_betaF, FUN = '/'),
                       betaB = sweep(orl_posteriors$beta_betaB[,2:4], 1, 
                                     orl_posteriors$sigma_betaB, FUN = '/')) %>% 
  pivot_longer(starts_with(c("Arew", "Apun", "betaF", "betaB")),
               names_to = c("parameter", "group"), values_to = "d", names_sep = "\\.") %>% 
  mutate(group = case_when(group == "1" ~ "Anx", group == "2" ~ "Dep", group == "3" ~ "SUD"))

cohens_ds %>% 
  ggplot(aes(x = d, fill = group)) +
    # geoms
    geom_density(alpha = .5, linewidth = .25) +
    geom_hline(yintercept = 0) +
    geom_vline(xintercept = 0) +
    # scales
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
    scale_color_manual(values = c("black", "#E01818", "#2184DA", "#FFC107"),
                       limits = c("Anx", "Dep", "SUD")) +
    scale_fill_manual(values = c("black", "#E01818", "#2184DA", "#FFC107"),
                      limits = c("Anx", "Dep", "SUD")) +
    # themes
    labs(x = "Effect Size") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black", size = 8),
          axis.ticks.x = element_line(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          axis.title.y = element_blank(),
          legend.text = element_text(size = 6),
          legend.spacing.x = unit(.05, 'cm'),
          legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.05, "lines"),
          legend.position = c(.125, .975),
          legend.background = element_rect(fill = "transparent", colour = "transparent"),
          legend.title = element_blank(),
          plot.margin = unit(c(.05, .2, 0, .5), "cm"),
          panel.spacing.x = unit(.3, "cm"),
          panel.spacing.y = unit(.1, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(parameter~., nrow = 2, ncol = 2,
                   scales = "free") +
    # facetted_pos_scales(x = x_scaling) +
    guides(fill = guide_legend(nrow = 3))
```



#***************************************



```{r}
simulated_parameters = readRDS(here("1_TADS_Parents_PP", "Data",
                                    "4_Parameter_Recovery", "simulated_parameters.RDS"))
```



# -------------------------------------------
# Simulate Data
## Simulation
```{r, eval = T}
sim_data = simulate_orl(parameter_values = simulated_parameters,
                        N = nrow(simulated_parameters),
                        X = X,
                        custom_seed = 20240304)


saveRDS(sim_data, here("1_TADS_Parents_PP", "Data",
                       "4_Parameter_Recovery", "sim_data.RDS"))
```



```{r}
sim_data = readRDS(here("1_TADS_Parents_PP", "Data",
                        "4_Parameter_Recovery", "sim_data.RDS"))
```




## Prep Stan Data
```{r, eval = T}
IDs = vector()
N = length(unique(sim_data$ID))
Trials = max(sim_data$trial)
S = 1
X_ = array(data = -1, c(nrow(X), ncol(X), S))

Tsubj = array(120, c(N, S))
choice = card = outcome = sign = array(-1, c(N, Trials, S))

for(i in 1:N){
  for(s in 1:S){
    
    if(Tsubj[i,s] > 0){
      temp_data = sim_data %>% 
        filter(ID == i) %>% 
        arrange(trial)
      IDs[i] = mean(temp_data$ID)
      choice[i,,s] = temp_data$choice
      card[i,,s] = temp_data$card
      outcome[i,,s] = temp_data$outcome
      sign[i,,s] = temp_data$sign
      X_[i,,s] = c(1, mean(temp_data$anx), mean(temp_data$dep), mean(temp_data$sud))
    }
  }
}
stan_data = list(
  ID = IDs,
  N = N,
  T = Trials,
  S = S,
  X = X_,
  D = ncol(X_),
  subjIDs = IDs,
  Tsubj = Tsubj,
  choice = choice,
  card = card,
  outcome = outcome,
  sign = sign
)
```



# -------------------------------------------
# Fit Model
```{r, eval = T}
# Compile model
orl_model = stan_model(here("1_TADS_Parents_PP", "Code", "Stan",
                            paste0(model_name, ".stan")))


# Fit model
sim_orl_fit = sampling(orl_model,
                       data   = stan_data, 
                       iter   = 5000, 
                       warmup = 1000, 
                       chains = 4, 
                       cores  = 4,
                       seed   = 43210,
                       save_warmup = F)


#save the fitted model as an .rds file
saveRDS(sim_orl_fit, here("1_TADS_Parents_PP", "Data",
                          "4_Parameter_Recovery", "sim_orl_fit.RDS"))
```



```{r}
sim_orl_fit = readRDS(here("1_TADS_Parents_PP", "Data",
                           "4_Parameter_Recovery", "sim_orl_fit.RDS"))
```



```{r, eval = T}
sim_orl_posteriors <- extract(sim_orl_fit)
saveRDS(sim_orl_posteriors,
        here("1_TADS_Parents_PP", "Data",
             "4_Parameter_Recovery", "sim_orl_posteriors.RDS"))


sim_orl_rhats = rhat(sim_orl_fit, pars = c(
  "mu_Arew", "mu_Apun", "mu_betaF", "mu_betaB", 
  "sigma_Arew", "sigma_Apun", "sigma_betaF", "sigma_betaB", 
  "Arew", "Apun", "betaF", "betaB", 
  "beta_Arew", "beta_Apun", "beta_betaF", "beta_betaB", 
  "R_Arew", "R_Apun", "R_betaF", "R_betaB"
)) %>%
    data.frame() %>% mutate(parameter = rownames(.))
saveRDS(sim_orl_rhats,
        here("1_TADS_Parents_PP", "Data",
             "4_Parameter_Recovery", "sim_orl_rhats.RDS"))
```


```{r}
sim_orl_posteriors = readRDS(here("1_TADS_Parents_PP", "Data",
                                  "4_Parameter_Recovery", "sim_orl_posteriors.RDS"))
```


## Traceplots
```{r, eval = T}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          "Covariate_Joint_ORL_Bias", "T1_parent_Anx_Dep_SUD",
          "Supplement_0 Group Traceplots.tiff"),
     width = 35, height = 25, units = "cm", res = 300)
  traceplot(
    sim_orl_fit,
    pars = c(
      "mu_Arew", "mu_Apun", "mu_betaF", "mu_betaB", 
      "sigma_Arew", "sigma_Apun", "sigma_betaF", "sigma_betaB",
      "beta_Arew", "beta_Apun", "beta_betaF", "beta_betaB"))
dev.off()
```


# -------------------------------------------
# Plot Recovered Parameters
## Prep Data
```{r}
recovered_parameters =
  data.frame(Arew = sim_orl_posteriors$Arew,
             Apun = sim_orl_posteriors$Apun,
             betaF = sim_orl_posteriors$betaF,
             betaB = sim_orl_posteriors$betaB) %>% 
  pivot_longer(everything(),
               names_to = c("parameter", "ID", "session"),
               values_to = "recovered",
               names_sep = "\\.", names_transform = list(ID = as.numeric)) %>% 
  group_by(parameter, ID) %>% 
  summarise(recovered = mean(recovered))


actual_parameters = simulated_parameters %>%
  pivot_longer(c(everything(), -ID), 
               names_to = "parameter", values_to = "actual")

combined_parameters = full_join(recovered_parameters, actual_parameters)
```



## Run Correlations
```{r}
set.seed(20240323)
PR_correlations = data.frame()

for(p in c("Arew", "Apun", "betaF", "betaB")){
  cur_data = filter(combined_parameters,
                    parameter == p)
  cur_cor = boot.cor.bca(
    x = cur_data$actual, y = cur_data$recovered,
    alternative = c("two.sided", "less", "greater"),
    null.hyp = NULL, conf.level = 0.95, type = NULL, R = 9999)
  PR_correlations = data.frame(parameter = p,
                               estimate = cur_cor$Observed) %>% 
    bind_rows(PR_correlations)
}
PR_correlations = PR_correlations %>% 
  mutate(estimate = round(estimate,2),
         estimate_lab = paste("r =", ifelse(sign(estimate)==1," ","-"),
                              stri_pad_right(str_remove(abs(estimate), "^0+"),
                                             width = 3, pad = "0"),sep=""),
         parameter = factor(parameter,
                            levels = c("Arew", "Apun", "betaF", "betaB"),
                            labels = c(expression(paste(italic(A),"+",sep="")),
                                       expression(paste(italic(A),"-",sep="")),
                                       expression(paste("\u03B2",italic(f),sep="")),
                                       expression(paste("\u03B2",italic(b),sep="")))))
```



## Plot Parameter Recovery Correlations
```{r}
tiff(here("1_TADS_Parents_PP", "Figs_Tables", "Covariate_Joint_ORL_Bias",
          "T1_parent_Anx_Dep_SUD",
          "Supplement_1 Parameter Recovery.tiff"),
     width = 14.6, height = 5, units = "cm", res = 300)
  combined_parameters %>% 
    group_by(parameter) %>% 
    mutate(z_actual = (actual - mean(actual)) / sd(actual),
           z_recovered = (recovered - mean(recovered)) / sd(recovered),
           parameter = factor(
             parameter,
             levels = c("Arew", "Apun", "betaF", "betaB"),
             labels = c(expression(paste(italic(A),"+",sep="")),
                        expression(paste(italic(A),"-",sep="")),
                        expression(paste("\u03B2",italic(f),sep="")),
                        expression(paste("\u03B2",italic(b),sep=""))))) %>% 
    ggplot(aes(x = z_actual, y = z_recovered)) +
      geom_text_npc(data = PR_correlations, aes(npcx = "left", npcy = "top",
                                                label = estimate_lab),
                    vjust = .5, size = 3) +
        geom_point(size = 1, shape = 21, color = "black", fill = "gray50") +
        geom_smooth(method = "lm", formula = "y ~ x", color = "black",
                    se = F, size = .5, fullrange = T) +
      theme_classic() +
      theme(aspect.ratio = 1,
            axis.text = element_text(color = "black"),
            strip.background = element_blank()) +
      labs(x = "Actual", y = "Recovered",
           caption = "X- and Y-axis values are z-scored") +
      facet_rep_grid(.~parameter,
                     labeller = label_parsed)
dev.off()
```



# -------------------------------------------
# Check Group-Differences
```{r}
group_differences = data.frame(
  iteration = 1:((sim_orl_fit@sim$iter -
                    sim_orl_fit@sim$warmup) *
                   sim_orl_fit@sim$chains), 
  Arew_2 = sim_orl_posteriors$beta_Arew[,2],
  Arew_3 = sim_orl_posteriors$beta_Arew[,3],
  Arew_4 = sim_orl_posteriors$beta_Arew[,4],
  Apun_2 = sim_orl_posteriors$beta_Apun[,2],
  Apun_3 = sim_orl_posteriors$beta_Apun[,3],
  Apun_4 = sim_orl_posteriors$beta_Apun[,4],
  betaF_2 = sim_orl_posteriors$beta_betaF[,2],
  betaF_3 = sim_orl_posteriors$beta_betaF[,3],
  betaF_4 = sim_orl_posteriors$beta_betaF[,4],
  betaB_2 = sim_orl_posteriors$beta_betaB[,2],
  betaB_3 = sim_orl_posteriors$beta_betaB[,3],
  betaB_4 = sim_orl_posteriors$beta_betaB[,4]) %>% 
  pivot_longer(starts_with(c("Arew", "Apun", "betaF", "betaB")),
               names_to = c("parameter", "group"),
               values_to = "estimate", names_sep = "_") %>% 
  mutate(group = case_when(group == 2 ~ "Anx",
                           group == 3 ~ "Dep",
                           group == 4 ~ "SUD"),
         parameter = factor(parameter, ordered = T,
                            levels = c("Arew", "Apun", "betaF", "betaB")),
         group = factor(group, levels = c("Anx", "Dep", "SUD"),
                        ordered = T))

group_differences %>% 
  group_by(parameter, group) %>% 
  summarise(mu = round(mean(estimate), 2),
            lower = round(HDIofMCMC(estimate)[1], 2),
            upper = round(HDIofMCMC(estimate)[2], 2),
            greater_0 = round(mean(estimate > 0), 2),
            sig = case_when(lower < 0 & upper < 0 ~ "*",
                            lower > 0 & upper > 0 ~ "*",
                            T ~ "")) %>% 
  write.csv(here("1_TADS_Parents_PP", "Figs_Tables", "Covariate_Joint_ORL_Bias",
                 "T1_parent_Anx_Dep_SUD", "Supplement_1 Parameter Recovery.csv"))
```



## X-Axis
```{r}
x_scaling = list(
  parameter == "Arew" ~ scale_x_continuous(limits = c(-.4, .4), breaks = seq(-.4, .4, length.out = 3),
                                           expand = expansion(mult = .05)),
  parameter == "Apun" ~ scale_x_continuous(limits = c(-.4, .4), breaks = seq(-.4, .4, length.out = 3),
                                           expand = expansion(mult = .05)),
  parameter == "betaF" ~ scale_x_continuous(limits = c(-2.5, 2.5), breaks = seq(-2.5, 2.5, length.out = 3),
                                            expand = expansion(mult = .05)),
  parameter == "betaB" ~ scale_x_continuous(limits = c(-.75, .75), breaks = seq(-.8, .8, length.out = 3),
                                            expand = expansion(mult = .05))
)
```



## Make Plots
```{r}
tiff(here("1_TADS_Parents_PP", "Figs_Tables", "Covariate_Joint_ORL_Bias",
          "T1_parent_Anx_Dep_SUD", "Supplement_2 Parameter Recovery.tiff"),
     width = 3.4, height = 7, units = "cm", res = 300)
  group_differences %>% 
    ggplot(aes(x = estimate, fill = group)) +
      # geoms
      geom_density(alpha = .5, linewidth = .25) +
      geom_hline(yintercept = 0) +
      # scales
      scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
      scale_color_manual(values = c("black", "#E01818", "#2184DA", "#FFC107"),
                         limits = c("Con", "Anx", "Dep", "SUD")) +
      scale_fill_manual(values = c("black", "#E01818", "#2184DA", "#FFC107"),
                        limits = c("Con", "Anx", "Dep", "SUD")) +
      # themes
      labs(x = "Estimate") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black", size = 8),
            axis.ticks.x = element_line(color = "black"),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank(),
            axis.line.y = element_blank(),
            axis.title.y = element_blank(),
            legend.text = element_text(size = 6),
            legend.spacing.x = unit(.05, 'cm'),
            legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.05, "lines"),
            legend.position = c(.125, .125),
            legend.background = element_rect(fill = "transparent", colour = "transparent"),
            legend.title = element_blank(),
            plot.margin = unit(c(.05, .2, 0, .5), "cm"),
            panel.spacing.x = unit(.3, "cm"),
            panel.spacing.y = unit(.1, "cm"),
            strip.text = element_blank(),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_wrap(parameter~., nrow = 4, ncol = 1,
                     scales = "free") +
      facetted_pos_scales(x = x_scaling) +
      guides(fill = guide_legend(nrow = 2))
  
    grid.text(c(expression(paste(italic(A),"+",sep="")),
                expression(paste(italic(A),"-",sep="")),
                expression(paste("\u03B2",italic(f),sep="")),
                expression(paste("\u03B2",italic(b),sep=""))),
              x = rep(.93, 4), y = c(.92, .68, .45, .21),
              gp = gpar(fontsize = 9.5))
dev.off()
```



# ---------------------------------------







