---
title: "Fitting Binomial Model"
output: html_document
date: "2023-03-07"
---



# -------------------------------------------
# Setup
## Load Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggpubr)
library(ggh4x)
library(rstan)
library(hBayesDM)
library(bayesplot)
library(here)
library(miscTools)
library(cmdstanr)
library(stringi)
library(ggpp)
library(lemon)
library(grid)
library(egg)
# source(here("Code", "R", "3_Other", "helpful_functions.R"))
```



## RMD Setup
```{r}
sample = "T1_parent_SU_Dep_Anx"

stan_data = readRDS(here("1_TADS_Parents_PP", "Data", "1_Stan",
                         paste("design", sample, "Binomial", "IGT.RDS", sep = "_")))
```



# -------------------------------------------
# Deck Model
## Setup
```{r, eval = F}
model_name = "Covariate_Deck_Binomial"
sample = "T1_parent_SU_Dep_Anx"

focal_parameters = c(
  "mu_A", "mu_B", "mu_C", "mu_D",
  "sigma_A", "sigma_B", "sigma_C", "sigma_D",
  "tilde_A", "tilde_B", "tilde_C", "tilde_D",
  "mu_A_theta", "mu_B_theta", "mu_C_theta", "mu_D_theta",
  "A_theta", "B_theta", "C_theta", "D_theta"
)


group_parameters <- grep("mu|sigma", focal_parameters, value=TRUE)
person_parameters <- grep("mu|sigma", focal_parameters, value=TRUE, invert=TRUE)
```



## Check Model
```{r, eval = F}
model_code = cmdstan_model(here("1_TADS_Parents_PP", "Code", "Stan", 
                                paste0(model_name, ".stan")), compile = F)

model_code$check_syntax(quiet = T)
```



## Fit Model
```{r, eval = F}
# Compile model
deck_model = stan_model(here("1_TADS_Parents_PP", "Code", "Stan",
                             paste0(model_name, ".stan")))
  

# -----------------------------------------------------------------------------------
# Fit model
deck_fit = sampling(deck_model, 
                    data   = stan_data, 
                    iter   = 5000, 
                    warmup = 1000, 
                    chains = 4, 
                    cores  = 4,
                    seed   = 43210,
                    save_warmup = F)
saveRDS(deck_fit, here("1_TADS_Parents_PP", "Data", "2_Fitted",
                       model_name,
                       paste(sample, model_name, "fit.rds", sep = "_")))

# -----------------------------------------------------------------------------------
# save posteriors
saveRDS(extract(deck_fit), here("1_TADS_Parents_PP", "Data", "2_Fitted",
                                    model_name,
                                    paste(sample, model_name, "posteriors.rds", sep = "_")))

# -----------------------------------------------------------------------------------
# save rhats
rhat(deck_fit, pars = focal_parameters) %>%
  data.frame() %>% mutate(parameter = rownames(.)) %>% 
  saveRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
               model_name,
               paste(sample, model_name, "rhats.rds", sep = "_")))
```



# -------------------------------------------
# Good/Bad Model
# ----------------
# Setup
```{r, eval = T}
model_name = "Covariate_Good_Bad_Binomial"
sample = "T1_parent_SU_Dep_Anx"

focal_parameters = c(
  "mu_good", "mu_bad",
  "sigma_good", "sigma_bad",
  "tilde_good", "tilde_bad",
  "mu_good_theta", "mu_bad_theta",
  "good_theta", "bad_theta"
)


group_parameters <- grep("mu|sigma", focal_parameters, value=TRUE)
person_parameters <- grep("mu|sigma", focal_parameters, value=TRUE, invert=TRUE)
```



# Model-Fitting
## Check Model
```{r, eval = F}
model_code = cmdstan_model(here("1_TADS_Parents_PP", "Code", "Stan", 
                                paste0(model_name, ".stan")), compile = F)

model_code$check_syntax(quiet = T)
```



## Fit Model
```{r, eval = F}
# Compile model
good_bad_model = stan_model(here("1_TADS_Parents_PP", "Code", "Stan",
                                 paste0(model_name, ".stan")))
  

# -----------------------------------------------------------------------------------
# Fit model
good_bad_fit = sampling(good_bad_model, 
                        data   = stan_data, 
                        iter   = 5000, 
                        warmup = 1000, 
                        chains = 4, 
                        cores  = 4,
                        seed   = 43210,
                        save_warmup = F)
saveRDS(good_bad_fit, here("1_TADS_Parents_PP", "Data", "2_Fitted",
                           model_name,
                           paste(sample, model_name, "fit.rds", sep = "_")))

# -----------------------------------------------------------------------------------
# save posteriors
saveRDS(extract(good_bad_fit), here("1_TADS_Parents_PP", "Data", "2_Fitted",
                                    model_name,
                                    paste(sample, model_name, "posteriors.rds", sep = "_")))

# -----------------------------------------------------------------------------------
# save rhats
rhat(good_bad_fit, pars = focal_parameters) %>%
  data.frame() %>% mutate(parameter = rownames(.)) %>% 
  saveRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
               model_name,
               paste(sample, model_name, "rhats.rds", sep = "_")))
```



# Process Model Data
## Import Data
```{r}
# subset participant to exclude
sub_keep = stan_data$ID_participant[stan_data$X[,1] == 0]

model_name = "Covariate_Good_Bad_Binomial"

# -----------------------------------------------------------------------------------
# read in model fit
good_bad_fit = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                            model_name,
                            paste(sample, model_name, "fit.rds", sep = "_")))

# -----------------------------------------------------------------------------------
# read in posteriors
good_bad_posteriors = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                                   model_name,
                                   paste(sample, model_name, "posteriors.rds", sep = "_")))

# -----------------------------------------------------------------------------------
# read in rhats
good_bad_rhats = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                              model_name,
                              paste(sample, model_name, "rhats.rds", sep = "_")))
```



## Prep Data
### Group-Level Data
```{r, eval = T}
good_bad_grp_thetas = data.frame(iteration = 1:((good_bad_fit@sim$iter -
                                                   good_bad_fit@sim$warmup) *
                                                  good_bad_fit@sim$chains),
                                 good_mu = good_bad_posteriors$mu_good_theta,
                                 good_beta = good_bad_posteriors$mu_good,
                                 bad_mu = good_bad_posteriors$mu_bad_theta,
                                 bad_beta = good_bad_posteriors$mu_bad) %>% 
  pivot_longer(starts_with(c("good", "bad")), names_to = c("valence", "group"),
               values_to = "estimate", names_sep = "\\.") %>% 
  filter(!(str_detect(valence, "beta") & group == 1)) %>% 
  separate(col = "valence", into = c("valence", "parameter"), sep = "_") %>% 
  mutate(group = case_when(group == 1 & parameter == "mu" ~ "Con",
                           group == 2 & parameter == "mu" ~ "SU",
                           group == 3 & parameter == "mu" ~ "Dep",
                           group == 4 & parameter == "mu" ~ "Anx",
                           group == 2 & parameter == "beta" ~ "SU-Con",
                           group == 3 & parameter == "beta" ~ "Dep-Con",
                           group == 4 & parameter == "beta" ~ "Anx-Con")) %>% 
  group_by(valence, parameter, group) %>% 
  mutate(mu = mean(estimate),
         lower = HDIofMCMC(estimate)[1],
         upper = HDIofMCMC(estimate)[2],
         valence = factor(valence, levels = c("good", "bad"), ordered = T),
         group = factor(group, levels = c("Con", "SU", "Dep", "Anx",
                                          "SU-Con", "Dep-Con", "Anx-Con")),
         group_mean = case_when(group %in% c("Con", "SU", "Dep", "Anx") ~ group,
                                T ~ "Comparison"),
         group_mean = factor(group_mean, ordered = T,
                             levels = c("Con", "SU", "Dep", "Anx", "Comparison")),
         comparison = case_when(group %in% c("Con", "SU", "Dep", "Anx") ~ "Group Mean",
                                T ~ group),
         comparison = factor(comparison, ordered = T,
                             levels = c("Group Mean", "SU-Con", "Dep-Con", "Anx-Con")))
```



### Individual-Subject Data
```{r, eval = T}
good_bad_ind_data = data.frame(ID = stan_data$ID_OG,
                               ID_participant = stan_data$ID_participant,
                               SU = stan_data$X[,2],
                               Dep = stan_data$X[,3],
                               Anx = stan_data$X[,4],
                               obs_good = (stan_data$C_plays +
                                           stan_data$D_plays) /
                                          (stan_data$C_trials +
                                           stan_data$D_trials),
                               obs_bad = (stan_data$A_plays +
                                          stan_data$B_plays) /
                                         (stan_data$A_trials +
                                          stan_data$B_trials),
                               pred_good = apply(good_bad_posteriors$good_pred, 2, mean) /
                                 (stan_data$C_trials + stan_data$D_trials),
                               pred_bad = apply(good_bad_posteriors$bad_pred, 2, mean) /
                                 (stan_data$A_trials + stan_data$B_trials)) %>% 
  pivot_longer(ends_with(c("good", "bad")), names_to = c("type", "valence"),
               values_to = "estimate", names_sep = "_") %>% 
  pivot_wider(names_from = "type", values_from = "estimate")
```



# Distribution Plots
## Group-Level Posterior Distributions
```{r}
# build plot
good_bad_group_plot = good_bad_grp_thetas %>% 
  filter(comparison == "Group Mean") %>% 
  mutate(valence = factor(valence, levels = c("good", "bad"),
                            ordered = T)) %>% 
  ggplot(aes(x = estimate, fill = group)) +
    # geoms
    geom_text_npc(data = data.frame(valence = factor(c("good", "bad"), ordered = T),
                                    lab_ = c("Good", "Bad")),
                  aes(label = lab_), npcx = 1, npcy = .5, angle = 270, size = 4, vjust = 1) +
    geom_density(alpha = .5, linewidth = .25) +
    geom_hline(yintercept = 0) +
    # scales
    scale_x_continuous(limits = c(.55,.95), expand = c(0, 0), breaks = seq(.6, .9, .1)) +
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
    scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9", "#009E73"),
                      limits = c("Con", "SU", "Dep", "Anx")) +
    # themes
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          axis.title = element_blank(),
          legend.text = element_text(size = 6),
          legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.05, "lines"),
          legend.position = c(.25, .75),
          legend.background = element_rect(fill = "transparent", colour = "transparent"),
          legend.title = element_blank(),
          plot.margin = unit(c(0, .2, 0, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(-.25, "cm"),
          strip.text = element_blank(),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_grid(valence~., scales = "free",
                   labeller = labeller(valence = c("good" = "Good", "bad" = "Bad")))# +
    # guides(fill = guide_legend(nrow = 2))
```



## Make Person-Level Plots
```{r}
make_plot = function(data, grp_diag, grp_color = "gray45",
                     good_lab = NA_character_, bad_lab = NA_character_) {
  colnames(data)[colnames(data)==grp_diag] = "group"
  
  plot = data %>% 
    mutate(valence = factor(valence, levels = c("good", "bad"), labels = c("Good", "Bad"),
                            ordered = T),
           lab_ = case_when(valence == "Good" ~ grp_diag, T ~ NA_character_)) %>%
           # lab_ = case_when(valence == "Good" ~ good_lab, T ~ bad_lab)) %>% 
    filter(group == 1) %>% 
    ggplot() +
    # geoms
    geom_text_npc(aes(label = lab_), npcx = 0, npcy = 1) +
    geom_histogram(aes(x = obs, y = ..density..), color = "black", fill = grp_color,
                   alpha = .5, linewidth = .25) +
    geom_density(aes(x = pred), fill = grp_color, linewidth = .5, alpha = .5) +
    # scales
    scale_x_continuous(limits = c(0, 1), expand = c(0, 0), breaks = seq(0, 1, .25),
                       labels = c("0", ".25", ".50", ".75", "1")) +
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05))) +
    # themes
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.x = element_line(color = "black"),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          axis.title = element_blank(),
          legend.text = element_text(size = 6),
          legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.1, "lines"),
          legend.position = c(.1, .945), legend.direction = "vertical",
          legend.background = element_rect(fill = "transparent", colour = "transparent"),
          legend.title = element_blank(),
          plot.margin = unit(c(0, .2, 0, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(-.25, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_grid(valence~., scales = "free")
    
  return(plot)
}
```



## Combine & Save Plots
```{r}
# -----------------------------------------------------------------------------------
# save plot
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name,
          paste(sample, "Distribution Plots.tiff", sep = " ")),
     width = 14.6, height = 4, units = "cm", res = 300)
  
  grid.newpage()
  # main plot
  pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
  grid.draw(ggarrange(make_plot(good_bad_ind_data, "SU",  "#E69F00", "Good", "Bad"),
                      make_plot(good_bad_ind_data, "Dep", "#56B4E9"),
                      make_plot(good_bad_ind_data, "Anx", "#009E73"),
                      good_bad_group_plot,
                      ncol = 4) %>% 
               annotate_figure(left = textGrob("Density", rot = 90, hjust = .5),
                              bottom = textGrob("Estimate")))
  
dev.off()
```



## -----------
## SU
### Person-Level Plots
```{r}
SU_ind_plot = 
  good_bad_ind_data %>% 
  mutate(valence = factor(valence, levels = c("good", "bad"), labels = c("Good", "Bad"),
                          ordered = T),
         SU = factor(SU)) %>% 
  ggplot(aes(fill = SU)) +
    # geoms
    geom_histogram(aes(x = obs, y = ..density..), color = "black",
                   linewidth = .1, bins = 75) +
    geom_density(aes(x = pred, color = SU), linewidth = .5) +
    # scales
    scale_x_continuous(limits = c(0, 1), expand = c(0, 0), breaks = seq(0, 1, .25),
                       labels = c("0", ".25", ".50", ".75", "1")) +
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05))) +
    scale_fill_manual(values = alpha(c("gray45", "goldenrod3"), alpha = .5),
                      labels = c("Con", "SU")) +
    scale_color_manual(values = alpha(c("gray45", "goldenrod3"), alpha = .5),
                      labels = c("Con", "SU")) +
    # themes
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.x = element_line(color = "black"),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          legend.text = element_text(size = 6),
          legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.1, "lines"),
          legend.position = c(.1, .945), legend.direction = "vertical",
          legend.background = element_rect(fill = "transparent", colour = "transparent"),
          legend.title = element_blank(),
          plot.margin = unit(c(.5, .5, .3, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(.5, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(valence~., scales = "free",
                   nrow = 2, ncol = 1)
# -----------------------------------------------------------------------------------
# save plot
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name,
          paste(sample, "Con-SU Ind Distributions.tiff", sep = " ")),
     width = 6, height = 6, units = "cm", res = 300)
  
  grid.newpage()
  # main plot
  pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
  grid.draw(SU_ind_plot)
  # popViewport()
  
dev.off()
```



### Group-Level Plots
```{r}
# -----------------------------------------------------------------------------------
# Mu Plots
# prep specific data for this plot
SU_mus_plot =
  good_bad_grp_thetas %>% 
  filter(group %in% c("Con", "SU")) %>% 
  mutate(valence = factor(valence, levels = c("good", "bad"), labels = c("Good", "Bad"),
                          ordered = T)) %>% 
  # build plot
  ggplot(aes(x = estimate, fill = group)) +
    # geoms
    geom_density(alpha = .5) +
    geom_hline(yintercept = 0) +
    # scales
    scale_x_continuous(limits = c(.5, 1), expand = c(0, 0), breaks = seq(.5,1, .25)) +
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
    scale_fill_manual(values = alpha(c("gray45", "goldenrod3"), alpha = .5)) +
    # themes
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10, vjust = 3),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          legend.text = element_text(size = 7),
          legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.1, "lines"),
          legend.position = c(.1, .925), legend.direction = "vertical",
          legend.background = element_rect(fill = "transparent", colour = "transparent"),
          legend.title = element_blank(),
          plot.margin = unit(c(.125, .4, .2, .125), "cm"),
          panel.spacing.y = unit(0, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(valence~., scales = "free",
                   nrow = 2, ncol = 1)
# -----------------------------------------------------------------------------------
# Good Beta Plot
# prep specific data for this plot
SU_good_beta_plot =
  good_bad_grp_thetas %>% 
  filter(group == "SU-Con" & valence == "good") %>% 
  # build plot
  ggplot(aes(x = estimate)) +
    # geoms
    geom_density(fill = "gray45", linewidth = .25) +
    geom_hline(yintercept = 0) +
    geom_vline(aes(xintercept = mu), color = "red2", linewidth = .25) +
    geom_vline(aes(xintercept = lower), color = "red", linetype = "dashed", linewidth = .25) +
    geom_vline(aes(xintercept = upper), color = "red", linetype = "dashed", linewidth = .25) +
    # scales
    scale_x_continuous(breaks = 0) +
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
    # themes
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black", size = 6),
          axis.title = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.margin = unit(c(.1, .4, .2, .1), "cm"),
          panel.spacing.y = unit(0, "cm"),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent"))
# -----------------------------------------------------------------------------------
# Bad Beta Plot
# prep specific data for this plot
SU_bad_beta_plot =
  good_bad_grp_thetas %>% 
  filter(group == "SU-Con" & valence == "bad") %>% 
  # build plot
  ggplot(aes(x = estimate)) +
    # geoms
    geom_density(fill = "gray45", linewidth = .25) +
    geom_hline(yintercept = 0) +
    geom_vline(aes(xintercept = mu), color = "red2", linewidth = .25) +
    geom_vline(aes(xintercept = lower), color = "red", linetype = "dashed", linewidth = .25) +
    geom_vline(aes(xintercept = upper), color = "red", linetype = "dashed", linewidth = .25) +
    # scales
    scale_x_continuous(breaks = 0) +
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
    # themes
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black", size = 6),
          axis.title = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.margin = unit(c(.1, .4, .2, .1), "cm"),
          panel.spacing.y = unit(0, "cm"),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent"))
# -----------------------------------------------------------------------------------
# save plot
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name,
          paste(sample, "Con-SU Mus & Beta Posterior Distributions.tiff", sep = " ")),
     width = 4, height = 6, units = "cm", res = 300)
  
  grid.newpage()
  # main plot
  grid.draw(ggplotGrob(SU_mus_plot))
  
  # top inset
  pushViewport(viewport(x = .825, y = .8, width = .375, height = .2))
  grid.draw(ggplotGrob(SU_good_beta_plot))
  popViewport()
  
  # bottom inset
  pushViewport(viewport(x = .825, y = .35, width = .375, height = .2))
  grid.draw(ggplotGrob(SU_bad_beta_plot))
  
  popViewport()
  
dev.off()
```



## -----------
## Dep
### Person-Level Plots
```{r}
Dep_ind_plot = 
  good_bad_ind_data %>% 
  mutate(valence = factor(valence, levels = c("good", "bad"), labels = c("Good", "Bad"),
                          ordered = T)) %>% 
  ggplot() +
    # geoms
    geom_histogram(aes(x = obs, y = ..density.., fill = factor(Dep)), color = "black",
                   linewidth = .1, bins = 75,) +
    geom_density(aes(x = pred, fill = factor(Dep)), linewidth = .5) +
    # scales
    scale_x_continuous(limits = c(0, 1), expand = c(0, 0), breaks = seq(0, 1, .25),
                       labels = c("0", ".25", ".50", ".75", "1")) +
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05))) +
    scale_fill_manual(values = alpha(c("gray45", "goldenrod3"), alpha = .5),
                      labels = c("Con", "Dep")) +
    # themes
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          legend.text = element_text(size = 6),
          legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.1, "lines"),
          legend.position = c(.1, .945), legend.direction = "vertical",
          legend.background = element_rect(fill = "transparent", colour = "transparent"),
          legend.title = element_blank(),
          plot.margin = unit(c(.5, .5, .3, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(.5, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(valence~factor(Dep), scales = "free",
                   nrow = 2, ncol = 2)
# -----------------------------------------------------------------------------------
# save plot
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name,
          paste(sample, "Con-Dep Ind Distributions.tiff", sep = " ")),
     width = 6, height = 6, units = "cm", res = 300)
  
  grid.newpage()
  # main plot
  pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
  grid.draw(Dep_ind_plot)
  # popViewport()
  
dev.off()
```



### Group-Level Plots
```{r}
# -----------------------------------------------------------------------------------
# Mu Plots
# prep specific data for this plot
Dep_mus_plot =
  good_bad_grp_thetas %>% 
  filter(group %in% c("Con", "Dep")) %>% 
  mutate(valence = factor(valence, levels = c("good", "bad"), labels = c("Good", "Bad"),
                          ordered = T)) %>% 
  # build plot
  ggplot(aes(x = estimate, fill = group)) +
    # geoms
    geom_density(alpha = .5) +
    geom_hline(yintercept = 0) +
    # scales
    scale_x_continuous(limits = c(.5, 1), expand = c(0, 0), breaks = seq(.5,1, .25)) +
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
    scale_fill_manual(values = alpha(c("gray45", "goldenrod3"), alpha = .5)) +
    # themes
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10, vjust = 3),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          legend.text = element_text(size = 7),
          legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.1, "lines"),
          legend.position = c(.1, .925), legend.direction = "vertical",
          legend.background = element_rect(fill = "transparent", colour = "transparent"),
          legend.title = element_blank(),
          plot.margin = unit(c(.125, .4, .2, .125), "cm"),
          panel.spacing.y = unit(0, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(valence~., scales = "free",
                   nrow = 2, ncol = 1)
# -----------------------------------------------------------------------------------
# Good Beta Plot
# prep specific data for this plot
Dep_good_beta_plot =
  good_bad_grp_thetas %>% 
  filter(group == "Dep-Con" & valence == "good") %>% 
  # build plot
  ggplot(aes(x = estimate)) +
    # geoms
    geom_density(fill = "gray45", linewidth = .25) +
    geom_hline(yintercept = 0) +
    geom_vline(aes(xintercept = mu), color = "red2", linewidth = .25) +
    geom_vline(aes(xintercept = lower), color = "red", linetype = "dashed", linewidth = .25) +
    geom_vline(aes(xintercept = upper), color = "red", linetype = "dashed", linewidth = .25) +
    # scales
    scale_x_continuous(breaks = 0) +
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
    # themes
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black", size = 6),
          axis.title = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.margin = unit(c(.1, .4, .2, .1), "cm"),
          panel.spacing.y = unit(0, "cm"),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent"))
# -----------------------------------------------------------------------------------
# Bad Beta Plot
# prep specific data for this plot
Dep_bad_beta_plot =
  good_bad_grp_thetas %>% 
  filter(group == "Dep-Con" & valence == "bad") %>% 
  # build plot
  ggplot(aes(x = estimate)) +
    # geoms
    geom_density(fill = "gray45", linewidth = .25) +
    geom_hline(yintercept = 0) +
    geom_vline(aes(xintercept = mu), color = "red2", linewidth = .25) +
    geom_vline(aes(xintercept = lower), color = "red", linetype = "dashed", linewidth = .25) +
    geom_vline(aes(xintercept = upper), color = "red", linetype = "dashed", linewidth = .25) +
    # scales
    scale_x_continuous(breaks = 0) +
    scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
    # themes
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black", size = 6),
          axis.title = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.margin = unit(c(.1, .4, .2, .1), "cm"),
          panel.spacing.y = unit(0, "cm"),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent"))
# -----------------------------------------------------------------------------------
# save plot
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name,
          paste(sample, "Con-Dep Mus & Beta Posterior Distributions.tiff", sep = " ")),
     width = 4, height = 6, units = "cm", res = 300)
  
  grid.newpage()
  # main plot
  grid.draw(ggplotGrob(Dep_mus_plot))
  
  # top inset
  pushViewport(viewport(x = .825, y = .8, width = .375, height = .2))
  grid.draw(ggplotGrob(Dep_good_beta_plot))
  popViewport()
  
  # bottom inset
  pushViewport(viewport(x = .825, y = .35, width = .375, height = .2))
  grid.draw(ggplotGrob(Dep_bad_beta_plot))
  
  popViewport()
  
dev.off()
```



















