---
title: "Manuscript Plots"
output: 
  html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: true
---


```{css, echo = F}
#TOC {
    max-width: fit-content;
    white-space: nowrap;
  }
  
  div:has(> #TOC) {
    display: flex;
    flex-direction: row-reverse;
}
div.tocify {
width: 100%;
}
```


# -------------------------------------------
# Setup
## Load Packages
```{r setup, include = F}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.align = "center")

library(tidyverse)
library(rstan)
library(hBayesDM)
library(bayesplot)
library(here)
library(miscTools)
library(cmdstanr)
library(stringi)
library(ggpp)
library(lemon)
library(MASS)
library(ggh4x)
library(grid)
library(extraDistr)
library(lme4)
library(kableExtra)
```


## Import Models
```{r}
conditions  = c("neg.beta_neg.cor", "neg.beta_neu.cor", "neg.beta_pos.cor",
                "neu.beta_neg.cor", "neu.beta_neu.cor", "neu.beta_pos.cor",
                "pos.beta_neg.cor", "pos.beta_neu.cor", "pos.beta_pos.cor")
conditions_labs = c("-.3 Beta & -.3 r", "-.3 Beta & 0 r", "-.3 Beta & +.3 r",
                    "0 Beta & -.3 r", "0 Beta & 0 r", "0 Beta & +.3 r",
                    "+.3 Beta & -.3 r", "+.3 Beta & 0 r", "+.3 Beta & +.3 r")
sim_numbers = 1:100

characteristics = data.frame()
diagnostics     = data.frame()
simulations     = data.frame()

for(condition in conditions){
  for(sim in sim_numbers){
    characteristics = bind_rows(characteristics,
                                readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                             paste0("RL_Characteristics_", sim, ".RDS"))),
                                readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                             paste0("HLCM_Characteristics_", sim, ".RDS"))))
    diagnostics = bind_rows(diagnostics,
                            readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                         paste0("RL_Diagnostics_", sim, ".RDS"))),
                            readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                         paste0("HLCM_Diagnostics_", sim, ".RDS")))) %>% 
      filter(!str_detect(parameter, "RL1|RL2|RL3"))
    simulations = bind_rows(simulations,
                            readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                         paste0("RL_Simulation_", sim, ".RDS"))),
                            readRDS(here("1_HLCM", "Data", "2_Fitted", condition,
                                         paste0("HLCM_Simulation_", sim, ".RDS")))) %>% 
      filter(!str_detect(parameter, "RL1|RL2|RL3"))
  }
}
```


```{r}
characteristics %>%
  group_by(hypermodel) %>% 
  summarise(avg = round(mean(as.numeric(duration, units = "mins")), 2),
            sd = round(sd(as.numeric(duration, units = "mins")), 2))
```


# -------------------------------------------
# Posterior Means
## Group-Level Growth Parameters
### Prep Data
```{r}
group_level_parameters = simulations %>% 
    filter(parameter_type == "group") %>%
    group_by(hypermodel, condition, parameter) %>% 
    mutate(mean_posterior_mean = mean(posterior_mean),
           mean_diff = mean(posterior_mean - true_value)) %>%
    mutate(hypermodel = factor(hypermodel, levels = c("RL", "HLCM"),
                               labels = c("Two-Stage", "HLCM"), ordered = T),
           parameter = factor(parameter, ordered = T,
                              levels = c("intercept", "slope", "int_slope_R", 
                                         "intercept_SD", "slope_SD", "residual_SD"),
                              labels = c("Intercept~(\u03B3[0][0])", "Slope~(\u03B3[1][0])", "Int-Slope~Cor~(\u03c1)",
                                         "Intercept~SD~(\u03c4[0][0])", "Slope~SD~(\u03c4[1][0])", "Residual~SD~(\u03c3)")),
           condition = factor(condition, ordered = T,
                              levels = conditions, 
                              labels = c(expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=+.3")),
                                         
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=+.3")),
                                         
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=+.3"))
                              )),
           mean_diff_x = case_when(parameter == "Residual~SD~(\u03c3)" ~ .25, T ~ .75),
           mean_diff_y = case_when(hypermodel == "Two-Stage" ~ 1.0, T ~ .95),
           cond_lab = case_when(parameter %in% c("Int-Slope~Cor~(\u03c1)", "Residual~SD~(\u03c3)") ~ condition))
```


### Group-Level Plot
```{r}
tiff(here("1_HLCM", "Figs_Tables", "1 - Distribution of Group-Level Growth Parameters.tiff"),
     width = 14.6, height = 16, units = "cm", res = 300)

  group_level_parameters %>% 
    filter(parameter %in% c("Intercept~(\u03B3[0][0])", "Slope~(\u03B3[1][0])", "Int-Slope~Cor~(\u03c1)")) %>%
    ggplot(aes(x = posterior_mean, fill = hypermodel)) +
      # GEOMS
      geom_histogram(color = "black", linewidth = .75, bins = 25) +
      geom_hline(yintercept = 0) +
      geom_vline(aes(xintercept = true_value), color = "red2", linewidth = .75) +
      geom_point(aes(x = mean_posterior_mean, y = 42.5),
                 shape = 21, size = 1.6, stroke = 1, show.legend = F) +
      geom_text(aes(x = .7, y = 30, label = cond_lab), parse = T, hjust = 0, check_overlap = T) +
      # SCALES
      scale_y_continuous(limits = c(0, 45), expand = c(0, 0), breaks = c(0, 15, 30, 45)) +
      scale_color_manual(values = c("goldenrod3", "dodgerblue3")) +
      scale_fill_manual(values = c("goldenrod3", "dodgerblue3")) +
      # THEMES
      labs(x = "Posterior Mean", y = "Frequency") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text = element_text(color = "black", size = 11),
            axis.ticks = element_line(color = "black", linewidth = .75),
            axis.line = element_line(linewidth = .75),
            axis.title = element_text(size = 14),
            legend.title = element_blank(),
            legend.position = c(.5, 1.085),
            legend.direction = "horizontal",
            plot.margin = unit(c(.85, 1.1, .1, .3), "cm"),
            panel.spacing = unit(.45, "cm"),
            strip.text.x= element_text(size = 12, hjust = 0),
            strip.text.y = element_blank(),
            strip.clip = "off",
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_grid(condition~parameter, scales = "free", labeller = label_parsed)
  
dev.off()
```


### SD Plot
```{r}
tiff(here("1_HLCM", "Figs_Tables", "2 - Distribution of SD Growth Parameters.tiff"),
     width = 14.6, height = 16, units = "cm", res = 300)

  group_level_parameters %>% 
    filter(parameter %in% c("Intercept~SD~(\u03c4[0][0])", "Slope~SD~(\u03c4[1][0])", "Residual~SD~(\u03c3)")) %>%
    ggplot(aes(x = posterior_mean, fill = hypermodel)) +
      # GEOMS
      geom_histogram(color = "black", linewidth = .75, bins = 25) +
      geom_hline(yintercept = 0) +
      geom_vline(aes(xintercept = true_value), color = "red2", linewidth = .75) +
      geom_point(aes(x = mean_posterior_mean, y = 42.5),
                 shape = 21, size = 1.6, stroke = 1, show.legend = F) +
      geom_text(aes(x = 1.75, y = 30, label = cond_lab), parse = T, hjust = 0, check_overlap = T) +
      # SCALES
      scale_y_continuous(limits = c(0, 45), expand = c(0, 0), breaks = c(0, 15, 30, 45)) +
      scale_color_manual(values = c("goldenrod3", "dodgerblue3")) +
      scale_fill_manual(values = c("goldenrod3", "dodgerblue3")) +
      # THEMES
      labs(x = "Posterior Mean", y = "Frequency") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text = element_text(color = "black", size = 11),
            axis.ticks = element_line(color = "black", linewidth = .75),
            axis.line = element_line(linewidth = .75),
            axis.title = element_text(size = 14),
            legend.title = element_blank(),
            legend.position = c(.5, 1.085),
            legend.direction = "horizontal",
            plot.margin = unit(c(.85, 1.1, .1, .3), "cm"),
            panel.spacing = unit(.45, "cm"),
            strip.text.x = element_text(size = 12, hjust = 0),
            strip.text.y = element_blank(),
            strip.clip = "off",
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_grid(condition~parameter, scales = "free", labeller = label_parsed)
  
dev.off()
```


### All Parameters Plot
```{r}
tiff(here("1_HLCM", "Figs_Tables", "1 - Distribution of All Group-Level Growth Parameters.tiff"),
     width = 14.6, height = 16, units = "cm", res = 300)

  group_level_parameters %>% 
    mutate(cond_lab = case_when(parameter == "Residual~SD~(\u03c3)" ~ condition)) %>% 
    ggplot(aes(x = posterior_mean, fill = hypermodel)) +
      # GEOMS
      geom_histogram(color = "black", linewidth = .25, bins = 25) +
      geom_hline(yintercept = 0) +
      geom_vline(aes(xintercept = true_value), color = "red2", linewidth = .75) +
      geom_point(aes(x = mean_posterior_mean, y = 42.5),
                 shape = 21, size = 1.6, stroke = 1, show.legend = F) +
      geom_text(aes(x = 1.75, y = 30, label = cond_lab), size = 3,
                parse = T, hjust = .35, check_overlap = T) +
      # geom_text_npc(aes(npcx = mean_diff_x, npcy = mean_diff_y, label = paste0("MD=", round(mean_diff, 2)),
      #                   color = hypermodel), size = 2, hjust = .5, check_overlap = T) +
      # SCALES
      scale_y_continuous(limits = c(0, 45), expand = c(0, 0), breaks = c(0, 15, 30, 45)) +
      scale_color_manual(values = c("goldenrod3", "dodgerblue3")) +
      scale_fill_manual(values = c("goldenrod3", "dodgerblue3")) +
      # THEMES
      labs(x = "Posterior Mean", y = "Frequency") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text = element_text(color = "black", size = 8),
            axis.ticks = element_line(color = "black", linewidth = .75),
            axis.line = element_line(linewidth = .75),
            axis.title = element_text(size = 12),
            legend.title = element_blank(),
            legend.position = c(.5, 1.075),
            legend.direction = "horizontal",
            plot.margin = unit(c(.75, .5, .1, .15), "cm"),
            panel.spacing.x = unit(.2, "cm"),
            panel.spacing.y = unit(.35, "cm"),
            strip.text.x = element_text(size = 8, hjust = .25),
            strip.text.y = element_blank(),
            strip.clip = "off",
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_grid(condition~parameter, scales = "free", labeller = label_parsed)
  
dev.off()
```


### Visually Displaying All Parameters
```{r}
tiff(here("1_HLCM", "Figs_Tables", "0 - Distribution of All Group-Level Growth Parameters.tiff"),
     width = 25, height = 50, units = "cm", res = 300)

  group_level_parameters %>% 
    mutate(cond_lab = case_when(parameter == "Residual~SD~(\u03c3)" ~ condition)) %>% 
    ggplot(aes(x = posterior_mean, fill = hypermodel)) +
      # GEOMS
      geom_histogram(color = "black", linewidth = .25, bins = 25) +
      geom_hline(yintercept = 0) +
      geom_vline(aes(xintercept = true_value), color = "red2", linewidth = .75) +
      geom_point(aes(x = mean_posterior_mean, y = 42.5),
                 shape = 21, size = 1.6, stroke = 1, show.legend = F) +
      # SCALES
      scale_y_continuous(limits = c(0, NA)) +
      scale_color_manual(values = c("goldenrod3", "dodgerblue3")) +
      scale_fill_manual(values = c("goldenrod3", "dodgerblue3")) +
      # THEMES
      labs(x = "Posterior Mean", y = "Frequency") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text = element_text(color = "black", size = 8),
            axis.ticks = element_line(color = "black", linewidth = .75),
            axis.line = element_line(linewidth = .75),
            axis.title = element_text(size = 12),
            legend.title = element_blank(),
            legend.position = c(.5, 1.075),
            legend.direction = "horizontal",
            plot.margin = unit(c(1.5, .5, .1, .15), "cm"),
            panel.spacing.x = unit(.2, "cm"),
            panel.spacing.y = unit(.35, "cm"),
            strip.text = element_text(size = 8),
            strip.clip = "off",
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_wrap(condition~parameter, scales = "free", labeller = label_parsed, ncol = 6)
  
dev.off()
```


## Person-Level Parameters
### Define Aspects of Plot
```{r}
correlations = simulations %>% 
  filter(parameter_type != "group") %>%
  group_by(simulation, condition, hypermodel, parameter) %>% 
  reframe(r = cor(true_value, posterior_mean)) %>% 
  mutate(hypermodel = factor(hypermodel, levels = c("RL", "HLCM"),
                             labels = c("Two-Stage", "HLCM"), ordered = T),
         parameter = factor(parameter, ordered = T,
                            levels = c("intercept", "slope", "unbounded_A", "A"),
                            labels = c("Intercept~(\u03B2[0])", "Slope~(\u03B2[1])", "Unbounded~A", "A")),
         condition = factor(condition, ordered = T,
                            levels = conditions, 
                            labels = c(expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=-.3")),
                                       expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=0")),
                                       expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=+.3")),
                                       
                                       expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=-.3")),
                                       expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=0")),
                                       expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=+.3")),
                                       
                                       expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=-.3")),
                                       expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=0")),
                                       expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=+.3"))
                            )),
         cond_lab = case_when(parameter == "A" ~ condition))

mean_correlation = correlations %>% 
  group_by(hypermodel, condition, parameter) %>%
  reframe(mean_r = mean(r)) %>% 
  mutate(hypermodel = case_when(hypermodel == "HLCM" ~ "HLCM", T ~ "Two_Stage")) %>% 
  pivot_wider(names_from = "hypermodel", values_from = "mean_r")
```


### True v Est Correlation Plot
```{r}
tiff(here("1_HLCM", "Figs_Tables", "3 - Correlation Bw True & Estimated Parameters.tiff"),
     width = 14.6, height = 16, units = "cm", res = 300)

  correlations %>% 
    ggplot(aes(x = r, fill = hypermodel)) +
      # GEOMS
      geom_vline(data = mean_correlation, aes(xintercept = Two_Stage), color = "goldenrod3",
                 show.legend = F) +
      geom_vline(data = mean_correlation, aes(xintercept = HLCM), color = "dodgerblue3",
                 show.legend = F) +
      geom_histogram(color = "black", linewidth = .25, bins = 50) +
      geom_hline(yintercept = 0) +
      geom_text_npc(data = mean_correlation, color = "goldenrod4", size = 2.5, inherit.aes = F, hjust = 0,
                aes(npcx = "left", npcy = 1, label = paste0("r = ", round(Two_Stage, 2)))) +
      geom_text_npc(data = mean_correlation, color = "dodgerblue4", size = 2.5, inherit.aes = F, hjust = 0,
                aes(npcx = "left", npcy = .7, label = paste0("r = ", round(HLCM, 2)))) +
      geom_text_npc(aes(npcx = "right", npcy = 1.1, label = cond_lab), parse = T, hjust = -.1, check_overlap = T) +
      # SCALES
      scale_x_continuous(limits = c(-1,1), expand = expansion(mult = .05),
                         breaks = c(-1, 0, 1), labels = c("-1", "0", "+1")) +
      scale_y_continuous(limits = c(0, NA), expand = c(0, 0), n.breaks = 3) +
      scale_color_manual(values = c("goldenrod3", "dodgerblue3")) +
      scale_fill_manual(values = c("goldenrod3", "dodgerblue3")) +
      # THEMES
      labs(x = "Correlation Between True & Estimated Parameter", y = "Frequency") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text = element_text(color = "black", size = 11),
            axis.ticks = element_line(color = "black", linewidth = .75),
            axis.line = element_line(linewidth = .75),
            axis.title = element_text(size = 14),
            legend.title = element_blank(),
            legend.position = c(.5, 1.085),
            legend.direction = "horizontal",
            plot.margin = unit(c(.75, 1.35, .1, .3), "cm"),
            panel.spacing.x = unit(.4, "cm"),
            panel.spacing.y = unit(.375, "cm"),
            strip.text.x = element_text(size = 12, hjust = 0),
            strip.text.y = element_blank(),
            strip.clip = "off",
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_grid(condition~parameter, scales = "free", labeller = label_parsed)
  
dev.off()
```


# -------------------------------------------
# True in HDI
## Group-Level Growth Parameters
```{r}
tiff(here("1_HLCM", "Figs_Tables", "4 - Percent Group-Level Growth Parameters in HDIs.tiff"),
     width = 7, height = 15, units = "cm", res = 300)

  simulations %>% 
    filter(parameter_type == "group") %>%
    group_by(condition, parameter, hypermodel) %>% 
    summarise(true_in_HDI95 = mean(true_in_HDI95)*100) %>% 
    mutate(hypermodel = factor(hypermodel, levels = c("RL", "HLCM"),
                               labels = c("Two-Stage", "HLCM"), ordered = T),
           parameter = factor(parameter, ordered = T,
                              levels = c("intercept", "slope", "int_slope_R", 
                                         "intercept_SD", "slope_SD", "residual_SD")),
           condition = factor(condition, ordered = T,
                              levels = conditions, 
                              labels = c(expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=+.3")),
                                         
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=+.3")),
                                         
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=+.3"))
                              ))) %>% 
    ggplot(aes(x = parameter, y = true_in_HDI95, fill = hypermodel)) +
      # GEOMS
      geom_bar(color = "black", linewidth = .75, stat = "identity") +
      # geom_text(aes(label = paste0(round(true_in_HDI95), "%")),
      #           vjust = .5, hjust = -.125, size = 2, angle = 90) +
      # SCALES
      scale_x_discrete(labels = parse(text = c("Intercept~(\u03B3[0][0])", "Slope~(\u03B3[1][0])",
                                               "Int-Slope~Cor~(\u03c1)", "Intercept~SD~(\u03c4[0][0])",
                                               "Slope~SD~(\u03c4[1][0])", "Residual~SD~(\u03c3)"))) +
      scale_y_continuous(limits = c(0,100), expand = c(0,0), 
                         breaks = seq(0, 100, 50), labels = c("0%", "50%", "100%")) +
      scale_fill_manual(values = c("goldenrod3", "dodgerblue3")) +
      # THEMES
      labs(y = "Percent of HDIs Encompassing True Parameter") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black", size = 8, angle = 90, vjust = .5, hjust = 1),
            axis.text.y = element_text(color = "black", size = 8),
            axis.ticks = element_line(color = "black", linewidth = .75),
            axis.line = element_line(linewidth = .75),
            axis.title.y = element_text(size = 12),
            axis.title.x = element_blank(),
            legend.position = "none",
            plot.margin = unit(c(.1,0, .1, .2), "cm"),
            panel.spacing.x = unit(.25, "cm"),
            panel.spacing.y = unit(.375, "cm"),
            strip.text.y = element_text(angle = 0),
            strip.clip = "off",
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_grid(condition~hypermodel, labeller = label_parsed)

dev.off()
```


## Person-Level Parameters
```{r}
tiff(here("1_HLCM", "Figs_Tables", "5 - Percent Person-Level Parameters in HDIs.tiff"),
     width = 7, height = 15, units = "cm", res = 300)

  simulations %>% 
    filter(parameter_type != "group") %>%
    group_by(condition, parameter, hypermodel) %>% 
    summarise(true_in_HDI95 = mean(true_in_HDI95)*100) %>%
    mutate(hypermodel = factor(hypermodel, levels = c("RL", "HLCM"),
                               labels = c("Two-Stage", "HLCM"), ordered = T),
           parameter = factor(parameter, ordered = T,
                              levels = c("intercept", "slope", "unbounded_A", "A")),
           condition = factor(condition, ordered = T,
                              levels = conditions, 
                              labels = c(expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=+.3")),
                                         
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=+.3")),
                                         
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=+.3"))
                              ))) %>% 
    ggplot(aes(x = parameter, y = true_in_HDI95, fill = hypermodel)) +
      # GEOMS
      geom_bar(color = "black", linewidth = .75, stat = "identity") +
      # geom_text(aes(label = paste0(round(true_in_HDI95), "%")),
      #           vjust = .5, hjust = -.125, size = 2, angle = 90) +
      # SCALES
      scale_x_discrete(labels = parse(text = c("Intercept~(\u03B2[0])", "Slope~(\u03B2[1])", "Unbounded~A", "A"))) +
      scale_y_continuous(limits = c(0,100), expand = c(0,0), 
                         breaks = seq(0, 100, 50), labels = c("0%", "50%", "100%")) +
      scale_fill_manual(values = c("goldenrod3", "dodgerblue3")) +
      # THEMES
      labs(y = "Percent of HDIs Encompassing True Parameter") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black", size = 8, angle = 90, vjust = .5, hjust = 1),
            axis.text.y = element_text(color = "black", size = 8),
            axis.ticks = element_line(color = "black", linewidth = .75),
            axis.line = element_line(linewidth = .75),
            axis.title.y = element_text(size = 12),
            axis.title.x = element_blank(),
            legend.position = "none",
            plot.margin = unit(c(.1,0, .1, .2), "cm"),
            panel.spacing.x = unit(.25, "cm"),
            panel.spacing.y = unit(.375, "cm"),
            strip.text.y = element_text(angle = 0),
            strip.clip = "off",
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_grid(condition~hypermodel, labeller = label_parsed)

dev.off()
```


# -------------------------------------------
# Percentiles
## Group-Level Growth Parameters
```{r}
tiff(here("1_HLCM", "Figs_Tables", "S1 - Distribution of All Group-Level Growth Parameter Percentiles.tiff"),
     width = 20, height = 20, units = "cm", res = 300)

  group_level_parameters %>% 
    mutate(cond_lab = case_when(parameter == "Residual~SD~(\u03c3)" ~ condition)) %>% 
    ggplot(aes(x = percentile, fill = hypermodel)) +
      # GEOMS
      geom_histogram(color = "black", linewidth = .25, bins = 25) +
      geom_hline(yintercept = 0) +
      geom_text(aes(x = .95, y = 30, label = cond_lab), size = 3.5,
                parse = T, hjust = .35, check_overlap = T) +
      # SCALES
      scale_x_continuous(limits = c(0, 1), breaks = c(0, .5, 1)) +
      scale_y_continuous(limits = c(0, 40), expand = c(0, 0)) +
      scale_color_manual(values = c("goldenrod3", "dodgerblue3")) +
      scale_fill_manual(values = c("goldenrod3", "dodgerblue3")) +
      # THEMES
      labs(x = "Percentile", y = "Frequency") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text = element_text(color = "black", size = 10),
            axis.ticks = element_line(color = "black", linewidth = .75),
            axis.line = element_line(linewidth = .75),
            axis.title = element_text(size = 12),
            legend.title = element_blank(),
            legend.position = c(.5, 1.065),
            legend.direction = "horizontal",
            plot.margin = unit(c(1, .5, .1, .15), "cm"),
            panel.spacing.x = unit(.25, "cm"),
            panel.spacing.y = unit(.35, "cm"),
            strip.text.x = element_text(size = 10, hjust = .25),
            strip.text.y = element_blank(),
            strip.clip = "off",
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_grid(condition~parameter, scales = "free", labeller = label_parsed)
  
dev.off()
```


## Person-Level Growth Parameters
```{r}
tiff(here("1_HLCM", "Figs_Tables", "S2 - Distribution of All Person-Level Growth Parameter Percentiles.tiff"),
     width = 20, height = 20, units = "cm", res = 300)

  simulations %>% 
    filter(parameter_type != "group") %>%
    mutate(hypermodel = factor(hypermodel, levels = c("RL", "HLCM"),
                               labels = c("Two-Stage", "HLCM"), ordered = T),
           parameter = factor(parameter, ordered = T,
                              levels = c("intercept", "slope", "unbounded_A", "A"),
                              labels = c("Intercept~(\u03B2[0])", "Slope~(\u03B2[1])", "Unbounded~A", "A")),
           condition = factor(condition, ordered = T,
                              levels = conditions, 
                              labels = c(expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=-.3","\n\u03c1=+.3")),
                                         
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=0  ","\n\u03c1=+.3")),
                                         
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=-.3")),
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=0")),
                                         expression(atop("\u03B3"["10"]*"=+.3","\n\u03c1=+.3"))
                              )),
           cond_lab = case_when(parameter == "A" ~ condition)) %>% 
    ggplot(aes(x = percentile, fill = hypermodel)) +
      # GEOMS
      geom_histogram(color = "black", linewidth = .25, bins = 25) +
      geom_hline(yintercept = 0) +
      geom_text(aes(x = .95, y = 1000, label = cond_lab), size = 3.5,
                parse = T, hjust = 0, check_overlap = T) +
      # SCALES
      scale_x_continuous(limits = c(0, 1), breaks = c(0, .5, 1)) +
      scale_y_continuous(limits = c(0, 2000), expand = c(0, 0)) +
      scale_color_manual(values = c("goldenrod3", "dodgerblue3")) +
      scale_fill_manual(values = c("goldenrod3", "dodgerblue3")) +
      # THEMES
      labs(x = "Percentile", y = "Frequency") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text = element_text(color = "black", size = 10),
            axis.ticks = element_line(color = "black", linewidth = .75),
            axis.line = element_line(linewidth = .75),
            axis.title = element_text(size = 12),
            legend.title = element_blank(),
            legend.position = c(.5, 1.065),
            legend.direction = "horizontal",
            plot.margin = unit(c(1, 1, .1, .15), "cm"),
            panel.spacing.x = unit(.25, "cm"),
            panel.spacing.y = unit(.35, "cm"),
            strip.text.x = element_text(size = 10, hjust = .25),
            strip.text.y = element_blank(),
            strip.clip = "off",
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_grid(condition~parameter, scales = "free", labeller = label_parsed)
  
dev.off()
```


# -------------------------------------------
# Summary Stats
```{r}
diagnostics %>% 
  filter(parameter != "Intercept") %>% 
  mutate(parameter_type = case_when(parameter %in% c("gamma00", "gamma10", "sigma_U[1]",
                                                     "sigma_U[2]", "R_theta[2,1]", "sigma_resid") ~ "group",
                                    T ~ "person"),
         new_parameter = case_when(str_detect(parameter, "beta0") ~ "beta0",
                                   str_detect(parameter, "beta1") ~ "beta1",
                                   str_detect(parameter, "theta") ~ "theta",
                                   str_detect(parameter, "A") ~ "A",
                                   T ~ parameter)) %>% 
  group_by(hypermodel, new_parameter) %>% 
  reframe(percent_under_1.1 = mean(rhat<1.1),
          m_rhat = mean(rhat),
          sd_rhat = sd(rhat)) %>% View()

characteristics %>% 
  group_by(hypermodel) %>% 
  reframe(m_duration = mean(duration),
          sd_duration = sd(duration))
```


# -------------------------------------------








