---
title: "Manuscript Plots"
output: html_document
date: "2023-03-09"
---



# ---------------------------------------
# Setup
## Loading Packages
```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstan)
library(hBayesDM)
library(bayesplot)
library(foreach)
library(tidybayes)
library(patchwork)
library(abind)
library(zoo)
library(here)
library(ggpubr)
library(egg)
library(grid)
library(tidyverse)
library(lemon)
library(ggpp)
library(wBoot)
library(stringi)
library(ggh4x)
library(hBayesDM)
source(here("1_IGT_PP", "Code", "R", "3_other", "helpful_functions.R"))
```



## Load Data
```{r include=FALSE}
stan_data = readRDS(here("1_IGT_PP", "Data", "1_Preprocessed",
                         "stan_ready_ORL_IGT.rds"))

orl_posteriors = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                              "Joint_ORL_posteriors.rds"))
self_report = readRDS(here("1_IGT_PP", "Data", "1_Preprocessed",
                           "self_report.rds"))
```



```{r, eval = F}
trial_choice_proportions = calculate_proportions(orl_posteriors, stan_data,
                                                 data_type = "data.frame"
                                                 # data_type = "list_of_matrices"
)
saveRDS(trial_choice_proportions,
        here("1_IGT_PP", "Data", "2_Fitted", 
             "Joint_ORL", "Joint_ORL_ppcs.rds"))
```



```{r}
trial_choice_proportions = readRDS(here("1_IGT_PP", "Data", "2_Fitted",
                                        "Joint_ORL", "Joint_ORL_ppcs.rds"))
```



## Functions
```{r}
# MAKE A FANCY LABEL FOR PLOTS
estimate_CI_label = function(estimate, lower, upper){
  
  estimate = round(estimate,2)
  estimate_lab = paste(ifelse(sign(estimate)==1," ","-"), stri_pad_right(str_remove(abs(estimate), "^0+"),
                                                           width = 3, pad = "0"),sep="")
  lower = round(as.numeric(str_remove(lower, "\\(")),2)
  upper = round(as.numeric(str_remove(upper, "\\)")),2)
  
  lower_lab = paste(ifelse(sign(lower)==1,"","-"), stri_pad_right(str_remove(abs(lower), "^0+"),
                                                                  width = 3, pad = "0"),sep="")
  
  upper_lab = paste(ifelse(sign(upper)==1,"","-"), stri_pad_right(str_remove(abs(upper), "^0+"),
                                                                  width = 3, pad = "0"),sep="")
  estimate_CI = paste("=",estimate_lab," [",lower_lab,",",upper_lab,"]",sep="")
  
  return(estimate_CI)
}


#------------------------------------------------------------------------------
# USE SOFTMAX TO OBTAIN CHOICE PROBABILITIES - USED IN SIMULATIONS
softmax = function(values){
  return(exp(values) / sum(exp(values)))
}


#------------------------------------------------------------------------------
# SIMULATION FUNCTION
simulate_orl = function(parameter_mus, condition,
                        custom_seed = 20230928, n_iterations = 1000) {
  set.seed(seed = custom_seed)
  data = data.frame()
  
  # parameters for sim
  Arew = filter(parameter_mus, parameter == "Arew")[[condition]]
  Apun = filter(parameter_mus, parameter == "Apun")[[condition]]
  K = filter(parameter_mus, parameter == "K")[[condition]]
  betaF = filter(parameter_mus, parameter == "betaF")[[condition]]
  betaP = filter(parameter_mus, parameter == "betaP")[[condition]]
  
  for(i in 1:n_iterations){
    utility = rep(0,4)
    ev = rep(0,4)
    ef = rep(0,4)
    pers = rep(0,4)
    K_tr = 3^(K)-1
    
    ef_chosen = 0
    PEval = 0
    PEfreq = 0
    PEfreq_fic = rep(0,4)
    
    for(t in 1:120){
      outcome = outcomes$outcome[outcomes$trial == t]
      sign = outcomes$sign[outcomes$trial == t]
      card = outcomes$card[outcomes$trial == t]
      prob = softmax(c(utility[card], 0))
      curr_choice = sample(c(1,2), 1, prob = prob)
      
      if(curr_choice==1) {
        PEval = outcome - ev[card]
        PEfreq= -1*sign - ef[card]
        PEfreq_fic = -1*sign/3 - ef;
        ef_chosen = ef[card];
        
        if(outcome >= 0) {
          ef = ef + Apun * PEfreq_fic
          ef[card] = ef_chosen + Arew * PEfreq
          ev[card] = ev[card] + Arew * PEval
        } else {
          ef = ef + Arew * PEfreq_fic
          ef[card] = ef_chosen + Apun * PEfreq;
          ev[card] = ev[card] + Apun * PEval;
        }
        pers[card] = 1;
      }
      pers = pers / (1 + K_tr)
      
      utility = ev + ef * betaF + pers * betaP
      data = data.frame(simulation = condition,
                        iteration = i,
                        card = card,
                        trial = t,
                        choice = curr_choice) %>% 
        bind_rows(data)
    }
  }
  data %>%
    group_by(iteration, card) %>%
    mutate(card_trial = 1:30) %>% 
    return()
}


#------------------------------------------------------------------------------
# RUN AND CLEAN UP CORRELATIONS
run_cor = function(cur_data, s, cor_type, x_nam, y_nam){
  cor = boot.cor.bca(
    x = cur_data[[x_nam]], y = cur_data[[y_nam]],
    alternative = c("two.sided", "less", "greater"),
    null.hyp = NULL, conf.level = 0.95, type = NULL, R = 9999)
  return(data.frame(
    cor_type = cor_type,
    x = x_nam, y = y_nam,
    session = s,
    r = cor$Observed,
    CI = cor$Confidence.interval))
}
```



# ---------------------------------------
# Good/Bad Play Proportions
## Prep Data
```{r, eval = T}
# Recode choice data
choices = ifelse(stan_data$choice == 2, 0, ifelse(stan_data$choice == 1, 1, NA))

# Empty matrices
IDs = matrix(data = NA, nrow = 49, ncol = 2, dimnames = list(NULL, c("subjID", "id")))
good_proportions = matrix(data = NA, nrow = 49, ncol = 2)
bad_proportions = matrix(data = NA, nrow = 49, ncol = 2)

# Calculate proportions
for(i in 1:49){
  IDs[i,] = c(stan_data$subjIDs[i], i)
  for(s in 1:2){
    good_proportions[i,s] = mean(choices[i,,s][stan_data$card[i,,s] == 3 | stan_data$card[i,,s] == 4], na.rm = T)
    bad_proportions[i,s] = mean(choices[i,,s][stan_data$card[i,,s] == 1 | stan_data$card[i,,s] == 2], na.rm = T)
  }
}

choice_proportions = data.frame(ID = IDs[,"subjID"], id = IDs[,"id"],
                                good_1 = good_proportions[,1], good_2 = good_proportions[,2],
                                bad_1 = bad_proportions[,1], bad_2 = bad_proportions[,2]) %>% 
  pivot_longer(c("good_1", "good_2", "bad_1", "bad_2"), names_sep = "_",
               names_to = c("type", "session"),
               values_to = "choice_proportion") %>% 
  mutate(type = factor(type, levels = c("good", "bad"), labels = c("Good", "Bad"), ordered = T),
         session = factor(session, levels = c("1", "2"), labels = c("1", "2"), ordered = T)) %>% 
  group_by(type, session) %>% 
  mutate(lower = t.test(choice_proportion)$conf.int[1],
         upper = t.test(choice_proportion)$conf.int[2],
         mu_sess = mean(choice_proportion, na.rm = T))

(good_t = t.test(good_proportions[,2], good_proportions[,1], paired = T, alternative = "two.sided"))
(good_r = boot.cor.bca(x = good_proportions[,1][!is.na(good_proportions[,2])],
                       y = good_proportions[,2][!is.na(good_proportions[,2])],
                       null.hyp = NULL,
                       alternative = c("two.sided", "less", "greater"),
                       conf.level = 0.95, type = NULL, R = 9999))
good_r_info = data.frame(r = good_r$Observed,
                         CI = good_r$Confidence.interval) %>% 
  separate(col = "CI", into = c("lower", "upper"), sep = ",") %>% 
  mutate(lower = as.numeric(str_remove(lower, "\\(")), upper = as.numeric(str_remove(upper, "\\)")))

(bad_t = t.test(bad_proportions[,2], bad_proportions[,1], paired = T, alternative = "two.sided"))
(bad_r = boot.cor.bca(x = bad_proportions[,1][!is.na(bad_proportions[,2])],
                      y = bad_proportions[,2][!is.na(bad_proportions[,2])],
                      null.hyp = NULL,
                      alternative = c("two.sided", "less", "greater"),
                      conf.level = 0.95, type = NULL, R = 9999))
bad_r_info = data.frame(r = bad_r$Observed,
                         CI = bad_r$Confidence.interval) %>% 
  separate(col = "CI", into = c("lower", "upper"), sep = ",") %>% 
  mutate(lower = as.numeric(str_remove(lower, "\\(")), upper = as.numeric(str_remove(upper, "\\)")))

prop_rCIs = data.frame(type = factor(c("good", "bad"), levels = c("good", "bad"), labels = c("Good", "Bad"), ordered = T),
                       rCI = c(estimate_CI_label(good_r_info$r, good_r_info$lower, good_r_info$upper),
                               estimate_CI_label(bad_r_info$r, bad_r_info$lower, bad_r_info$upper)))

boot.cor.bca(x = as.numeric(good_proportions[,1]),
             y = as.numeric(bad_proportions[,1]),
             null.hyp = NULL,
             alternative = c("two.sided", "less", "greater"),
             conf.level = 0.95, type = NULL, R = 9999)

boot.cor.bca(x = as.numeric(good_proportions[,2][!is.na(good_proportions[,2])]),
             y = as.numeric(bad_proportions[,2][!is.na(bad_proportions[,2])]),
             null.hyp = NULL,
             alternative = c("two.sided", "less", "greater"),
             conf.level = 0.95, type = NULL, R = 9999)

boot.cor.bca(x = apply(good_proportions, 1, mean, na.rm = T),
             y = apply(bad_proportions, 1, mean, na.rm = T),
             null.hyp = NULL,
             alternative = c("two.sided", "less", "greater"),
             conf.level = 0.95, type = NULL, R = 9999)
```



## Absolute Reliability Plots
```{r, eval = F}
prop_abs_plot = 
  choice_proportions %>% 
    group_by(type) %>% 
    mutate(mu = mean(choice_proportion, na.rm = T)) %>% 
    # plot
    ggplot(aes(x = type, y = choice_proportion, fill = session)) +
      # geoms
      geom_crossbar(aes(y = mu, ymin = mu, ymax = mu), size = .5, fatten = 0) +
      geom_dotplot(binaxis = "y", stackdir = "center",
                   position = position_dodge(width = .8)) +
      geom_pointrange(aes(y = mu_session, ymin = lower, ymax = upper),
                      color = "red", size = .1,
                      position = position_dodge(width = .8)) +
      # scales
      scale_y_continuous(limits = c(0, 1), expand = c(.01, .01), breaks = seq(0, 1, .25)) +
      scale_fill_manual(values = c("gray25", "gray75"),
                        labels = c("Session 1", "Session 2")) +
      # themes
      labs(x = "Session", y = "Proportion of Plays") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black", size = 10),
            axis.text.y = element_text(color = "black", size = 9),
            axis.title.x = element_blank(),
            axis.title.y = element_text(size = 10),
            plot.margin = unit(c(1.5,0,0,0), "lines"),
            legend.position = "none")


tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "Summary_Abs_Reliability.tiff"),
     width = 7, height = 4, units = "cm", res = 300)

  grid.newpage()
  pushViewport(viewport(x = .5, y = .5, width = .9, height = .9))
  grid.draw(prop_abs_plot)
  
  # text
  grid.text(c("1", "2", "1", "2"),
            x = c(.3225, .475, .6975, .85), y = .85,
            gp = gpar(fontsize = 9.5))
  grid.text("Session",
            x = .59, y = .94,
            gp = gpar(fontsize = 9.5))
  grid.lines(x = c(.5,.68), y = .9)
  
dev.off()
```



## Relative Reliability Plots
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "Summary_Rel_Reliability.tiff"),
     width = 7, height = 3.5, units = "cm", res = 300)
  
  (prop_rel_plot = 
    choice_proportions %>% 
      pivot_wider(names_from = "session", values_from = "choice_proportion", names_prefix = "session_") %>% 
      ggplot(aes(x = session_1, y = session_2)) +
        # geoms
        geom_point(size = 1, shape = 21, color = "black", fill = "gray50") +
        geom_smooth(method = "lm", formula = "y ~ x", color = "black", se = F, size = .5,
                    fullrange = T) +
        geom_text_npc(data = prop_rCIs, aes(npcx = "right", npcy = "bottom",
                                            label = rCI), size = 2.25, vjust = 0) +
        geom_text_npc(aes(npcx = "right", npcy = "bottom"), label = expression(italic(r)),
                      size = 2.25, hjust = 21.25, vjust = 0) +
        # scales
        scale_x_continuous(limits = c(0, 1), expand = c(.01, .01), breaks = seq(0, 1, .25),
                           labels = c("0", ".25", ".50", ".75", "1")) +
        scale_y_continuous(limits = c(0, 1), expand = c(.01, .01), breaks = seq(0, 1, .25),
                           labels = c("0", ".25", ".50", ".75", "1")) +
        # themes
        labs(x = "Session 1", y = "Session 2") +
        coord_cartesian(clip = "off") +
        theme_classic() +
        theme(axis.text = element_text(color = "black"),
              text = element_text(color = "black", size = 10),
              panel.spacing.y = unit(-1, "lines"),
              strip.background = element_rect(color = "transparent", fill = NA),
              strip.text = element_text(vjust = -2),
              plot.margin = unit(c(-.5,0.1,0.1,0.1), "lines"),
              aspect.ratio = 1) +
        facet_rep_wrap(.~type, ncol = 2))
  
dev.off()
```



# ---------------------------------------
# PPC Plot
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "PPC.tiff"),
     width = 15, height = 7, units = "cm", res = 300)

  # simplify data
  trial_choice_proportions %>% 
    group_by(trial, deck, session) %>% 
    summarise(observed = mean(observed), mu = mean(mu),
              lower50 = mean(lower50), upper50 = mean(upper50),
              lower95 = mean(lower95), upper95 = mean(upper95)) %>%
    # plotting
    ggplot(aes(x = trial,
               group = trial)) +
    # geoms
    geom_linerange(aes(ymin = lower95, ymax = upper95),
                   linewidth = .35, color = "goldenrod3", alpha = .35) +
    geom_linerange(aes(ymin = lower50, ymax = upper50),
                   linewidth = .35, color = "goldenrod3") +
    geom_point(aes(y = mu, color = "Predicted", fill = "Predicted"),
               shape = 21, size = .75) +
    geom_point(aes(y = observed, color = "Observed", fill = "Observed"),
               shape = 21, size = .75) +
    # scales
    scale_y_continuous(limits = c(0,1), expand = c(0,0),
                       breaks = seq(0,1,.25)) +
    scale_color_manual(name = "hello", values = c("Observed" = "black", "Predicted" = "goldenrod3")) +
    scale_fill_manual(name = "hello", values = c("Observed" = "black", "Predicted" = "white")) +
    # theme
    labs(x = "Trial", y = "Proportion Play") +
    theme_classic() +
    theme(axis.text = element_text(color = "black"),
          legend.title = element_blank(),
          legend.background = element_rect(fill = "transparent", colour = "transparent"),
          legend.position = c(.84,.59), 
          legend.spacing.x = unit(0, 'cm'),
          legend.spacing.y = unit(-.25, 'cm'),
          legend.text = element_text(size = 8),
          strip.background = element_blank(),
          panel.spacing.x = unit(-.5,"lines"),
          legend.key.size = unit(.25, "cm"),
          panel.spacing.y = unit(0,"lines")) +
    guides(color = guide_legend(override.aes = list(size = 1.25))) +
    facet_rep_grid(session~deck,
                   labeller = labeller(session = c("1" = "Session 1", "2" = "Session 2"),
                                       deck = c("A" = "Deck A", "B" = "Deck B",
                                                "C" = "Deck C", "D" = "Deck D")))
dev.off()
```



# ---------------------------------------
# Ind-Person PPC Plot
## Calculations
```{r}
N = stan_data$N
S = stan_data$S
C = 4
Trials = stan_data$T
size = 6
```



```{r, eval = F}
ind_choice_proportions = data.frame()

for(i in 1:N){
  for(s in 1:S){
    if(stan_data$Tsubj[i,s] > 0){
      for(c in 1:C){
        curr_data = ifelse(stan_data$choice[i,stan_data$card[i,,s] == c,s] == 2, 0, 1)
        curr_posterior = ifelse(orl_posteriors$choice_pred[,i,stan_data$card[i,,s] == c,s] == 2, 0, 1)
        for(k in 1:(30-(size-1))){
          ind_choice_proportions = data.frame(
            id = i,
            session = s,
            binC = median(k:(k+(size-1))),
            card = c,
            choice = mean(curr_data[k:(k+(size-1))]),
            prob_mean = mean(apply(curr_posterior[,k:(k+(size-1))], 1, mean)),
            prob_median = median(apply(curr_posterior[,k:(k+(size-1))], 1, mean)),
            lower95 = HDIofMCMC(apply(curr_posterior[,k:(k+(size-1))], 1, mean))[1],
            upper95 = HDIofMCMC(apply(curr_posterior[,k:(k+(size-1))], 1, mean))[2],
            lower50 = HDIofMCMC(apply(curr_posterior[,k:(k+(size-1))], 1, mean), credMass = .5)[1],
            upper50 = HDIofMCMC(apply(curr_posterior[,k:(k+(size-1))], 1, mean), credMass = .5)[2]
            ) %>% 
            bind_rows(ind_choice_proportions)
        }
      }
    }
  }
}
saveRDS(ind_choice_proportions, here("1_IGT_PP", "Data", "2_Fitted",
                                     "Joint_ORL", paste0("Joint_ORL_ind_", size,"trial_ppcs.rds")))
```



```{r}
ind_choice_proportions = readRDS(here("1_IGT_PP", "Data", "2_Fitted",
                                      "Joint_ORL", paste0("Joint_ORL_ind_", size,"trial_ppcs.rds")))
rm(list = c("N", "S", "C", "Trials", "size"))
```



## Plot 2050 & 2051
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "Individual_PPCs.tiff"),
     width = 15, height = 7, units = "cm", res = 300)

  # simplify data
  ind_choice_proportions %>% 
    left_join(data.frame(IDs)) %>% 
    filter(subjID == 2051 | subjID == 2050) %>% 
    mutate(id = paste0("ID #", subjID)) %>%
    select(everything(),
           prob = prob_mean, lower = lower95, upper = upper95,
           -c(prob_median, lower50, upper50)) %>% 
    pivot_wider(names_from = "session", values_from = c("prob", "choice", "lower", "upper")) %>%
    # plotting
    ggplot(aes(x = binC-2.5)) +
      # geoms
      # geom_linerange(aes(ymin = lower_1, ymax = upper_1), show.legend = F,
      #                linewidth = .35, color = "goldenrod3") +
      # geom_linerange(aes(ymin = lower_2, ymax = upper_2), show.legend = F,
      #                linewidth = .35, color = "goldenrod3") +
      geom_point(aes(y = prob_1, shape = "Session 1 Predicted",
                     color = "Session 1 Predicted", fill = "Session 1 Predicted"),
                 size = .75) +
      geom_point(aes(y = choice_1, shape = "Session 1 Observed",
                     color = "Session 1 Observed", fill = "Session 1 Observed"),
                 size = .75) +
      geom_point(aes(y = prob_2, shape = "Session 2 Predicted",
                     color = "Session 2 Predicted", fill = "Session 2 Predicted"),
                 size = .75) +
      geom_point(aes(y = choice_2, shape = "Session 2 Observed",
                     color = "Session 2 Observed", fill = "Session 2 Observed"),
                 size = .75) +
      # scales
      scale_x_continuous(limits = c(0, 25), expand = c(.0175, .0175), breaks = seq(0, 25, 5)) +
      scale_y_continuous(limits = c(0, 1), expand = c(.015, .015), breaks = seq(0, 1, .25),
                         labels = c("0", ".25", ".50", ".75", "1")) +
      scale_color_manual(name = "hello",
                         values = c("Session 1 Observed" = "black",
                                    "Session 1 Predicted" = "goldenrod3",
                                    "Session 2 Observed" = "black",
                                    "Session 2 Predicted" = "goldenrod3")) +
      scale_fill_manual(name = "hello",
                        values = c("Session 1 Observed" = "black",
                                   "Session 1 Predicted" = "white",
                                   "Session 2 Observed" = "black",
                                   "Session 2 Predicted" = "white")) +
      scale_shape_manual(name = "hello",
                         values = c("Session 1 Observed" = 22,
                                    "Session 1 Predicted" = 22,
                                    "Session 2 Observed" = 23,
                                    "Session 2 Predicted" = 23)) +
      # theme
      labs(x = "6-Trial Bin", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.title = element_blank(),
            legend.background = element_rect(fill = "transparent", colour = "transparent"),
            legend.position = c(.855,.6175),
            # legend.position = "top", 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 6.25),
            legend.key.size = unit(.2, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      guides(color = guide_legend(override.aes = list(size = 1.25))) +
      facet_rep_grid(id~card,
                     labeller = labeller(card = c("1" = "Deck A", "2" = "Deck B",
                                                  "3" = "Deck C", "4" = "Deck D")))
dev.off()
```



## Plot All
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "ALL_Individual_PPCs.tiff"),
     width = 15, height = 7*25, units = "cm", res = 300)

  # simplify data
  ind_choice_proportions %>% 
    left_join(data.frame(IDs)) %>% 
    mutate(id = paste0("ID #", subjID)) %>%
    select(everything(),
           prob = prob_mean, lower = lower95, upper = upper95,
           -c(prob_median, lower50, upper50)) %>% 
    pivot_wider(names_from = "session", values_from = c("prob", "choice", "lower", "upper")) %>%
    # plotting
    ggplot(aes(x = binC-2.5)) +
      # geoms
      # geom_linerange(aes(ymin = lower_1, ymax = upper_1), show.legend = F,
      #                linewidth = .35, color = "goldenrod3") +
      # geom_linerange(aes(ymin = lower_2, ymax = upper_2), show.legend = F,
      #                linewidth = .35, color = "goldenrod3") +
      geom_point(aes(y = prob_1, shape = "Session 1 Predicted",
                     color = "Session 1 Predicted", fill = "Session 1 Predicted"),
                 size = .75) +
      geom_point(aes(y = choice_1, shape = "Session 1 Observed",
                     color = "Session 1 Observed", fill = "Session 1 Observed"),
                 size = .75) +
      geom_point(aes(y = prob_2, shape = "Session 2 Predicted",
                     color = "Session 2 Predicted", fill = "Session 2 Predicted"),
                 size = .75) +
      geom_point(aes(y = choice_2, shape = "Session 2 Observed",
                     color = "Session 2 Observed", fill = "Session 2 Observed"),
                 size = .75) +
      # scales
      scale_x_continuous(limits = c(0, 25), expand = c(.0175, .0175), breaks = seq(0, 25, 5)) +
      scale_y_continuous(limits = c(0, 1), expand = c(.015, .015), breaks = seq(0, 1, .25),
                         labels = c("0", ".25", ".50", ".75", "1")) +
      scale_color_manual(name = "hello",
                         values = c("Session 1 Observed" = "black",
                                    "Session 1 Predicted" = "goldenrod3",
                                    "Session 2 Observed" = "black",
                                    "Session 2 Predicted" = "goldenrod3")) +
      scale_fill_manual(name = "hello",
                        values = c("Session 1 Observed" = "black",
                                   "Session 1 Predicted" = "white",
                                   "Session 2 Observed" = "black",
                                   "Session 2 Predicted" = "white")) +
      scale_shape_manual(name = "hello",
                         values = c("Session 1 Observed" = 22,
                                    "Session 1 Predicted" = 22,
                                    "Session 2 Observed" = 23,
                                    "Session 2 Predicted" = 23)) +
      # theme
      labs(x = "6-Trial Bin", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.title = element_blank(),
            legend.background = element_rect(fill = "transparent", colour = "transparent"),
            legend.position = c(.855,.6175),
            # legend.position = "top", 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 6.25),
            legend.key.size = unit(.2, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      guides(color = guide_legend(override.aes = list(size = 1.25))) +
      facet_rep_grid(id~card,
                     labeller = labeller(card = c("1" = "Deck A", "2" = "Deck B",
                                                  "3" = "Deck C", "4" = "Deck D")))
dev.off()
```



# ---------------------------------------
# ORL Parameters
## Absolute Reliability
```{r, eval = F}
orl_abs_data = bind_rows(data.frame(parameter = "Arew", session = orl_posteriors$mu_Arew),
                         data.frame(parameter = "Apun", session = orl_posteriors$mu_Apun),
                         data.frame(parameter = "betaF", session = orl_posteriors$mu_betaF),
                         data.frame(parameter = "betaP", session = orl_posteriors$mu_betaP),
                         data.frame(parameter = "K", session = orl_posteriors$mu_K)) %>% 
  mutate(session.diff = session.2 - session.1) %>% 
  pivot_longer(starts_with("session"),
               names_to = "session", values_to = "estimate", names_prefix = "session.") %>% 
  group_by(parameter, session) %>% 
  mutate(mu = mean(estimate),
         lower50 = HDIofMCMC(estimate, credMass = .5)[1],
         upper50 = HDIofMCMC(estimate, credMass = .5)[2],
         lower95 = HDIofMCMC(estimate)[1],
         upper95 = HDIofMCMC(estimate)[2],
         parameter = factor(parameter, ordered = T,
                            levels = c("Arew", "Apun", "betaF", "betaP", "K")),
         parameter_lab = factor(parameter,
                                levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                                labels = c(expression(paste(italic(A),"+",sep="")),
                                           expression(paste(italic(A),"-",sep="")),
                                           expression(paste("\u03B2",italic(f),sep="")),
                                           expression(paste("\u03B2",italic(p),sep="")),
                                           expression(italic(K)))),
         parameter_lab = case_when(session == "diff" ~ parameter_lab, T ~ NA))

orl_abs_scales =
  list(parameter == "Arew" & session != "diff" ~
         scale_x_continuous(limits = c(0, .3), expand = expansion(add = c(0, 0)),
                            breaks = seq(0, .3, .15), labels = c("0", ".15", ".3")),
       parameter == "Arew" & session == "diff" ~
         scale_x_continuous(limits = c(-.3, .3), expand = expansion(add = c(0, 0)),
                            breaks = seq(-.3, .3, .3), labels = c("-.3", "0", ".3")),
       
       parameter == "Apun" & session != "diff" ~
         scale_x_continuous(limits = c(.05, .15), expand = expansion(add = c(0, 0)),
                            breaks = seq(.05, .15, .05), labels = c(".05", ".1", ".15")),
       parameter == "Apun" & session == "diff" ~
         scale_x_continuous(limits = c(-.05, .05), expand = expansion(add = c(0, 0)),
                            breaks = seq(-.05, .05, .05), labels = c("-.05", "0", ".05")),
       
       parameter == "betaF" & session != "diff" ~
         scale_x_continuous(limits = c(0, 6), expand = expansion(add = c(0, 0)),
                            breaks = seq(0, 6, 3), labels = c(".05", ".1", ".15")),
       parameter == "betaF" & session == "diff" ~
         scale_x_continuous(limits = c(-3, 3), expand = expansion(add = c(0, 0)),
                            breaks = seq(-3, 3, 3), labels = c("-3", "0", "3")),
       
       parameter == "betaP" & session != "diff" ~
         scale_x_continuous(limits = c(0, 3), expand = expansion(add = c(0, 0)),
                            breaks = seq(0, 3, 1.5), labels = c("0", "1.5", "3")),
       parameter == "betaP" & session == "diff" ~
         scale_x_continuous(limits = c(-2, 2), expand = expansion(add = c(0, 0)),
                            breaks = seq(-2, 2, 2), labels = c("-2", "0", "2")),
       
       parameter == "K" & session != "diff" ~
         scale_x_continuous(limits = c(0, .3), expand = expansion(add = c(0, 0)),
                            breaks = seq(0, .3, .15), labels = c("0", ".15", ".3")),
       parameter == "K" & session == "diff" ~
         scale_x_continuous(limits = c(-.1, .1), expand = expansion(add = c(0, 0)),
                            breaks = seq(-.1, .1, .1), labels = c("-.1", "0", ".1")))
```



```{r, eval = F}
orl_abs_plot = orl_abs_data %>% 
  ggplot(aes(x = estimate)) +
    # geoms
    geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                   linewidth = .1, bins = 50) +
  
    geom_hline(yintercept = 0) +
    geom_vline(aes(xintercept = mu), color = "red2", linewidth = .25) +
    geom_vline(aes(xintercept = lower95), color = "red", linetype = "dashed", linewidth = .25) +
    geom_vline(aes(xintercept = upper95), color = "red", linetype = "dashed", linewidth = .25) +
    # scales
    scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
    # themes
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.margin = unit(c(.5, .5, .3, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(0, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(parameter~session, scales = "free",
                   nrow = 5, ncol = 3) +
    facetted_pos_scales(x = orl_abs_scales)
```



```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "ORL_Abs_Reliability.tiff"),
     width = 7, height = 10, units = "cm", res = 300)

  grid.newpage()
  pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
  grid.draw(orl_abs_plot)
  
  # text
  grid.text(c("Session 1", "Session 2", " Session 2-1"),
            x = c(.2, .515, .81), y = .98,
            gp = gpar(fontsize = 9.5))
  grid.text(c(expression(paste(italic(A),"+",sep="")),
              expression(paste(italic(A),"-",sep="")),
              expression(paste("\u03B2",italic(f),sep="")),
              expression(paste("\u03B2",italic(p),sep="")),
              expression(italic(K))),
            x = rep(.93, 5), y = c(.89, .725, .55, .37, .195),
            gp = gpar(fontsize = 9.5))
  
dev.off()
```



## Relative Reliability
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "ORL_Rel_Reliability.tiff"),
     width = 14.6, height = 4, units = "cm", res = 300)

  bind_rows(data.frame(parameter = "Arew", r = orl_posteriors$R_Arew[,2,1]),
            data.frame(parameter = "Apun", r = orl_posteriors$R_Apun[,2,1]),
            data.frame(parameter = "betaF", r = orl_posteriors$R_betaF[,2,1]),
            data.frame(parameter = "betaP", r = orl_posteriors$R_betaP[,2,1]),
            data.frame(parameter = "K", r = orl_posteriors$R_K[,2,1])) %>% 
    mutate(parameter = factor(parameter,
                              levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                              labels = c(expression(paste(italic(A),"+",sep="")),
                                         expression(paste(italic(A),"-",sep="")),
                                         expression(paste("\u03B2",italic(f),sep="")),
                                         expression(paste("\u03B2",italic(p),sep="")),
                                         expression(italic(K))))) %>% 
    group_by(parameter) %>% 
    mutate(mu_r = mean(r), lower = HDIofMCMC(r)[1], upper = HDIofMCMC(r)[2],
           below_0 = paste0(round(mean(r<0)*100), "% < 0"), above_0 = paste0(round(mean(r>0)*100), "% > 0"),
           height = max(density(r)$x)*.025) %>% 
    ggplot(aes(x = r)) +
      # geoms
      geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                     linewidth = .1, bins = 50) +
      geom_text_npc(aes(npcx = "left", npcy = "top", label = below_0),
                    size = 2, vjust = -1.43) +
      geom_text_npc(aes(npcx = "right", npcy = "top", label = above_0),
                    size = 2, vjust = -1.43) +
      # geom_text_npc(aes(npcx = "left", npcy = "top", label = below_0),
      #               size = 2, hjust = -3, vjust = -1.43) +
      # geom_text_npc(aes(npcx = "right", npcy = "top",
      #                   label = rCI_lab), size = 2, vjust = -1.05) +
      geom_hline(yintercept = 0) +
      geom_vline(aes(xintercept = mu_r), color = "red2", linewidth = .4) +
      geom_errorbarh(aes(xmin = lower, xmax = upper,
                         y = height),
                         color = "red", linewidth = .4) +
      # scales
      scale_x_continuous(limits = c(-1,1), expand = c(0,0), breaks = seq(-1,1,.5),
                         labels = c("-1","-.5","0",".5", "1")) +
      scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
      # themes
      labs(x = "Reliability Coefficient", y = "Density") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black"),
            axis.ticks.x = element_line(color = "black"),
            axis.line.x = element_line(color = "transparent"),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank(),
            axis.line.y = element_blank(),
            plot.margin = unit(c(.1, .3, .1, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            strip.text.x = element_text(size = 12, vjust = 1.5),
            strip.text.y = element_blank(),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_grid(.~parameter, scales = "free",
                     labeller = label_parsed)
dev.off()
```



# ---------------------------------------
# Prop/ORL/Self-Report Correlations
## Prep Data
```{r}
IDs = matrix(data = NA, nrow = 49, ncol = 2, dimnames = list(NULL, c("subjID", "id")))
temp_good = matrix(data = NA, nrow = 49, ncol = 1)
temp_bad = matrix(data = NA, nrow = 49, ncol = 1)

for(i in 1:49){
  temp_good[i] = mean(choices[i,,][stan_data$card[i,,] == 3 | stan_data$card[i,,] == 4], na.rm = T)
  temp_bad[i] = mean(choices[i,,][stan_data$card[i,,] == 1 | stan_data$card[i,,] == 2], na.rm = T)
}
```


```{r}
ch_prop_sess = choice_proportions %>%
  pivot_wider(names_from = "type", values_from = "choice_proportion") %>% 
  mutate(session = as.numeric(session))
ch_prop_avg = ch_prop_sess %>% 
  group_by(ID) %>% 
  reframe(Good = mean(Good, na.rm = T), Bad = mean(Bad, na.rm = T))

orl_parameters = data.frame(ID = stan_data$subjIDs,
                            Arew = apply(orl_posteriors$Arew, c(2,3), mean),
                            Apun = apply(orl_posteriors$Apun, c(2,3), mean),
                            betaF = apply(orl_posteriors$betaF, c(2,3), mean),
                            betaP = apply(orl_posteriors$betaP, c(2,3), mean),
                            K = apply(orl_posteriors$K, c(2,3), mean),
                            Arew.0 = apply(orl_posteriors$Arew, 2, mean),
                            Apun.0 = apply(orl_posteriors$Apun, 2, mean),
                            betaF.0 = apply(orl_posteriors$betaF, 2, mean),
                            betaP.0 = apply(orl_posteriors$betaP, 2, mean),
                            K.0 = apply(orl_posteriors$K, 2, mean)) %>% 
  pivot_longer(starts_with(c("Arew", "Apun", "betaF", "betaP", "K")),
               names_to = c("parameter", "session"), values_to = "estimate",
               names_sep = "\\.", names_transform = list(session = as.numeric)) %>% 
  pivot_wider(names_from = "parameter", values_from = "estimate") %>% 
  mutate(ratio = Apun/Arew)

session1_session2 = self_report %>% 
  pivot_wider(names_from = "scale", values_from = "score") %>% 
  left_join(orl_parameters) %>% left_join(ch_prop_sess)
averages = self_report %>% 
  group_by(ID, scale) %>% 
  reframe(score = mean(score, na.rm = T), session = 0) %>% 
  pivot_wider(names_from = "scale", values_from = "score") %>% 
  left_join(orl_parameters) %>% left_join(ch_prop_avg)

combined = bind_rows(session1_session2, averages)
```



```{r}
set.seed(20230320)

# RUN SELF-REPORT/PLAY PROPORTION CORRELATIONS
SR_prop_correlations = data.frame()

for(s in unique(combined$session)){
  for(scale in unique(self_report$scale)){
    for(prop in c("Good", "Bad")){
      cur_data = combined %>% 
        filter(session == s) %>% 
        select(ID, all_of(scale), all_of(prop)) %>% 
        na.omit()
      
      if(nrow(cur_data)!=0){
        SR_prop_correlations = run_cor(cur_data, s, "SR-Prop", scale, prop) %>% 
          bind_rows(SR_prop_correlations)
      }
    }
  }
}

# RUN SELF-REPORT/ORL CORRELATIONS
SR_ORL_correlations = data.frame()

for(s in unique(combined$session)){
  for(scale in unique(self_report$scale)){
    for(parameter in c("Arew", "Apun", "betaF", "betaP", "K")){
      cur_data = combined %>% 
        filter(session == s) %>% 
        select(ID, all_of(scale), all_of(parameter)) %>% 
        na.omit()
      
      if(nrow(cur_data)!=0){
        SR_ORL_correlations = run_cor(cur_data, s, "SR-ORL", scale, parameter) %>% 
          bind_rows(SR_ORL_correlations)
      }
    }
  }
}

# RUN Play Proportion/ORL CORRELATIONS
prop_ORL_correlations = data.frame()

for(s in unique(combined$session)){
  for(prop in c("Good", "Bad")){
    for(parameter in c("Arew", "Apun", "betaF", "betaP", "K")){
      cur_data = combined %>% 
        filter(session == s) %>% 
        select(ID, all_of(prop), all_of(parameter)) %>% 
        na.omit()
      
      if(nrow(cur_data)!=0){
        prop_ORL_correlations = run_cor(cur_data, s, "ORL-Prop", parameter, prop) %>% 
          bind_rows(prop_ORL_correlations)
      }
    }
  }
}

correlations = bind_rows(SR_prop_correlations,
                         SR_ORL_correlations,
                         prop_ORL_correlations) %>% 
  separate(col = "CI", into = c("lower", "upper"), sep = ",") %>% 
  mutate(lower = as.numeric(str_remove(lower, "\\(")),
         upper = as.numeric(str_remove(upper, "\\)")),
         sig = case_when(lower < 0 & upper < 0 ~ "*",
                         lower > 0 & upper > 0 ~ "*",
                         lower < 0 & upper < .01 ~ "#",
                         lower > .01 & upper > 0 ~ "#",
                         T ~ ""))

saveRDS(correlations, here("1_IGT_PP", "Data", "2_Fitted",
                           "Joint_ORL", paste0("Joint_ORL_correlations.rds")))
```



## Save Correlations
```{r}
correlations = readRDS(here("1_IGT_PP", "Data", "2_Fitted",
                            "Joint_ORL", paste0("Joint_ORL_correlations.rds")))

correlations %>% 
  mutate(# MAKE NICE LABEL
         estimate = round(r,2),
         estimate_lab = paste(ifelse(sign(estimate)==1," ","-"), stri_pad_right(str_remove(abs(estimate), "^0+"),
                                                                                width = 3, pad = "0"),sep=""),
         lower = round(as.numeric(str_remove(lower, "\\(")),2),
         upper = round(as.numeric(str_remove(upper, "\\)")),2),
         
         lower_lab = paste(ifelse(sign(lower)==1,"","-"), stri_pad_right(str_remove(abs(lower), "^0+"),
                                                                         width = 3, pad = "0"),sep=""),
         
         upper_lab = paste(ifelse(sign(upper)==1,"","-"), stri_pad_right(str_remove(abs(upper), "^0+"),
                                                                         width = 3, pad = "0"),sep=""),
         lower_lab = case_when(lower_lab == "-000" ~ "-.00", T ~ lower_lab),
         upper_lab = case_when(upper_lab == "-000" ~ "-.00", T ~ upper_lab),
         estimate_lab = case_when(estimate_lab == "-000" ~ "-.00", T ~ estimate_lab),
         estimate_CI = paste(estimate_lab," [",lower_lab,",",upper_lab,"]",sep=""),
         # SORTING
         SR_sort = case_when(x == "bastot" ~ 1, x == "basdrive" ~ 2, x == "basfunsk" ~ 3, 
                             x == "basrewres" ~ 4, x == "bis" ~ 5, x == "panas_pa" ~ 6, 
                             x == "panas_na" ~ 7, x == "masqGDA" ~ 8, x == "masqAA" ~ 9, 
                             x == "masqGDD" ~ 10, x == "masqAD" ~ 11, x == "shaps_tot" ~ 12,
                             x == "prdep_tot" ~ 13)) %>% 
  write.csv(here("1_IGT_PP", "Data", "2_Fitted",
                 "Joint_ORL", paste0("Joint_ORL_correlations.csv")))
```



# ---------------------------------------
# Simulate ORL Parameters
## Prep Inputs for Simulations
```{r, eval = F}
# PREP TASK-RELATED INPUTS
cards = data.frame(card = stan_data$card[1,,1]) %>%
  mutate(trial = 1:n()) %>% 
  group_by(card) %>% 
  mutate(card_trial = 1:n())

outcomes = read.csv(here("1_IGT_PP", "Data", "0_Raw", "outcomes.csv")) %>% 
  mutate(card_trial = 1:n()) %>% 
  pivot_longer(starts_with("Deck"), names_to = "card",
               values_to = "outcome", names_prefix = "Deck_") %>% 
  mutate(card = case_when(card == "A" ~ 1, card == "B" ~ 2,
                          card == "C" ~ 3, card == "D" ~ 4),
         sign = sign(outcome),
         outcome = outcome / 100) %>% 
  left_join(cards) %>% na.omit()

#------------------------------------------------------------------------------
# PARAMETER VALUES FOR SIMULATION
parameter_mus = data.frame(Arew = orl_posteriors$mu_Arew,
                           Apun = orl_posteriors$mu_Apun,
                           K = orl_posteriors$mu_K,
                           betaF = orl_posteriors$mu_betaF,
                           betaP = orl_posteriors$mu_betaP) %>%
  pivot_longer(everything(), names_to = c("parameter", "session"), names_sep = "\\.",
               values_to = "estimate") %>%
  group_by(parameter, session) %>%
  reframe(mu = mean(estimate)) %>%
  pivot_wider(names_from = "session", values_from = "mu", names_prefix = "session_") %>%
  mutate(# Parameter values of observed changes in Arew & betaP with interaction
         BL = session_1,
         me_betaP = case_when(parameter == "Arew" ~ session_1, T ~ session_2),
         me_Arew = case_when(parameter == "betaP" ~ session_1, T ~ session_2),
         int = session_2,
         # Overall mu parameter values
         mu = (session_1 + session_2) / 2,
         # Parameter values of manipulating Arew
         rew_HI = case_when(parameter == "Arew" ~ mu*4, T ~ mu),
         rew_LO = case_when(parameter == "Arew" ~ mu/4, T ~ mu),
         # Parameter values of manipulating Apun
         pun_HI = case_when(parameter == "Apun" ~ mu*4, T ~ mu),
         pun_LO = case_when(parameter == "Apun" ~ mu/4, T ~ mu),
         # Parameter values of manipulating betaP
         betaP_HI = case_when(parameter == "betaP" ~ mu*4, T ~ mu),
         betaP_LO = case_when(parameter == "betaP" ~ mu/4, T ~ mu),
         # Parameter values of manipulating betaF
         betaF_HI = case_when(parameter == "betaF" ~ mu*4, T ~ mu),
         betaF_LO = case_when(parameter == "betaF" ~ mu/4, T ~ mu),
         # Parameter values of manipulating K
         K_HI = case_when(parameter == "K" ~ mu*4, T ~ mu),
         K_LO = case_when(parameter == "K" ~ mu/4, T ~ mu),
         # Parameter values of manipulating Arew & betaP
         rew_LO_betaP_HI = case_when(parameter == "betaP" ~ mu*4,
                                     parameter == "Arew" ~ mu/4,
                                     T ~ mu))
#------------------------------------------------------------------------------
# RUN SIMULATIONS
# Simulation of observed changes in Arew & betaP with interaction
databased_simulations = bind_rows(simulate_orl(parameter_mus, "BL"),
                                   simulate_orl(parameter_mus, "me_betaP"),
                                   simulate_orl(parameter_mus, "me_Arew"),
                                   simulate_orl(parameter_mus, "int"))
saveRDS(databased_simulations, here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                                    "databased_simulations.rds"))
# Simulation of overall mus
mu_simultations = simulate_orl(parameter_mus, "mu")
saveRDS(mu_simultations, here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                              "mu_simultations.rds"))
# Simulation of changes in Arew & betaP with interaction
Arew_betaP_simulations = bind_rows(mu_simultations,
                                   simulate_orl(parameter_mus, "rew_LO"),
                                   simulate_orl(parameter_mus, "betaP_HI"),
                                   simulate_orl(parameter_mus, "rew_LO_betaP_HI"))
saveRDS(Arew_betaP_simulations, here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                                     "Arew_betaP_simulations.rds"))
# Simulation of manipulating Arew
Arew_simulations = bind_rows(mu_simultations,
                             simulate_orl(parameter_mus, "rew_HI"),
                             simulate_orl(parameter_mus, "rew_LO"))
saveRDS(Arew_simulations, here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                               "Arew_simulations.rds"))
# Simulation of manipulating Apun
Apun_simulations = bind_rows(mu_simultations,
                             simulate_orl(parameter_mus, "pun_HI"),
                             simulate_orl(parameter_mus, "pun_LO"))
saveRDS(Apun_simulations, here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                               "Apun_simulations.rds"))
# Simulation of manipulating betaP
betaP_simulations = bind_rows(mu_simultations,
                              simulate_orl(parameter_mus, "betaP_HI"),
                              simulate_orl(parameter_mus, "betaP_LO"))
saveRDS(betaP_simulations, here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                                "betaP_simulations.rds"))
# Simulation of manipulating betaF
betaF_simulations = bind_rows(mu_simultations,
                              simulate_orl(parameter_mus, "betaF_HI"),
                              simulate_orl(parameter_mus, "betaF_LO"))
saveRDS(betaF_simulations, here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                                "betaF_simulations.rds"))
# Simulation of manipulating Apun
K_simulations = bind_rows(mu_simultations,
                          simulate_orl(parameter_mus, "K_HI"),
                          simulate_orl(parameter_mus, "K_LO"))
saveRDS(K_simulations, here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                            "K_simulations.rds"))
```



```{r}
databased_simulations = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                                     "databased_simulations.rds"))
Arew_betaP_simulations = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                                      "Arew_betaP_simulations.rds"))
mu_simultations = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                               "mu_simultations.rds"))
Arew_simulations = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                                "Arew_simulations.rds"))
Apun_simulations = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                                "Apun_simulations.rds"))
betaP_simulations = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                                 "betaP_simulations.rds"))
betaF_simulations = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                                 "betaF_simulations.rds"))
K_simulations = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL",
                             "K_simulations.rds"))
```



## Arew/BetaP Simulation
```{r, eval = F}
labs = c("Session 1",
         expression(paste("\u0394",italic(A),"+",sep="")),
         expression(paste("\u0394","\u03B2",italic(f),sep="")),
         "Session 2")

tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "Satabased Simulations.tiff"),
     width = 6.5, height = 2.5, units = "in", res = 300)

  # data
  databased_simulations %>% 
    select(everything(), deck = card) %>% 
    mutate(choice = case_when(choice == 2 ~ 0, T ~ choice),
           simulation = factor(simulation,
                               levels = c("BL", "me_Arew", "me_betaP", "int"))) %>% 
    group_by(simulation, trial, deck) %>% 
    reframe(proportion = mean(choice)) %>% 
    # plotting
    ggplot(aes(x = trial, color = simulation)) +
      # geoms
      geom_line(aes(y = proportion)) +
      # scales
      scale_y_continuous(limits = c(0,1), expand = c(0,0),
                         breaks = seq(0,1,.25)) +
      scale_color_manual(values = c("black", "dodgerblue3", "orange2", "gray45"), labels = labs) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.title = element_blank(),
            legend.background = element_rect(fill = "transparent", colour = "transparent"),
            legend.position = "top",
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            panel.spacing.y = unit(0,"lines"),
            plot.margin = unit(c(.1,.25,.1,.1), "cm")) +
      facet_rep_grid(.~deck,
                     labeller = labeller(deck = c("1" = "Deck A", "2" = "Deck B",
                                                  "3" = "Deck C", "4" = "Deck D")))
dev.off()  
```



## Arew-Only Simulation
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "Arew_Simulations.tiff"),
     width = 6.5, height = 3, units = "in", res = 300)

  # data
  Arew_simulations %>% 
    select(everything(), deck = card) %>% 
    mutate(choice = case_when(choice == 2 ~ 0, T ~ choice)) %>% 
    group_by(simulation, trial, deck) %>% 
    reframe(proportion = mean(choice)) %>% 
    # plotting
    ggplot(aes(x = trial, color = simulation)) +
      # geoms
      # geom_point(aes(y = proportion, color = "Predicted", fill = "Predicted"),
      #            shape = 21, size = .75) +
      geom_line(aes(y = proportion)) +
      # scales
      scale_y_continuous(limits = c(0,1), expand = c(0,0),
                         breaks = seq(0,1,.25)) +
      # scale_color_manual(name = "hello", values = c("Predicted" = "goldenrod3")) +
      # scale_fill_manual(name = "hello", values = c("Predicted" = "white")) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.title = element_blank(),
            legend.background = element_rect(fill = "transparent", colour = "transparent"),
            # legend.position = "none", 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.key.size = unit(.25, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      # guides(color = guide_legend(override.aes = list(size = 1.25))) +
      facet_rep_grid(.~deck,
                     labeller = labeller(deck = c("1" = "Deck A", "2" = "Deck B",
                                                  "3" = "Deck C", "4" = "Deck D")))
dev.off()  
```



## Apun-Only Simulation
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "Apun_Simulations.tiff"),
     width = 6.5, height = 3, units = "in", res = 300)

  # data
  Apun_simulations %>% 
    select(everything(), deck = card) %>% 
    mutate(choice = case_when(choice == 2 ~ 0, T ~ choice)) %>% 
    group_by(simulation, trial, deck) %>% 
    reframe(proportion = mean(choice)) %>% 
    # plotting
    ggplot(aes(x = trial, color = simulation)) +
      # geoms
      # geom_point(aes(y = proportion, color = "Predicted", fill = "Predicted"),
      #            shape = 21, size = .75) +
      geom_line(aes(y = proportion)) +
      # scales
      scale_y_continuous(limits = c(0,1), expand = c(0,0),
                         breaks = seq(0,1,.25)) +
      # scale_color_manual(name = "hello", values = c("Predicted" = "goldenrod3")) +
      # scale_fill_manual(name = "hello", values = c("Predicted" = "white")) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.title = element_blank(),
            legend.background = element_rect(fill = "transparent", colour = "transparent"),
            # legend.position = "none", 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.key.size = unit(.25, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      # guides(color = guide_legend(override.aes = list(size = 1.25))) +
      facet_rep_grid(.~deck,
                     labeller = labeller(deck = c("1" = "Deck A", "2" = "Deck B",
                                                  "3" = "Deck C", "4" = "Deck D")))
dev.off()  
```



## BetaP-Only Simulation
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "betaP_Simulations.tiff"),
     width = 6.5, height = 3, units = "in", res = 300)

  # data
  betaP_simulations %>% 
    select(everything(), deck = card) %>% 
    mutate(choice = case_when(choice == 2 ~ 0, T ~ choice)) %>% 
    group_by(simulation, trial, deck) %>% 
    reframe(proportion = mean(choice)) %>% 
    # plotting
    ggplot(aes(x = trial, color = simulation)) +
      # geoms
      # geom_point(aes(y = proportion, color = "Predicted", fill = "Predicted"),
      #            shape = 21, size = .75) +
      geom_line(aes(y = proportion)) +
      # scales
      scale_y_continuous(limits = c(0,1), expand = c(0,0),
                         breaks = seq(0,1,.25)) +
      # scale_color_manual(name = "hello", values = c("Predicted" = "goldenrod3")) +
      # scale_fill_manual(name = "hello", values = c("Predicted" = "white")) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.title = element_blank(),
            legend.background = element_rect(fill = "transparent", colour = "transparent"),
            # legend.position = "none", 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.key.size = unit(.25, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      # guides(color = guide_legend(override.aes = list(size = 1.25))) +
      facet_rep_grid(.~deck,
                     labeller = labeller(deck = c("1" = "Deck A", "2" = "Deck B",
                                                  "3" = "Deck C", "4" = "Deck D")))
dev.off()  
```



## BetaF-Only Simulation
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "betaF_Simulations.tiff"),
     width = 6.5, height = 3, units = "in", res = 300)

  # data
  betaF_simulations %>% 
    select(everything(), deck = card) %>% 
    mutate(choice = case_when(choice == 2 ~ 0, T ~ choice)) %>% 
    group_by(simulation, trial, deck) %>% 
    reframe(proportion = mean(choice)) %>% 
    # plotting
    ggplot(aes(x = trial, color = simulation)) +
      # geoms
      # geom_point(aes(y = proportion, color = "Predicted", fill = "Predicted"),
      #            shape = 21, size = .75) +
      geom_line(aes(y = proportion)) +
      # scales
      scale_y_continuous(limits = c(0,1), expand = c(0,0),
                         breaks = seq(0,1,.25)) +
      # scale_color_manual(name = "hello", values = c("Predicted" = "goldenrod3")) +
      # scale_fill_manual(name = "hello", values = c("Predicted" = "white")) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.title = element_blank(),
            legend.background = element_rect(fill = "transparent", colour = "transparent"),
            # legend.position = "none", 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.key.size = unit(.25, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      # guides(color = guide_legend(override.aes = list(size = 1.25))) +
      facet_rep_grid(.~deck,
                     labeller = labeller(deck = c("1" = "Deck A", "2" = "Deck B",
                                                  "3" = "Deck C", "4" = "Deck D")))
dev.off()  
```



## K-Only Simulation
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "K_Simulations.tiff"),
     width = 6.5, height = 3, units = "in", res = 300)

  # data
  K_simulations %>% 
    select(everything(), deck = card) %>% 
    mutate(choice = case_when(choice == 2 ~ 0, T ~ choice)) %>% 
    group_by(simulation, trial, deck) %>% 
    reframe(proportion = mean(choice)) %>% 
    # plotting
    ggplot(aes(x = trial, color = simulation)) +
      # geoms
      # geom_point(aes(y = proportion, color = "Predicted", fill = "Predicted"),
      #            shape = 21, size = .75) +
      geom_line(aes(y = proportion)) +
      # scales
      scale_y_continuous(limits = c(0,1), expand = c(0,0),
                         breaks = seq(0,1,.25)) +
      # scale_color_manual(name = "hello", values = c("Predicted" = "goldenrod3")) +
      # scale_fill_manual(name = "hello", values = c("Predicted" = "white")) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.title = element_blank(),
            legend.background = element_rect(fill = "transparent", colour = "transparent"),
            # legend.position = "none", 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.key.size = unit(.25, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      # guides(color = guide_legend(override.aes = list(size = 1.25))) +
      facet_rep_grid(.~deck,
                     labeller = labeller(deck = c("1" = "Deck A", "2" = "Deck B",
                                                  "3" = "Deck C", "4" = "Deck D")))
dev.off()  
```



# ---------------------------------------
# Correlations Between Changes
* These are correlations between changes in parameters
```{r, eval = F}
choice_prop_wide = pivot_wider(choice_proportions,
                               values_from = "choice_proportion",
                               names_from = "session",
                               names_prefix = "session_") %>% 
  mutate(diff = session_2 - session_1) %>% 
  filter(type == "Good")

ind_orl_diffs = bind_rows(data.frame(parameter = "Arew", estimate = orl_posteriors$Arew, iteration = 1:16000),
                          data.frame(parameter = "betaP", estimate = orl_posteriors$betaP, iteration = 1:16000)) %>% 
  pivot_longer(starts_with("estimate"), names_to = c("id", "session"), values_to = "estimate",
               names_sep = "(\\.)", names_prefix = "estimate.",
               names_transform = list(id = as.numeric)) %>% 
  pivot_wider(names_from = "session", values_from = "estimate", names_prefix = "session_") %>% 
  mutate(diff = session_2 - session_1) %>% 
  group_by(parameter, id) %>% 
  reframe(mu_diff = mean(diff))

choice_orl = left_join(choice_prop_wide, ind_orl_diffs)
choice_Arew = filter(choice_orl, parameter == "Arew")
choice_betaP = filter(choice_orl, parameter == "betaP")
cor.test(choice_Arew$diff, choice_Arew$mu_diff)
cor.test(choice_betaP$diff, choice_betaP$mu_diff)
```



```{r, eval = F}
T1_net = apply((choices*outcomes)[,,1], 1, sum)
T2_net = apply((choices*outcomes)[,,2], 1, sum)

t.test(T1_net, T2_net, paired = T)

sum(T1_net)
sum(T2_net,na.rm = T)

negative_outcomes = ifelse(choices*outcomes < 0, 1, 0)
positive_outcomes = ifelse(choices*outcomes >= 0, 1, 0)

T1_negative_outcomes = apply(negative_outcomes[,,1], 1, sum)
T2_negative_outcomes = apply(negative_outcomes[,,2], 1, sum)

t.test(T1_negative_outcomes, T2_negative_outcomes, paired = T)

T1_positive_outcomes = apply(positive_outcomes[,,1], 1, sum)
T2_positive_outcomes = apply(positive_outcomes[,,2], 1, sum)

t.test(T1_positive_outcomes, T2_positive_outcomes, paired = T)
```



# ---------------------------------------
# Correlation with Ratios
```{r}
orl_ratio = data.frame(ID = stan_data$subjIDs,
                       ratio = apply(orl_posteriors$Apun, 2, mean)/
                         apply(orl_posteriors$Arew, 2, mean))

session1_session2 = self_report %>% 
  pivot_wider(names_from = "scale", values_from = "score") %>% 
  left_join(orl_parameters) %>% left_join(ch_prop_sess)
averages = self_report %>% 
  group_by(ID, scale) %>% 
  reframe(score = mean(score, na.rm = T), session = 0) %>% 
  pivot_wider(names_from = "scale", values_from = "score") %>% 
  left_join(orl_parameters) %>% left_join(ch_prop_avg)

combined = bind_rows(session1_session2, averages)

correlations = data.frame()

for(s in unique(combined$session)){
  for(parameter in c("Arew", "Apun", "betaF", "betaP", "K")){
    check_data = combined %>% 
      filter(session == s) %>% 
      select(ID, parameter, Good, Bad) %>% 
      na.omit()
    
    if(nrow(check_data)!=0){
      correlations = run_cor(combined, s, "ORL-Prop", parameter, "Good") %>% 
        bind_rows(correlations)
      correlations = run_cor(combined, s, "ORL-Prop", parameter, "Bad") %>% 
        bind_rows(correlations)
      
      for(scale in unique(self_report$scale)){
        correlations = run_cor(combined, s, "SR-ORL", scale, parameter) %>% 
          bind_rows(correlations)
        correlations = run_cor(combined, s, "SR-Prop", scale, "Good") %>% 
          bind_rows(correlations)
        correlations = run_cor(combined, s, "SR-Prop", scale, "Bad") %>% 
          bind_rows(correlations)
      }
    }
  }
}

correlations = correlations %>% 
  separate(col = "CI", into = c("lower", "upper"), sep = ",") %>% 
  mutate(lower = as.numeric(str_remove(lower, "\\(")),
         upper = as.numeric(str_remove(upper, "\\)")))          
```



# ---------------------------------------
# No Memory Decks Results
```{r, eval = F}
nom_orl_posteriors = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "Joint_ORL_start_noK",
                                  "Joint_ORL_start_noK_posteriors.rds"))
```



## Absolute Reliability
```{r, eval = F}
nom_orl_abs_data = bind_rows(data.frame(parameter = "Arew", session = nom_orl_posteriors$mu_Arew),
                         data.frame(parameter = "Apun", session = nom_orl_posteriors$mu_Apun),
                         data.frame(parameter = "betaF", session = nom_orl_posteriors$mu_betaF),
                         data.frame(parameter = "betaP", session = nom_orl_posteriors$mu_betaP)) %>% 
  mutate(session.diff = session.2 - session.1) %>% 
  pivot_longer(starts_with("session"),
               names_to = "session", values_to = "estimate", names_prefix = "session.") %>% 
  group_by(parameter, session) %>% 
  mutate(mu = mean(estimate),
         lower50 = HDIofMCMC(estimate, credMass = .5)[1],
         upper50 = HDIofMCMC(estimate, credMass = .5)[2],
         lower95 = HDIofMCMC(estimate)[1],
         upper95 = HDIofMCMC(estimate)[2],
         parameter = factor(parameter, ordered = T,
                            levels = c("Arew", "Apun", "betaF", "betaP")),
         parameter_lab = factor(parameter,
                                levels = c("Arew", "Apun", "betaF", "betaP"),
                                labels = c(expression(paste(italic(A),"+",sep="")),
                                           expression(paste(italic(A),"-",sep="")),
                                           expression(paste("\u03B2",italic(f),sep="")),
                                           expression(paste("\u03B2",italic(b),sep="")))),
         parameter_lab = case_when(session == "diff" ~ parameter_lab, T ~ NA))

nom_orl_abs_scales =
  list(parameter == "Arew" & session != "diff" ~
         scale_x_continuous(limits = c(0, .3), expand = expansion(add = c(0, 0)),
                            breaks = seq(0, .3, .15), labels = c("0", ".15", ".3")),
       parameter == "Arew" & session == "diff" ~
         scale_x_continuous(limits = c(-.3, .3), expand = expansion(add = c(0, 0)),
                            breaks = seq(-.3, .3, .3), labels = c("-.3", "0", ".3")),
       
       parameter == "Apun" & session != "diff" ~
         scale_x_continuous(limits = c(.05, .15), expand = expansion(add = c(0, 0)),
                            breaks = seq(.05, .15, .05), labels = c(".05", ".1", ".15")),
       parameter == "Apun" & session == "diff" ~
         scale_x_continuous(limits = c(-.05, .05), expand = expansion(add = c(0, 0)),
                            breaks = seq(-.05, .05, .05), labels = c("-.05", "0", ".05")),
       
       parameter == "betaF" & session != "diff" ~
         scale_x_continuous(limits = c(0, 6), expand = expansion(add = c(0, 0)),
                            breaks = seq(0, 6, 3), labels = c(".05", ".1", ".15")),
       parameter == "betaF" & session == "diff" ~
         scale_x_continuous(limits = c(-3, 3), expand = expansion(add = c(0, 0)),
                            breaks = seq(-3, 3, 3), labels = c("-3", "0", "3")),
       
       parameter == "betaP" & session != "diff" ~
         scale_x_continuous(limits = c(0, 3), expand = expansion(add = c(0, 0)),
                            breaks = seq(0, 3, 1.5), labels = c("0", "1.5", "3")),
       parameter == "betaP" & session == "diff" ~
         scale_x_continuous(limits = c(-2, 2), expand = expansion(add = c(0, 0)),
                            breaks = seq(-2, 2, 2), labels = c("-2", "0", "2")))
```



```{r, eval = F}
nom_orl_abs_plot = nom_orl_abs_data %>% 
  ggplot(aes(x = estimate)) +
    # geoms
    geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                   linewidth = .1, bins = 50) +
  
    geom_hline(yintercept = 0) +
    geom_vline(aes(xintercept = mu), color = "red2", linewidth = .25) +
    geom_vline(aes(xintercept = lower95), color = "red", linetype = "dashed", linewidth = .25) +
    geom_vline(aes(xintercept = upper95), color = "red", linetype = "dashed", linewidth = .25) +
    # scales
    scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
    # themes
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.margin = unit(c(.5, .5, .3, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(0, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(parameter~session, scales = "free",
                   nrow = 5, ncol = 3) +
    facetted_pos_scales(x = nom_orl_abs_scales)
```



```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "nom_ORL_Abs_Reliability.tiff"),
     width = 7, height = 10, units = "cm", res = 300)

  grid.newpage()
  pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
  grid.draw(nom_orl_abs_plot)
  
  # text
  grid.text(c("Session 1", "Session 2", " Session 2-1"),
            x = c(.2, .515, .81), y = .98,
            gp = gpar(fontsize = 9.5))
  grid.text(c(expression(paste(italic(A),"+",sep="")),
              expression(paste(italic(A),"-",sep="")),
              expression(paste("\u03B2",italic(f),sep="")),
              expression(paste("\u03B2",italic(b),sep=""))),
            x = rep(.93, 5), y = c(.87, .655, .43, .22),
            gp = gpar(fontsize = 9.5))
  
dev.off()
```



## Relative Reliability
```{r, eval = F}
print("R_Arew")
apply(nom_orl_posteriors$R_Arew, c(2,3), mean)
apply(nom_orl_posteriors$R_Arew, c(2,3), HDIofMCMC)
print("R_Apun")
apply(nom_orl_posteriors$R_Apun, c(2,3), mean)
apply(nom_orl_posteriors$R_Apun, c(2,3), HDIofMCMC)
print("R_betaF")
apply(nom_orl_posteriors$R_betaF, c(2,3), mean)
apply(nom_orl_posteriors$R_betaF, c(2,3), HDIofMCMC)
print("R_betaP")
apply(nom_orl_posteriors$R_betaP, c(2,3), mean)
apply(nom_orl_posteriors$R_betaP, c(2,3), HDIofMCMC)
```



```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "nom_ORL_Rel_Reliability.tiff"),
     width = 14.6, height = 4, units = "cm", res = 300)

  bind_rows(data.frame(parameter = "Arew", r = nom_orl_posteriors$R_Arew[,2,1]),
            data.frame(parameter = "Apun", r = nom_orl_posteriors$R_Apun[,2,1]),
            data.frame(parameter = "betaF", r = nom_orl_posteriors$R_betaF[,2,1]),
            data.frame(parameter = "betaP", r = nom_orl_posteriors$R_betaP[,2,1])) %>% 
    mutate(parameter = factor(parameter,
                              levels = c("Arew", "Apun", "betaF", "betaP"),
                              labels = c(expression(paste(italic(A),"+",sep="")),
                                         expression(paste(italic(A),"-",sep="")),
                                         expression(paste("\u03B2",italic(f),sep="")),
                                         expression(paste("\u03B2",italic(b),sep=""))))) %>% 
    group_by(parameter) %>% 
    mutate(mu_r = mean(r), lower = HDIofMCMC(r)[1], upper = HDIofMCMC(r)[2],
           below_0 = paste0(round(mean(r<0)*100), "% < 0"), above_0 = paste0(round(mean(r>0)*100), "% > 0"),
           height = max(density(r)$x)*.025) %>% 
    ggplot(aes(x = r)) +
      # geoms
      geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                     linewidth = .1, bins = 50) +
      geom_text_npc(aes(npcx = "left", npcy = "top", label = below_0),
                    size = 2, vjust = -1.43) +
      geom_text_npc(aes(npcx = "right", npcy = "top", label = above_0),
                    size = 2, vjust = -1.43) +
      # geom_text_npc(aes(npcx = "left", npcy = "top", label = below_0),
      #               size = 2, hjust = -3, vjust = -1.43) +
      # geom_text_npc(aes(npcx = "right", npcy = "top",
      #                   label = rCI_lab), size = 2, vjust = -1.05) +
      geom_hline(yintercept = 0) +
      geom_vline(aes(xintercept = mu_r), color = "red2", linewidth = .4) +
      geom_errorbarh(aes(xmin = lower, xmax = upper,
                         y = height),
                         color = "red", linewidth = .4) +
      # scales
      scale_x_continuous(limits = c(-1,1), expand = c(0,0), breaks = seq(-1,1,.5),
                         labels = c("-1","-.5","0",".5", "1")) +
      scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
      # themes
      labs(x = "Reliability Coefficient", y = "Density") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black"),
            axis.ticks.x = element_line(color = "black"),
            axis.line.x = element_line(color = "transparent"),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank(),
            axis.line.y = element_blank(),
            plot.margin = unit(c(.1, .3, .1, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            strip.text.x = element_text(size = 12, vjust = 1.5),
            strip.text.y = element_blank(),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      facet_rep_grid(.~parameter, scales = "free",
                     labeller = label_parsed)
dev.off()
```



## Self-Report Correlations
```{r}
nom_orl_parameters = data.frame(ID = stan_data$subjIDs,
                                Arew = apply(nom_orl_posteriors$Arew, c(2,3), mean),
                                Apun = apply(nom_orl_posteriors$Apun, c(2,3), mean),
                                betaF = apply(nom_orl_posteriors$betaF, c(2,3), mean),
                                betaP = apply(nom_orl_posteriors$betaP, c(2,3), mean),
                                Arew.0 = apply(nom_orl_posteriors$Arew, 2, mean),
                                Apun.0 = apply(nom_orl_posteriors$Apun, 2, mean),
                                betaF.0 = apply(nom_orl_posteriors$betaF, 2, mean),
                                betaP.0 = apply(nom_orl_posteriors$betaP, 2, mean)) %>% 
  pivot_longer(starts_with(c("Arew", "Apun", "betaF", "betaP")),
               names_to = c("parameter", "session"), values_to = "estimate",
               names_sep = "\\.", names_transform = list(session = as.numeric)) %>% 
  pivot_wider(names_from = "parameter", values_from = "estimate") %>% 
  mutate(ratio = Apun/Arew)

nom_session1_session2 = self_report %>% 
  pivot_wider(names_from = "scale", values_from = "score") %>% 
  left_join(nom_orl_parameters)
nom_averages = self_report %>% 
  group_by(ID, scale) %>% 
  reframe(score = mean(score, na.rm = T), session = 0) %>% 
  pivot_wider(names_from = "scale", values_from = "score") %>% 
  left_join(nom_orl_parameters)

nom_combined = bind_rows(session1_session2, averages)
```



```{r}
set.seed(20230320)

# RUN SELF-REPORT/ORL CORRELATIONS
SR_nom_ORL_correlations = data.frame()

for(s in unique(nom_combined$session)){
  for(scale in unique(self_report$scale)){
    for(parameter in c("Arew", "Apun", "betaF", "betaP")){
      cur_data = nom_combined %>% 
        filter(session == s) %>% 
        select(ID, all_of(scale), all_of(parameter)) %>% 
        na.omit()
      
      if(nrow(cur_data)!=0){
        SR_nom_ORL_correlations = run_cor(cur_data, s, "SR-ORL", scale, parameter) %>% 
          bind_rows(SR_nom_ORL_correlations)
      }
    }
  }
}

# RUN Play Proportion/ORL CORRELATIONS
prop_nom_ORL_correlations = data.frame()

for(s in unique(combined$session)){
  for(prop in c("Good", "Bad")){
    for(parameter in c("Arew", "Apun", "betaF", "betaP")){
      cur_data = combined %>% 
        filter(session == s) %>% 
        select(ID, all_of(prop), all_of(parameter)) %>% 
        na.omit()
      
      if(nrow(cur_data)!=0){
        prop_nom_ORL_correlations = run_cor(cur_data, s, "ORL-Prop", parameter, prop) %>% 
          bind_rows(prop_nom_ORL_correlations)
      }
    }
  }
}

nom_correlations = bind_rows(SR_nom_ORL_correlations,
                             prop_nom_ORL_correlations) %>% 
  separate(col = "CI", into = c("lower", "upper"), sep = ",") %>% 
  mutate(lower = as.numeric(str_remove(lower, "\\(")),
         upper = as.numeric(str_remove(upper, "\\)")),
         sig = case_when(lower < 0 & upper < 0 ~ "*",
                         lower > 0 & upper > 0 ~ "*",
                         lower < 0 & upper < .01 ~ "#",
                         lower > .01 & upper > 0 ~ "#",
                         T ~ ""))

saveRDS(nom_correlations, here("1_IGT_PP", "Data", "2_Fitted",
                           "Joint_ORL_start_noK", paste0("Joint_ORL_start_noK_correlations.rds")))
```



## Save Correlations
```{r}
nom_correlations = readRDS(here("1_IGT_PP", "Data", "2_Fitted",
                            "Joint_ORL_start_noK", paste0("Joint_ORL_start_noK_correlations.rds")))

nom_correlations %>% 
  mutate(# MAKE NICE LABEL
         estimate = round(r,2),
         estimate_lab = paste(ifelse(sign(estimate)==1," ","-"), stri_pad_right(str_remove(abs(estimate), "^0+"),
                                                                                width = 3, pad = "0"),sep=""),
         lower = round(as.numeric(str_remove(lower, "\\(")),2),
         upper = round(as.numeric(str_remove(upper, "\\)")),2),
         
         lower_lab = paste(ifelse(sign(lower)==1,"","-"), stri_pad_right(str_remove(abs(lower), "^0+"),
                                                                         width = 3, pad = "0"),sep=""),
         
         upper_lab = paste(ifelse(sign(upper)==1,"","-"), stri_pad_right(str_remove(abs(upper), "^0+"),
                                                                         width = 3, pad = "0"),sep=""),
         lower_lab = case_when(lower_lab == "-000" ~ "-.00", T ~ lower_lab),
         upper_lab = case_when(upper_lab == "-000" ~ "-.00", T ~ upper_lab),
         estimate_lab = case_when(estimate_lab == "-000" ~ "-.00", T ~ estimate_lab),
         estimate_CI = paste(estimate_lab," [",lower_lab,",",upper_lab,"]",sep=""),
         # SORTING
         SR_sort = case_when(x == "bastot" ~ 1, x == "basdrive" ~ 2, x == "basfunsk" ~ 3, 
                             x == "basrewres" ~ 4, x == "bis" ~ 5, x == "panas_pa" ~ 6, 
                             x == "panas_na" ~ 7, x == "masqGDA" ~ 8, x == "masqAA" ~ 9, 
                             x == "masqGDD" ~ 10, x == "masqAD" ~ 11, x == "shaps_tot" ~ 12,
                             x == "prdep_tot" ~ 13)) %>% 
  write.csv(here("1_IGT_PP", "Data", "2_Fitted",
                 "Joint_ORL_start_noK", paste0("Joint_ORL_start_noK_correlations.csv")))
```



# ---------------------------------------
# BELOW NOT FINISHED/USED
# ---------------------------------------
# ---------------------------------------
# Relations to Behavior
## Calculate Choice Proportions
```{r}
choice = ifelse(stan_data$choice == 1, 1, ifelse(stan_data$choice == 2, 0, NA))

card_proportions = array(data = NA, dim = c(49, 4, 2))
good_proportions = matrix(data = NA, nrow = 49, ncol = 2)
play_proportions = matrix(data = NA, nrow = 49, ncol = 2)

for(i in 1:49){
  for(s in 1:2){
    good_proportions[i,s] = mean(choice[i,,s][stan_data$card[i,,s] == 3 | stan_data$card[i,,s] == 4], na.rm = T)
    play_proportions[i,s] = mean(choice[i,,s] == 1, na.rm = T)
    for(c in 1:4){
      card_proportions[i,c,s] = mean(choice[i,,s][stan_data$card[i,,s] == c], na.rm = T)
    }
  }
}
```



## Correlations w/Card Proportions
```{r}
for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
    print(paste(" ", parameter))
    for(c in 1:4){
      card = ifelse(c == 1, "    Net = -750, Win Freq = 15, Lose Freq = 15",
                    ifelse(c == 2, "    Net = -750, Win Freq = 27, Lose Freq = 3",
                           ifelse(c == 3, "    Net = +600, Win Freq = 15, Lose Freq = 6",
                                  "    Net = +750, Win Freq = 27, Lose Freq = 3")))
      print(paste(card, ": r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], card_proportions[,c,s],
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
    }
  }
}
```



## Correlations w/Good Proportions
```{r}
for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
      print(paste("  ", parameter, " vs Proportion Good Cards: r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], good_proportions[,s],
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
  }
}
```



## Correlations w/Play Proportions
```{r}
for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
      print(paste("  ", parameter, " vs Proportion Played: r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], abs(play_proportions[,s]-.5),
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
  }
}
```



## Correlations w/Net Gain
```{r}
net_gains = apply(stan_data$outcome, c(1,3), sum)

for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
      print(paste("  ", parameter, " vs Net Gain: r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], net_gains[,s],
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
  }
}
print("Change in Gain")
for(parameter in person_parameters){
    print(paste("  ", parameter, " vs Delta Net Gain: r = ",
                round(cor(apply(orl_posteriors[[parameter]], 2, mean), (net_gains[,2]-net_gains[,1]),
                          use = "pairwise.complete.obs"), 2),
                sep = ""))
}
```


# ---------------------------------------
# ---------------------------------------
# ORL Choice Predictions
```{r}
outcomes = read.csv(here("1_IGT_PP", "Data", "0_Raw", "outcomes.csv")) %>% 
  as.matrix()
parameter_mus = data.frame(Arew = orl_posteriors$mu_Arew,
                           Apun = orl_posteriors$mu_Apun,
                           K = orl_posteriors$mu_K,
                           betaF = orl_posteriors$mu_betaF,
                           betaP = orl_posteriors$mu_betaP) %>% 
  pivot_longer(everything(), names_to = c("parameter", "session"),
               values_to = "estimate", names_sep = "\\.",
               names_transform = list(session = as.integer)) %>% 
  group_by(parameter, session) %>% 
  reframe(mu = mean(estimate),
          lower = HDIofMCMC(estimate)[1],
          upper = HDIofMCMC(estimate)[2])
```



## Softmax Function
```{r}
softmax = function(values){
  return(exp(values) / sum(exp(values)))
}
```



## Simulate Function
```{r}
simulate_orl = function(Arew_list, Apun_list, K_list, betaF_list, betaP_list,
                        N = 500, Trials = 30){
  
  combinations = length(levels(interaction(Arew_list, Apun_list, K_list,
                                           betaF_list, betaP_list)))
  
  EVs = array(dim = c(Trials, 4, combinations, N))
  colnames(EVs) = c("Deck_A", "Deck_B", "Deck_C", "Deck_D")
  
  probabilities = array(dim = c(Trials, 4, combinations, N))
  colnames(probabilities) = c("Deck_A", "Deck_B", "Deck_C", "Deck_D")
  
  choices = array(data = NA, dim = c(Trials, combinations, N))
  
  net = array(data = 0, dim = c(Trials, combinations, N))
  parameters = matrix(data = NA, nrow = combinations, ncol = 5,
                      dimnames = list(NULL, c("Arew", "Apun", "K", "betaF", "betaP")))
  
  EVs[1,,,] = c(0, 0, 0, 0)
  
  
  set.seed(20230504)
  for(i in 1:N){
    c = 1
    for(Arew in Arew_list){
      for(Apun in Apun_list){
        for(K in K_list){
          for(betaF in betaF_list){
            for(betaP in betaP_list){
        
              # save parameter set
              parameters[c,"Arew"] = Arew
              parameters[c,"Apun"] = Apun
              parameters[c,"K"] = K
              parameters[c,"betaF"] = betaF
              parameters[c,"betaP"] = betaP
              
              # set initial values for parameter set
              ev = rep(0, 4)
              ef = rep(0, 4)
              pers = rep(0, 4)
              utility = rep(0, 4)
              K_tr = 3^K - 1
              
              for(t in 1:Trials){ # loop through trials
                probabilities[t,,c,i] = softmax(utility) # calculate probability of choosing each card
                choices[t,c,i] = sample(1:4, 1, prob = probabilities[t,,c,i]) # simulate choice based on probabilites
                
                if(t < Trials){ # if it's not the last trial, calculate next trials utility
                  # calculate prediction error
                  PEval = outcomes[t,choices[t,c,i]] - utility[choices[t,c,i]]
                  PEfreq = sign(outcomes[t,choices[t,c,i]]) - ef[choices[t,c,i]]
                  PEfreq_fic = -1*sign(outcomes[t,choices[t,c,i]])/3 - ef
                  
                  ef_choice = ef[choices[t,c,i]]
                  ev_choice = ev[choices[t,c,i]]
                  
                  if(outcomes[t,choices[t,c,i]] >= 0) { # if positive outcome for choice
                    # update EF for all decks
                    ef = Apun*PEfreq_fic 
                    # update EF for chosen deck
                    ef[choices[t,c,i]] = ef_choice*Arew*PEfreq
                    ev[choices[t,c,i]] = ev_choice*Arew*PEval
                  } else { # if negative outcome for choice
                    # update EF for all decks
                    ef = Arew*PEfreq_fic 
                    # update EF for chosen deck
                    ef[choices[t,c,i]] = ef_choice*Apun*PEfreq
                    ev[choices[t,c,i]] = ev_choice*Apun*PEval
                  }
                  pers[choices[t,c,i]] = 1
                  pers = pers / (1+K_tr)
                  
                  utility = ev + ef*betaF + pers*betaP
                  # utility = ev + ef*betaF
                  
                  EVs[t+1,,c,i] = utility
                  net[t+1,c,i] = net[t,c,i] + outcomes[t,choices[t,c,i]]
                }
              }
              c = c + 1
            }
          }
        }
      }
    }
  }

  EV_df = data.frame()
  probabilities_df = data.frame()
  net_df = data.frame()
  choices_df = data.frame()
  
  for(c in 1:combinations){
    
    cur_parameters = data.frame(Arew = parameters[c,"Arew"], Apun = parameters[c,"Apun"],
                                K = parameters[c,"K"], betaF = parameters[c,"betaF"],
                                betaP = parameters[c,"betaP"])
    
    # Combine expected values
    c_EV = data.frame(apply(EVs, c(1,2,3), mean)[,,c], combination = c) %>% 
      cbind(cur_parameters) %>% 
      mutate(trial = 1, trial = cumsum(trial))
    EV_df = bind_rows(EV_df, c_EV)
    
    # Combine probabilities
    c_probabilities = data.frame(apply(probabilities, c(1,2,3), mean)[,,c], combination = c) %>% 
      cbind(cur_parameters) %>% 
      mutate(trial = 1, trial = cumsum(trial))
    probabilities_df = bind_rows(probabilities_df, c_probabilities)
    
    # Combine probabilities
    c_net = data.frame(net = apply(net, c(1,2), mean)[,c], combination = c) %>% 
      cbind(cur_parameters) %>% 
      mutate(trial = 1, trial = cumsum(trial))
    net_df = bind_rows(net_df, c_net)
    
    # Combine choice proportions
    c_choices = data.frame(Deck_A = mean(choices[,c,]==1), Deck_B = mean(choices[,c,]==2),
                           Deck_C = mean(choices[,c,]==3), Deck_D = mean(choices[,c,]==4),
                           combination = c) %>% 
      cbind(cur_parameters)
    choices_df = bind_rows(choices_df, c_choices)
  }
  EV_df = EV_df %>% 
    pivot_longer(cols = starts_with("Deck_"), names_prefix = "Deck_",
                 names_to = "deck", values_to = "EV")
  probabilities_df = probabilities_df %>% 
    pivot_longer(cols = starts_with("Deck_"), names_prefix = "Deck_",
                 names_to = "deck", values_to = "probability")
  
  return(list(EV = EV_df,
              probabilities = probabilities_df,
              net = net_df,
              choices = choices_df))
}
```



## Simulate & Plot
```{r}
simulations = simulate_orl(# VARYING
                           Arew_list = filter(parameter_mus, parameter == "Arew")$mu,
                           # Arew_list = mean(filter(parameter_mus, parameter == "Arew")$mu),
                           Apun_list = mean(filter(parameter_mus, parameter == "Apun")$mu),
                           K_list = mean(filter(parameter_mus, parameter == "K")$mu),
                           betaF_list = mean(filter(parameter_mus, parameter == "betaF")$mu),
                           # betaP_list = mean(filter(parameter_mus, parameter == "betaP")$mu),
                           betaP_list = filter(parameter_mus, parameter == "betaP")$mu,
                           N = 500,
                           Trials = 30)
hor = "betaP"
ver = "Arew"
# ver = "betaP"

tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
          "ORL Choice Predictions.tiff"),
     width = 20, height = 10, units = "cm", res = 300)
  simulations$choices %>% 
    pivot_longer(cols = starts_with("Deck"), names_to = "deck", values_to = "proportion",
                 names_prefix = "Deck_") %>% 
    mutate(good = )
    ggplot(aes(x = deck, y = proportion, fill = deck)) +
      geom_bar(stat = "identity", color = "black") +
      scale_y_continuous(limits = c(0,.5), expand = c(0,0)) +
      labs(x = "Deck", y = "Choice Proportion") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.title = element_blank()) +
      facet_rep_grid(reformulate(ver, hor), labeller = label_both)
dev.off()
```



# ---------------------------------------
# ---------------------------------------
## Prep Data
```{r}
# Card matrix
cards = stan_data$card


# Recode choice data
choices = ifelse(stan_data$choice == 2, 0, ifelse(stan_data$choice == 1, 1, NA))


# Trial matrix (to skip when participant wasn't there)
trials = stan_data$Tsubj


# Extract parameters
predicted_values = ifelse(orl_posteriors$choice_pred == 2, 0, 1)


# For binding together posterior predictions
acomb = function(...) abind(..., along=3)
bcomb = function(...) abind(..., along=4)
```



### Choice Data
```{r}
# Calculates group-level choice proportions into a 30 (trial) x 4 (card) x 2 (session) matrix
choice_proportions = foreach(s = 1:2, .combine = "acomb") %do% {
  foreach(c = 1:4, .combine = "cbind") %do% {
    temp = foreach(i = 1:49, .combine = "rbind") %do% {
        choices[i, cards[i, , s] == c, s]
    } %>% colMeans(na.rm = T)
  }
}
```



### Predicted Values
```{r}
predicted_proportions = foreach(s = 1:2, .combine = "bcomb") %do% {
  foreach(c = 1:4, .combine = "acomb") %do% {
    foreach(i = 1:49, .combine = "acomb") %do% {
      if(trials[i, s] > 0){
        predicted_values[ , i, cards[i, , s] == c, s]
      }
    } %>% 
      apply(., c(1,2), mean)
  }
}
```




## Plot Function
```{r}
make_plot = function(y_data, yrep_data, top, right,
                     x_axis_txt, y_axis_txt, deck){
  if(top){
    custom_margin = margin(t = 1, r = -.5, b = -.5, l = -.5, unit = "lines")
  } else {
    custom_margin = margin(t = -.5, r = -.5, b = 1, l = -.5, unit = "lines")
  }
  if(right == 1 | right == 2){
    session_text = paste("Session", right)
  } else {
    session_text = ""
  }
  
  ppc_intervals(x = 1:length(y_data),
                y = y_data*100,
                yrep = yrep_data*100,
                prob = 0.50, 
                prob_outer = .80) +
    geom_text(aes(x = 30, y = 5, label = session_text),
              color = "black", hjust = 1, vjust = 0, check_overlap = T) +
    scale_x_continuous(expand = c(0, 0), limits = c(0, 31), breaks = seq(0, 30, 5)) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 100), breaks = seq(0, 100, 25)) +
    theme_classic() +
    labs(x = "Trial", y = "Proportion Played", title = deck) +
    theme(legend.position = "none",
          axis.title = element_blank(),
          axis.text.x = element_text(color = x_axis_txt, size = 12),
          axis.text.y = element_text(color = y_axis_txt, size = 12),
          plot.title = element_text(hjust = .5, size = 12),
          plot.margin = custom_margin,
          plot.background = element_rect(fill = "transparent", colour = "transparent"))
}
```



## Make Plot
```{r}
# Set color scheme for bayesplot (it is a global setting)
color_scheme_set("viridisC")

plots = ggarrange(make_plot(choice_proportions[, 1, 1], predicted_proportions[,, 1, 1],
                            T, 0, "transparent", "black", "Deck A"),
                  make_plot(choice_proportions[, 2, 1], predicted_proportions[,, 2, 1],
                            T, 0, "transparent", "transparent", "Deck B"),
                  make_plot(choice_proportions[, 3, 1], predicted_proportions[,, 3, 1],
                            T, 0, "transparent", "transparent", "Deck C"),
                  make_plot(choice_proportions[, 4, 1], predicted_proportions[,, 4, 1],
                            T, 1, "transparent", "transparent", "Deck D"),
                  
                  make_plot(choice_proportions[, 1, 2], predicted_proportions[,, 1, 2],
                            F, 0, "black", "black", ""),
                  make_plot(choice_proportions[, 2, 2], predicted_proportions[,, 2, 2],
                            F, 0, "black", "transparent", ""),
                  make_plot(choice_proportions[, 3, 2], predicted_proportions[,, 3, 2],
                            F, 0, "black", "transparent", ""),
                  make_plot(choice_proportions[, 4, 2], predicted_proportions[,, 4, 2],
                            F, 2, "black", "transparent", ""),
                  nrow = 2, ncol = 4)
```



## Save Plot
```{r}
tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots", "PPC.tiff"),
     width = 25, height = 10, units = "cm", res = 300)

  grid.newpage()
  pushViewport(viewport(x = .5, y = .5, width = .9, height = .9))
  grid.draw(plots)
  popViewport()
  
  
  # x axis
  grid.text("Trial",
            x = .5125, y = .05,
            gp = gpar(fontsize = 16))
  # y axis
  grid.text("% Played",
            x = .0225, y = .5,
            gp = gpar(fontsize = 16),
            rot = 90)
dev.off()
```



# ---------------------------------------
# Correlations with Behavior




























## Calculate Person-Level Choice Proportions
```{r}
card_proportions = array(data = NA, dim = c(49, 4, 2))
good_proportions = matrix(data = NA, nrow = 49, ncol = 2)
bad_proportions = matrix(data = NA, nrow = 49, ncol = 2)
play_proportions = matrix(data = NA, nrow = 49, ncol = 2)

for(i in 1:49){
  for(s in 1:2){
    good_proportions[i,s] = mean(choices[i,,s][stan_data$card[i,,s] == 3 | stan_data$card[i,,s] == 4], na.rm = T)
    bad_proportions[i,s] = mean(choices[i,,s][stan_data$card[i,,s] == 1 | stan_data$card[i,,s] == 2], na.rm = T)
    play_proportions[i,s] = mean(choices[i,,s] == 1, na.rm = T)
    for(c in 1:4){
      card_proportions[i,c,s] = mean(choices[i,,s][stan_data$card[i,,s] == c], na.rm = T)
    }
  }
}
dimnames(card_proportions) = list(c(1:49), c(1:4), c(1:2))
```



## Calculate Person-Level Estimates
```{r}
orl_posterior_means = list()

for(parameter in c("Arew", "Apun", "K", "betaF", "betaP")){
  orl_posterior_means[[parameter]] = apply(orl_posteriors[[parameter]], c(2,3), mean)
}
```



## Calculate Correlations
```{r, eval = F}
set.seed(20230630)
correlations = data.frame()

for(s in 1:2){
  for(parameter in c("Arew", "Apun", "K", "betaF", "betaP")){
    
    # good proportions
    curr_orl = orl_posterior_means[[parameter]][,s][!is.na(good_proportions[,s])]
    curr_bx = good_proportions[,s][!is.na(good_proportions[,s])]
    corr = boot.cor.bca(x = curr_orl,
                        y = curr_bx,
                        null.hyp = NULL,
                        alternative = c("two.sided", "less", "greater"),
                        conf.level = 0.95, type = NULL, R = 9999)
    
    correlations = data.frame(proportion = "good",
                              session = s,
                              card = NA,
                              parameter = parameter,
                              r = corr$Observed,
                              CI = corr$Confidence.interval) %>%
      bind_rows(correlations)
    
    # bad proportions
    curr_orl = orl_posterior_means[[parameter]][,s][!is.na(bad_proportions[,s])]
    curr_bx = bad_proportions[,s][!is.na(bad_proportions[,s])]
    corr = boot.cor.bca(x = curr_orl,
                        y = curr_bx,
                        null.hyp = NULL,
                        alternative = c("two.sided", "less", "greater"),
                        conf.level = 0.95, type = NULL, R = 9999)
    
    correlations = data.frame(proportion = "bad",
                              session = s,
                              card = NA,
                              parameter = parameter,
                              r = corr$Observed,
                              CI = corr$Confidence.interval) %>%
      bind_rows(correlations)
    
    # play proportions
    curr_orl = orl_posterior_means[[parameter]][,s][!is.na(play_proportions[,s])]
    curr_bx = abs(play_proportions[,s][!is.na(play_proportions[,s])]-.5)
    corr = boot.cor.bca(x = curr_orl,
                        y = curr_bx,
                        null.hyp = NULL,
                        alternative = c("two.sided", "less", "greater"),
                        conf.level = 0.95, type = NULL, R = 9999)
    
    correlations = data.frame(proportion = "play",
                              session = s,
                              card = NA,
                              parameter = parameter,
                              r = corr$Observed,
                              CI = corr$Confidence.interval) %>%
      bind_rows(correlations)
      
    for(c in 1:4){
      # card proportions
      curr_orl = orl_posterior_means[[parameter]][,s][!is.na(card_proportions[,c,s])]
      curr_bx = card_proportions[,c,s][!is.na(card_proportions[,c,s])]
      corr = boot.cor.bca(x = curr_orl,
                          y = curr_bx,
                          null.hyp = NULL,
                          alternative = c("two.sided", "less", "greater"),
                          conf.level = 0.95, type = NULL, R = 9999)
      
      correlations = data.frame(proportion = "card",
                                session = s,
                                card = c,
                                parameter = parameter,
                                r = corr$Observed,
                                CI = corr$Confidence.interval) %>%
        bind_rows(correlations)
    }
  }
}
saveRDS(correlations, here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots", "bx_correlations.RDS"))
```



## Plot
```{r}
correlations = readRDS(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots", "bx_correlations.RDS")) %>% 
    # label parameters with specific text %>% 
    separate(col = "CI", into = c("lower", "upper"), sep = ",") %>% 
    mutate(card_lab = recode(card, "1" = "A", "2" = "B", "3" = "C", "4" = "D"),
           card_lab = case_when(parameter == "K" ~ card_lab),
           r = round(r,2),
           r_lab = paste(ifelse(sign(r)==1," ","-"), stri_pad_right(str_remove(abs(r), "^0+"),
                                                                     width = 3, pad = "0"),sep=""), 
           lower = round(as.numeric(str_remove(lower, "\\(")),2),
           upper = round(as.numeric(str_remove(upper, "\\)")),2),
           
           lower_lab = paste(ifelse(sign(lower)==1,"","-"), stri_pad_right(str_remove(abs(lower), "^0+"),
                                                                     width = 3, pad = "0"),sep=""), 
           
           upper_lab = paste(ifelse(sign(upper)==1,"","-"), stri_pad_right(str_remove(abs(upper), "^0+"),
                                                                     width = 3, pad = "0"),sep=""),
           rCI = paste("=",r_lab," (",lower_lab,",",upper_lab,")",sep=""))
```



```{r}
orl_df = data.frame(orl_posterior_means) %>%
  mutate(ID = rownames(.)) %>%
  pivot_longer(cols = c(everything(), -ID),
               names_to = c("parameter", "session"),
               names_sep = "\\.",
               names_transform = list(parameter = as.character,
                                      session = as.numeric),
               values_to = "estimate")
```



### Card Proportion
```{r}
# labels = function(x) round(x, 2),
card_df = 
  data.frame(card_proportions[,,]) %>% 
  mutate(ID = rownames(.)) %>% 
  pivot_longer(cols = c(everything(), -ID),
               names_to = c("card", "session"),
               names_sep = "\\.", names_prefix = "X",
               names_transform = list(card = as.numeric,
                                      session = as.numeric),
               values_to = "proportion")


for(sess in 1:2){
  tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots",
            paste0("Card_Proportions_Session", sess, ".tiff")),
       width = 15, height = 12.5, units = "cm", res = 300)
    # display plot in tiff
    print(
      # data
      # temp =
        filter(correlations, proportion == "card") %>% 
        select(-proportion) %>% 
        left_join(orl_df) %>% left_join(card_df) %>% 
        filter(session == sess) %>% 
        # label parameters with specific text
        mutate(card_lab = recode(card, "1" = "A", "2" = "B", "3" = "C", "4" = "D"),
               card_lab = case_when(parameter == "K" ~ card_lab),
               parameter = factor(parameter,
                                  levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                                  labels = c(expression(paste(italic(A),"+",sep="")),
                                             expression(paste(italic(A),"-",sep="")),
                                             expression(paste("\u03B2",italic(f),sep="")),
                                             expression(paste("\u03B2",italic(p),sep="")),
                                             expression(italic(K))))) %>% 
        # plot
        ggplot(aes(x = estimate, y = (proportion*100))) +
          # geoms
          geom_point(size = 1, color = "gray25") +
          geom_smooth(method = "lm", formula = "y ~ x", color = "black", se = F, size = .5,
                    fullrange = T) +
          # scales
          scale_x_continuous(labels = function(x) sprintf("%.2f", round(x, 2)),
                             n.breaks = 3) +
          scale_y_continuous(breaks = c(25, 50, 75, 100), limits = c(25, 100)) +
          # themes
          geom_text_npc(aes(npcx = "right", npcy = "top", label = card_lab), hjust = 0) +
          geom_text_npc(aes(npcx = "middle", npcy = "top",
                            label = rCI), size = 2, vjust = -1) +
          geom_text_npc(aes(npcx = "left", npcy = "top"), label = expression(italic(r)),
                        size = 2, hjust = -1.25, vjust = -1.425) +
          labs(x = "Estimate", y = "% Played") +
          coord_cartesian(clip = "off") +
          theme_classic() +
          theme(axis.text.x = element_text(color = "black"),
                axis.text.y = element_text(color = "black"),
                plot.margin = unit(c(.3, .3, .3, .3), "cm"),
                panel.spacing = unit(0, "cm"),
                strip.background = element_rect(fill = "transparent", colour = "transparent"),
                strip.text.x = element_text(size = 12, vjust = 1.5),
                strip.text.y = element_blank(),
                panel.background = element_rect(fill = "transparent", colour = "transparent"),
                plot.background = element_rect(fill = "transparent", color = "transparent"),
                aspect.ratio = 1) +
          facet_rep_grid(card~parameter, scales = "free",
                         labeller = label_parsed)
    )
  dev.off()
}
```



### Good Proportion
```{r}
# labels = function(x) round(x, 2),
good_df = 
  data.frame(good_proportions) %>% 
  mutate(ID = rownames(.)) %>% 
  pivot_longer(cols = c(everything(), -ID),
               names_to = "session",
               names_prefix = "X",
               names_transform = list(session = as.numeric),
               values_to = "proportion")


tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots", "Good_Proportions.tiff"),
     width = 15, height = 6.25, units = "cm", res = 300)
  # display plot in tiff
  print(
    # data
    # temp =
      filter(correlations, proportion == "good") %>% 
      select(-proportion) %>% 
      left_join(orl_df) %>% left_join(good_df) %>% 
      # label parameters with specific text
      mutate(sess_lab = case_when(parameter == "K" ~ session),
             parameter = factor(parameter,
                                levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                                labels = c(expression(paste(italic(A),"+",sep="")),
                                           expression(paste(italic(A),"-",sep="")),
                                           expression(paste("\u03B2",italic(f),sep="")),
                                           expression(paste("\u03B2",italic(p),sep="")),
                                           expression(italic(K))))) %>% 
      # plot
      ggplot(aes(x = estimate, y = (proportion*100))) +
        # geoms
        geom_point(size = 1, color = "gray25") +
        geom_smooth(method = "lm", formula = "y ~ x", color = "black", se = F, size = .5,
                    fullrange = T) +
        # scales
        scale_x_continuous(labels = function(x) sprintf("%.1f", round(x, 1)),
                           n.breaks = 3) +
        scale_y_continuous(breaks = c(25, 50, 75, 100), limits = c(25, 100)) +
        # themes
        geom_text_npc(aes(npcx = "right", npcy = "top", label = sess_lab), hjust = 0) +
        geom_text_npc(aes(npcx = "middle", npcy = "top",
                          label = rCI), size = 2, vjust = -1) +
        geom_text_npc(aes(npcx = "left", npcy = "top"), label = expression(italic(r)),
                      size = 2, hjust = 0, vjust = -1.425) +
        labs(x = "Estimate", y = "% Good Deck Played") +
        coord_cartesian(clip = "off") +
        theme_classic() +
        theme(axis.text.x = element_text(color = "black"),
              axis.text.y = element_text(color = "black"),
              plot.margin = unit(c(.3, .3, .3, .3), "cm"),
              panel.spacing = unit(0, "cm"),
              strip.background = element_rect(fill = "transparent", colour = "transparent"),
              strip.text.x = element_text(size = 12, vjust = 1.5),
              strip.text.y = element_blank(),
              panel.background = element_rect(fill = "transparent", colour = "transparent"),
              plot.background = element_rect(fill = "transparent", color = "transparent"),
              aspect.ratio = 1) +
        facet_rep_grid(session~parameter, scales = "free",
                       labeller = label_parsed)
  )
dev.off()
```



### Bad Proportion
```{r}
# labels = function(x) round(x, 2),
bad_df = 
  data.frame(bad_proportions) %>% 
  mutate(ID = rownames(.)) %>% 
  pivot_longer(cols = c(everything(), -ID),
               names_to = "session",
               names_prefix = "X",
               names_transform = list(session = as.numeric),
               values_to = "proportion")


tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots", "Bad_Proportions.tiff"),
     width = 15, height = 6.25, units = "cm", res = 300)
  # display plot in tiff
  print(
    # data
    # temp =
      filter(correlations, proportion == "bad") %>% 
      select(-proportion) %>% 
      left_join(orl_df) %>% left_join(bad_df) %>% 
      # label parameters with specific text
      mutate(sess_lab = case_when(parameter == "K" ~ session),
             parameter = factor(parameter,
                                levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                                labels = c(expression(paste(italic(A),"+",sep="")),
                                           expression(paste(italic(A),"-",sep="")),
                                           expression(paste("\u03B2",italic(f),sep="")),
                                           expression(paste("\u03B2",italic(p),sep="")),
                                           expression(italic(K))))) %>% 
      # plot
      ggplot(aes(x = estimate, y = (proportion*100))) +
        # geoms
        geom_point(size = 1, color = "gray25") +
        geom_smooth(method = "lm", formula = "y ~ x", color = "black", se = F, size = .5,
                    fullrange = T) +
        # scales
        scale_x_continuous(labels = function(x) sprintf("%.1f", round(x, 1)),
                           n.breaks = 3) +
        scale_y_continuous(breaks = c(25, 50, 75, 100), limits = c(25, 100)) +
        # themes
        geom_text_npc(aes(npcx = "right", npcy = "top", label = sess_lab), hjust = 0) +
        geom_text_npc(aes(npcx = "middle", npcy = "top",
                          label = rCI), size = 2, vjust = -1) +
        geom_text_npc(aes(npcx = "left", npcy = "top"), label = expression(italic(r)),
                      size = 2, hjust = 0, vjust = -1.425) +
        labs(x = "Estimate", y = "% Bad Deck Played") +
        coord_cartesian(clip = "off") +
        theme_classic() +
        theme(axis.text.x = element_text(color = "black"),
              axis.text.y = element_text(color = "black"),
              plot.margin = unit(c(.3, .3, .3, .3), "cm"),
              panel.spacing = unit(0, "cm"),
              strip.background = element_rect(fill = "transparent", colour = "transparent"),
              strip.text.x = element_text(size = 12, vjust = 1.5),
              strip.text.y = element_blank(),
              panel.background = element_rect(fill = "transparent", colour = "transparent"),
              plot.background = element_rect(fill = "transparent", color = "transparent"),
              aspect.ratio = 1) +
        facet_rep_grid(session~parameter, scales = "free",
                       labeller = label_parsed)
  )
dev.off()
```



# ---------------------------------------
# ---------------------------------------
# From RMD
```{r}
  tiff(here("1_IGT_PP", "Figs_Tables", "Manuscript_Plots", "reliability_coefficients.tiff"),
       width = 15, height = 6.25, units = "cm", res = 300)
  bind_rows(data.frame(parameter = "Arew", r = orl_posteriors$R_Arew[,2,1]),
            data.frame(parameter = "Apun", r = orl_posteriors$R_Apun[,2,1]),
            data.frame(parameter = "betaF", r = orl_posteriors$R_betaF[,2,1]),
            data.frame(parameter = "betaP", r = orl_posteriors$R_betaP[,2,1]),
            data.frame(parameter = "K", r = orl_posteriors$R_K[,2,1])) %>% 
    mutate(parameter = factor(parameter,
                              levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                              labels = c(expression(paste(italic(A),"+",sep="")),
                                         expression(paste(italic(A),"-",sep="")),
                                         expression(paste("\u03B2",italic(f),sep="")),
                                         expression(paste("\u03B2",italic(p),sep="")),
                                         expression(italic(K))))) %>% 
    group_by(parameter) %>% 
    mutate(mu_r = mean(r), lower = HDIofMCMC(r)[1], upper = HDIofMCMC(r)[2],
           mu_r_lab = paste(ifelse(sign(round(mu_r,2))==1," ","-"),
                            stri_pad_right(str_remove(abs(round(mu_r,2)), "^0+"),
                                           width = 3, pad = "0"),sep=""), 
           lower = as.numeric(str_remove(lower, "\\(")),
           upper = as.numeric(str_remove(upper, "\\(")),
           
           lower_lab = paste(ifelse(sign(round(lower,2))==1,"","-"),
                             stri_pad_right(str_remove(abs(round(lower,2)), "^0+"),
                                            width = 3, pad = "0"),sep=""), 
           upper_lab = paste(ifelse(sign(round(upper,2))==1,"","-"),
                             stri_pad_right(str_remove(abs(round(upper,2)), "^0+"),
                                            width = 3, pad = "0"),sep=""),
           upper_lab = case_when(round(upper,2) == 1 ~ "1.00", T ~ upper_lab),
           mu_rCI = paste("=",mu_r_lab," (",lower_lab,",",upper_lab,")",sep="")) %>% 
    ggplot(aes(x = r)) +
      # geoms
      geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                     linewidth = .1, bins = 50) +
      geom_text_npc(aes(npcx = "left", npcy = "top"), label = expression(italic(r)),
                    size = 2, hjust = -3, vjust = -1.425) +
      geom_text_npc(aes(npcx = "middle", npcy = "top",
                        label = mu_rCI), size = 2, vjust = -1) +
      geom_hline(yintercept = 0) +
      geom_vline(aes(xintercept = mu_r), color = "red2") +
      # scales
      scale_x_continuous(limits = c(-1,1), expand = c(0,0), breaks = seq(-1,1,.5),
                         labels = c("-1","-.5","0",".5", "1")) +
      scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
      # themes
      labs(x = "Reliability Coefficient", y = "Density") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black"),
            axis.text.y = element_text(color = "black"),
            axis.ticks = element_line(color = "black"),
            axis.line.x = element_line(color = "transparent"),
            plot.margin = unit(c(.3, .3, .3, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            strip.text.x = element_text(size = 12, vjust = 1.5),
            strip.text.y = element_blank(),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent"),
            aspect.ratio = 1) +
      facet_rep_grid(.~parameter, scales = "free",
                     labeller = label_parsed) +
      geom_segment(aes(x = lower, xend = upper, y = .025, yend = .025), size = 1, color = "red2", linewidth = .5)
dev.off()
```



# ---------------------------------------




# -------------------------------------------
# Results
## PPC Plot
```{r, eval = F}
choice_proportions = calculate_proportions(orl_posteriors, stan_data,
                                           data_type = "data.frame"
                                           # data_type = "list_of_matrices"
                                           )
saveRDS(choice_proportions,
        here("1_IGT_PP", "Data", "2_Fitted", 
             "Joint_ORL", "Joint_ORL_ppcs.rds"))

choice_proportions = readRDS(here("1_IGT_PP", "Data", "2_Fitted", 
                             "Joint_ORL", "Joint_ORL_ppcs.rds"))
```



```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", 
          "Joint_ORL", "Joint_ORL_PPC.tiff"),
     width = 15, height = 8, units = "cm", res = 300)

  # simplify data
  choice_proportions %>% 
    group_by(trial, deck, session) %>% 
    summarise(observed = mean(observed), mu = mean(mu),
              lower50 = mean(lower50), upper50 = mean(upper50),
              lower95 = mean(lower95), upper95 = mean(upper95)) %>%
    # plotting
    ggplot(aes(x = trial,
               group = trial)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95),
                   linewidth = .35, color = "goldenrod3", alpha = .35) +
    geom_linerange(aes(ymin = lower50, ymax = upper50),
                   linewidth = .35, color = "goldenrod3") +
    geom_point(aes(y = mu), shape = 21,
               color = "goldenrod3", fill = "white",
               size = .75) +
    geom_point(aes(y = observed), size = .75) +
    scale_y_continuous(limits = c(0,1), expand = c(0,0),
                       breaks = seq(0,1,.25)) +
    labs(x = "Trial", y = "Proportion Play") +
    theme_classic() +
    theme(axis.text = element_text(color = "black"),
          strip.background = element_blank(),
          panel.spacing.x = unit(-.5,"lines"),
          panel.spacing.y = unit(0,"lines")) +
    facet_rep_grid(session~deck,
                   labeller = labeller(session = c("1" = "Session 1", "2" = "Session 2"),
                                       deck = c("A" = "Deck A", "B" = "Deck B",
                                                "C" = "Deck C", "D" = "Deck D")))
dev.off()
```



## Reliability
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", 
          "Joint_ORL", "Joint_ORL_reliability_coefficients.tiff"),
     width = 15, height = 6.25, units = "cm", res = 300)
  bind_rows(data.frame(parameter = "Arew", r = orl_posteriors$R_Arew[,2,1]),
            data.frame(parameter = "Apun", r = orl_posteriors$R_Apun[,2,1]),
            data.frame(parameter = "betaF", r = orl_posteriors$R_betaF[,2,1]),
            data.frame(parameter = "betaP", r = orl_posteriors$R_betaP[,2,1]),
            data.frame(parameter = "K", r = orl_posteriors$R_K[,2,1])) %>% 
    mutate(parameter = factor(parameter,
                              levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                              labels = c(expression(paste(italic(A),"+",sep="")),
                                         expression(paste(italic(A),"-",sep="")),
                                         expression(paste("\u03B2",italic(f),sep="")),
                                         expression(paste("\u03B2",italic(p),sep="")),
                                         expression(italic(K))))) %>% 
    group_by(parameter) %>% 
    mutate(mu_r = mean(r), lower = HDIofMCMC(r)[1], upper = HDIofMCMC(r)[2],
           mu_r_lab = paste(ifelse(sign(round(mu_r,2))==1," ","-"),
                            stri_pad_right(str_remove(abs(round(mu_r,2)), "^0+"),
                                           width = 3, pad = "0"),sep=""), 
           lower = as.numeric(str_remove(lower, "\\(")),
           upper = as.numeric(str_remove(upper, "\\(")),
           
           lower_lab = paste(ifelse(sign(round(lower,2))==1,"","-"),
                             stri_pad_right(str_remove(abs(round(lower,2)), "^0+"),
                                            width = 3, pad = "0"),sep=""), 
           upper_lab = paste(ifelse(sign(round(upper,2))==1,"","-"),
                             stri_pad_right(str_remove(abs(round(upper,2)), "^0+"),
                                            width = 3, pad = "0"),sep=""),
           upper_lab = case_when(round(upper,2) == 1 ~ "1.00", T ~ upper_lab),
           mu_rCI = paste("=",mu_r_lab," (",lower_lab,",",upper_lab,")",sep="")) %>% 
    ggplot(aes(x = r)) +
      # geoms
      geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                     linewidth = .1, bins = 50) +
      geom_text_npc(aes(npcx = "left", npcy = "top"), label = expression(italic(r)),
                    size = 2, hjust = -3, vjust = -1.425) +
      geom_text_npc(aes(npcx = "middle", npcy = "top",
                        label = mu_rCI), size = 2, vjust = -1) +
      geom_hline(yintercept = 0) +
      geom_vline(aes(xintercept = mu_r), color = "red2") +
      # scales
      scale_x_continuous(limits = c(-1,1), expand = c(0,0), breaks = seq(-1,1,.5),
                         labels = c("-1","-.5","0",".5", "1")) +
      scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
      # themes
      labs(x = "Reliability Coefficient", y = "Density") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black"),
            axis.text.y = element_text(color = "black"),
            axis.ticks = element_line(color = "black"),
            axis.line.x = element_line(color = "transparent"),
            plot.margin = unit(c(.3, .3, .3, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            strip.text.x = element_text(size = 12, vjust = 1.5),
            strip.text.y = element_blank(),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent"),
            aspect.ratio = 1) +
      facet_rep_grid(.~parameter, scales = "free",
                     labeller = label_parsed) +
      geom_segment(aes(x = lower, xend = upper, y = .025, yend = .025),
                   size = 1, color = "red2", linewidth = .5)
dev.off()
```



## Self-Report Correlations
### ORL
```{r}
selfreport_models = readRDS(here("1_IGT_PP", "Data", "2_Fitted",
                                 "binomial_selfreport_indMu_fits.rds"))
selfreport = readRDS(here("1_IGT_PP", "Data", "1_Preprocessed",
                          "stan_ready_binomial_selfreport.rds"))
```



```{r}
# Check that orl and self-report IDs are in same order between data fed to models
for(scale in names(selfreport)){
  data.frame(orl_IDs = stan_data$subjIDs,
             selfreport_IDs = as.numeric(selfreport[[scale]]$IDs)) %>% 
    mutate(not_equal = ifelse(orl_IDs == selfreport_IDs, 0, 1)) %>% 
    reframe(ID_Check = ifelse(sum(not_equal) == 0, "EQUAL", "NOT EQUAL")) %>% 
    print()
}
```



```{r}
scales = c(# Session 1 only
           "prdep_tot", "masqGDA", "masqAA", "masqGDD",
           # "masqAD", # Removed
           # Both Sessions
           "bastot", "basdrive", "basfunsk", "basrewres",
           "bis", "panas_pa", "panas_na", "shaps_tot")


selfreport_posteriors = list()
sr_posterior_means = list()

for(scale in scales){
  dimensions = c(2,3)
  if(length(dim(selfreport_posteriors[[scale]]$theta)) == 2) dimensions = 2
  
  selfreport_posteriors[[scale]] = extract(selfreport_models[[scale]], par = "theta")
  sr_posterior_means[[scale]] = apply(selfreport_posteriors[[scale]]$theta*selfreport[[scale]]$M, 2, mean)
}

overall_orl_posterior_means = list()

for(parameter in person_parameters){
  overall_orl_posterior_means[[parameter]] = apply(orl_posteriors[[parameter]], 2, mean)
}


session_orl_posterior_means = list()

for(parameter in person_parameters){
  session_orl_posterior_means[[parameter]] = apply(orl_posteriors[[parameter]], c(2,3), mean)
}
```



```{r}
correlations = data.frame()

for(parameter in person_parameters){
  for(scale in scales){
    for(s in 1:ncol(selfreport[[scale]]$score)){
        
      orl = session_orl_posterior_means[[parameter]][,s][selfreport[[scale]]$score[,s] != -999]
      sr = selfreport[[scale]]$score[,s][selfreport[[scale]]$score[,s] != -999]
      
        correlation = boot.cor.bca(x = orl,
                                   y = sr,
                                   null.hyp = NULL,
                                   alternative = c("two.sided", "less", "greater"),
                                   conf.level = 0.95, type = NULL, R = 9999)
        
        correlations = data.frame(parameter = parameter,
                                  scale = scale,
                                  type = "sum-score",
                                  session = s,
                                  r = correlation$Observed,
                                  CI = correlation$Confidence.interval) %>%
          bind_rows(correlations)
    }
  }
}
correlations %>% 
  separate(col = "CI", into = c("lower", "upper"), sep = ",") %>% 
  mutate(lower = as.numeric(str_remove(lower, "\\(")), upper = as.numeric(str_remove(upper, "\\)"))) %>% 
  write.csv(here("1_IGT_PP", "Figs_Tables", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
                 "session_orl_sr_correlations.csv"))

correlations = data.frame()

for(parameter in person_parameters){
  for(scale in scales){
    orl = overall_orl_posterior_means[[parameter]]
    
    temp_sr = selfreport[[scale]]
    temp_sr$score[temp_sr$score==-999] = NA
    sr = apply(temp_sr$score, 1, mean, na.rm = T)

      correlation = boot.cor.bca(x = orl,
                                 y = sr,
                                 null.hyp = NULL,
                                 alternative = c("two.sided", "less", "greater"),
                                 conf.level = 0.95, type = NULL, R = 9999)

      correlations = data.frame(parameter = parameter,
                                scale = scale,
                                type = "sum-score",
                                r = correlation$Observed,
                                CI = correlation$Confidence.interval) %>%
        bind_rows(correlations)
  }
}
```



### Summary Scores
```{r}
# Recode choice data
choices = ifelse(stan_data$choice == 2, 0, ifelse(stan_data$choice == 1, 1, NA))

# Empty matrices
good_proportions = matrix(data = NA, nrow = 49, ncol = 2)
bad_proportions = matrix(data = NA, nrow = 49, ncol = 2)

# Calculate proportions
for(i in 1:49){
  for(s in 1:2){
    good_proportions[i,s] = mean(choices[i,,s][stan_data$card[i,,s] == 3 | stan_data$card[i,,s] == 4], na.rm = T)
    bad_proportions[i,s] = mean(choices[i,,s][stan_data$card[i,,s] == 1 | stan_data$card[i,,s] == 2], na.rm = T)
  }
}

for(scale in scales){
  good_prop = apply(good_proportions, 1, mean, na.rm = T)
  bad_prop = apply(bad_proportions, 1, mean, na.rm = T)
  
  temp_sr = selfreport[[scale]]
  temp_sr$score[temp_sr$score==-999] = NA
  sr = apply(temp_sr$score, 1, mean, na.rm = T)
  
  correlation = boot.cor.bca(x = good_prop,
                             y = sr,
                             null.hyp = NULL,
                             alternative = c("two.sided", "less", "greater"),
                             conf.level = 0.95, type = NULL, R = 9999)
  
  correlations = data.frame(parameter = "good_proportion",
                            scale = scale,
                            type = "sum-score",
                            r = correlation$Observed,
                            CI = correlation$Confidence.interval) %>%
    bind_rows(correlations)
  
  correlation = boot.cor.bca(x = bad_prop,
                             y = sr,
                             null.hyp = NULL,
                             alternative = c("two.sided", "less", "greater"),
                             conf.level = 0.95, type = NULL, R = 9999)
  
  correlations = data.frame(parameter = "bad_proportion",
                            scale = scale,
                            type = "sum-score",
                            r = correlation$Observed,
                            CI = correlation$Confidence.interval) %>%
    bind_rows(correlations)
}


correlations %>% 
  separate(col = "CI", into = c("lower", "upper"), sep = ",") %>% 
  mutate(lower = as.numeric(str_remove(lower, "\\(")), upper = as.numeric(str_remove(upper, "\\)"))) %>% 
write.csv(here("1_IGT_PP", "Figs_Tables", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
               "overall_sr_correlations.csv"))

correlations %>% 
  separate(col = "CI", into = c("lower", "upper"), sep = ",") %>% 
  mutate(lower = as.numeric(str_remove(lower, "\\(")), upper = as.numeric(str_remove(upper, "\\)")),
         sig = case_when(lower < 0 & upper < 0 ~ "*", lower > 0 & upper > 0 ~ "*", T ~ ""),
         estimate = round(r,2),
         estimate_lab = paste(ifelse(sign(estimate)==1," ","-"), stri_pad_right(str_remove(abs(estimate), "^0+"),
                                                                                width = 3, pad = "0"),sep=""),
         lower = round(as.numeric(str_remove(lower, "\\(")),2),
         upper = round(as.numeric(str_remove(upper, "\\)")),2),
         
         lower_lab = paste(ifelse(sign(lower)==1,"","-"), stri_pad_right(str_remove(abs(lower), "^0+"),
                                                                         width = 3, pad = "0"),sep=""),
         
         upper_lab = paste(ifelse(sign(upper)==1,"","-"), stri_pad_right(str_remove(abs(upper), "^0+"),
                                                                         width = 3, pad = "0"),sep=""),
         upper_lab = case_when(upper_lab == "-000" ~ "-.00", T ~ upper_lab),
         estimate_lab = case_when(estimate_lab == "-000" ~ "-.00", T ~ estimate_lab),
         estimate_CI = paste(estimate_lab," [",lower_lab,",",upper_lab,"]",sep="")) %>% 
  select(parameter, scale, lab = estimate_CI, sig) %>% 
  pivot_wider(names_from = "parameter", values_from = c("lab", "sig")) %>% 
  write.csv(here("1_IGT_PP", "Figs_Tables",
                 "ORL_Joint_playfic_playupdate_modifiedK_simplified",
                 "organized_overall_sr_correlations.csv"))
```



## Correlations B/w Arew & Apun
```{r}
overall_pcor = data.frame()
overall_Arew = apply(orl_posteriors$Arew, c(1,2), mean)
overall_Apun = apply(orl_posteriors$Apun, c(1,2), mean)
for(i in 1:iterations){
  overall_pcor = data.frame(r = cor(overall_Arew[i,], overall_Apun[i,])) %>% 
    bind_rows(overall_pcor)
}
session1_pcor = data.frame()
for(i in 1:iterations){
  session1_pcor = data.frame(r = cor(orl_posteriors$Arew[i,,1], orl_posteriors$Apun[i,,1])) %>% 
    bind_rows(session1_pcor)
}
session2_pcor = data.frame()
for(i in 1:iterations){
  session2_pcor = data.frame(r = cor(orl_posteriors$Arew[i,,2], orl_posteriors$Apun[i,,2])) %>% 
    bind_rows(session2_pcor)
}

hist(overall_pcor$r, main = paste0("overall: r = ", round(mean(overall_pcor$r),2)))
abline(v = mean(overall_pcor$r))
hist(session1_pcor$r, main = paste0("overall: r = ", round(mean(session1_pcor$r),2)))
abline(v =mean(session1_pcor$r))
hist(session2_pcor$r, main = paste0("overall: r = ", round(mean(session2_pcor$r),2)))
abline(v =mean(session2_pcor$r))

mean(session1_pcor$r)
HDIofMCMC(session1_pcor$r)
mean(session2_pcor$r)
HDIofMCMC(session2_pcor$r)
```



## Relations to Behavior
### Calculate Choice Proportions
```{r}
choice = ifelse(stan_data$choice == 1, 1, ifelse(stan_data$choice == 2, 0, NA))

card_proportions = array(data = NA, dim = c(49, 4, 2))
good_proportions = matrix(data = NA, nrow = 49, ncol = 2)
play_proportions = matrix(data = NA, nrow = 49, ncol = 2)

for(i in 1:49){
  for(s in 1:2){
    good_proportions[i,s] = mean(choice[i,,s][stan_data$card[i,,s] == 3 | stan_data$card[i,,s] == 4], na.rm = T)
    play_proportions[i,s] = mean(choice[i,,s] == 1, na.rm = T)
    for(c in 1:4){
      card_proportions[i,c,s] = mean(choice[i,,s][stan_data$card[i,,s] == c], na.rm = T)
    }
  }
}
```



### Correlations w/Card Proportions
```{r}
for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
    print(paste(" ", parameter))
    for(c in 1:4){
      card = ifelse(c == 1, "    Net = -750, Win Freq = 15, Lose Freq = 15",
                    ifelse(c == 2, "    Net = -750, Win Freq = 27, Lose Freq = 3",
                           ifelse(c == 3, "    Net = +600, Win Freq = 15, Lose Freq = 6",
                                  "    Net = +750, Win Freq = 27, Lose Freq = 3")))
      print(paste(card, ": r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], card_proportions[,c,s],
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
    }
  }
}
```



### Correlations w/Good Proportions
```{r}
for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
      print(paste("  ", parameter, " vs Proportion Good Cards: r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], good_proportions[,s],
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
  }
}
```



### Correlations w/Play Proportions
```{r}
for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
      print(paste("  ", parameter, " vs Proportion Played: r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], abs(play_proportions[,s]-.5),
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
  }
}
```



### Correlations w/Net Gain
```{r}
net_gains = apply(stan_data$outcome, c(1,3), sum)

for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
      print(paste("  ", parameter, " vs Net Gain: r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], net_gains[,s],
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
  }
}
print("Change in Gain")
for(parameter in person_parameters){
    print(paste("  ", parameter, " vs Delta Net Gain: r = ",
                round(cor(apply(orl_posteriors[[parameter]], 2, mean), (net_gains[,2]-net_gains[,1]),
                          use = "pairwise.complete.obs"), 2),
                sep = ""))
}
```











