---
title: "Estimate MLMs"
output: html_document
date: "2024-05-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lme4)
library(psych)
library("lmerTest")
library(here)
library("jtools")
library("sjPlot")
library(tidyverse)
library(ggplot2)

# Note here() starts at:  /Users/tuo09169/Dropbox/1_Comp_Modelling/1_IGT_PlayPass/IGT_PP_Shared
```



# import long-format data
```{r}

data <- read.csv(here("1_TADS_long", "Data", "3_LongFormat", "TADS_child_long_IGT.csv"))

```


# general spaghetti plot code 
```{r, echo=FALSE}
# Create the plot
spaghetti_plot <- ggplot(data, aes(x = age_centered, y = Arew_qnormed, colour = as.factor(id), group = id)) +
  geom_point() + 
  geom_line() +  # Add lines for each id
  geom_smooth(method = "lm", se = FALSE, color = "black", aes(group = 1)) +  # Add overall fit line
  theme_bw() +  # Apply a black-and-white theme
  theme(legend.position = "none")

print(spaghetti_plot)

```


# define colors for subject-level data
```{r}

cols=rainbow(length(unique(data$id)))

# Reset the plot window
dev.off() 

```



NOTE:  here is the lmer cheatsheet:  https://eshinjolly.com/pymer4/rfx_cheatsheet.html


# random intercepts only Arew_qnormed
```{r}

rand_intcpt_Arew_qnormed <- lmer(Arew_qnormed ~ age_centered + (1 | id), data=data, REML=FALSE)
summ(rand_intcpt_Arew_qnormed)
summary(rand_intcpt_Arew_qnormed)
tab_model(rand_intcpt_Arew_qnormed)


# NOTE:  1 unit change in age = -.04 unit change in Arew_qnormed

```


# random slopes only Arew_qnormed
```{r}

rand_slope_Arew_qnormed <- lmer(Arew_qnormed ~ age_centered + (0 + age_centered | id), data=data, REML=FALSE)
summ(rand_slope_Arew_qnormed)
summary(rand_slope_Arew_qnormed)
tab_model(rand_slope_Arew_qnormed)

```



# random intercepts and slopes (without their correlation) Arew_qnormed
```{r}

rand_intcpt_slope_Arew_qnormed <- lmer(Arew_qnormed ~ age_centered + (0 + age_centered | id), data=data, REML=FALSE)
summ(rand_intcpt_slope_Arew_qnormed)
summary(rand_intcpt_slope_Arew_qnormed)
tab_model(rand_intcpt_slope_Arew_qnormed)

```



#Random intercepts and slopes (without their correlation)
```{r}
rand_intcpt_slope_Arew_qnormed <- lmer(Arew_qnormed ~ age_centered + MatHxDepress + age_centered*MatHxDepress + (1 | id) + (0 + age_centered | id), data=data, REML=FALSE)
summ(rand_intcpt_slope_Arew_qnormed)
summary(rand_intcpt_slope_Arew_qnormed)
tab_model(rand_intcpt_slope_Arew_qnormed)
  
```



#Random intercepts and slopes (without their correlation)
```{r}
rand_intcpt_slope_Apun_qnormed <- lmer(Apun_qnormed ~ age_centered + MatHxDepress + age_centered*MatHxDepress + (1 | id) + (0 + age_centered | id), data=data, REML=FALSE)
summ(rand_intcpt_slope_Apun_qnormed)
summary(rand_intcpt_slope_Apun_qnormed)
tab_model(rand_intcpt_slope_Apun_qnormed)
  
```





