---
title: "Fitting ORL"
output: html_document
date: "2023-03-07"
---



# -------------------------------------------
# Setup
## Load Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rstan)
library(hBayesDM)
library(bayesplot)
library(here)
library(miscTools)
library(cmdstanr)
library(stringi)
library(ggpp)
library(lemon)
source(here("1_TADS_long", "Code", "R", "3_Other", "helpful_functions.R"))
```



## RMD Setup
```{r}
model_name = "ORL"
samples = c("T1_IGT_child", "T2_IGT_child", "T3_IGT_child", "T4_IGT_child", "T5_IGT_child")
# sample = "T2_IGT_child"

focal_parameters = c(
  "mu_Arew", "mu_Apun", "mu_K", "mu_betaF", "mu_betaP", 
  "sigma_Arew", "sigma_Apun", "sigma_K", "sigma_betaF", "sigma_betaP", 
  "Arew", "Apun", "K", "betaF", "betaP"
)


group_parameters <- grep("mu|sigma", focal_parameters, value=TRUE)
person_parameters <- grep("mu|sigma", focal_parameters, value=TRUE, invert=TRUE)
```




# Fit Model
```{r, eval = F}
# Compile model
orl_model = stan_model(here("1_TADS_long", "Code", "Stan",
                            paste0(model_name, ".stan")))

for(sample in samples){

  stan_data = readRDS(here("1_TADS_long", "Data", "1_Preprocessed",
                           paste0(sample, "_stanReady.RDS")))
  
  
  stan_data$ID = stan_data$ID_num # set ID variable to use in stan code

  # Fit model
  orl_fit = sampling(orl_model, 
                     data   = stan_data, 
                     iter   = 5000, 
                     warmup = 1000, 
                     chains = 4, 
                     cores  = 4,
                     seed   = 43210)
  
  
  # Save the fitted model as an rds file
  saveRDS(orl_fit, here("1_TADS_long", "Data", "2_Fitted",
                        paste0(sample, "_", model_name, "_fit.rds")))

}
```



```{r}

samples = c("T1_IGT_child", "T2_IGT_child", "T3_IGT_child", "T4_IGT_child", "T5_IGT_child")

for(sample in samples){
  orl_fit = readRDS(here("1_TADS_long", "Data", "2_Fitted",
                           paste0(sample, "_ORL_fit.rds")))

iterations = orl_fit@sim$chains * (orl_fit@sim$iter - orl_fit@sim$warmup)
print(iterations)
}
```



# Model Diagnostics (_fit.rds) & Posteriors (_posteriors.rds)
```{r}
for(sample in samples){
  orl_fit = readRDS(here("1_TADS_long", "Data", "2_Fitted",
                           paste0(sample, "_ORL_fit.rds")))
  orl_posteriors <- extract(orl_fit)
  saveRDS(orl_posteriors, here("1_TADS_long", "Data", "2_Fitted",
                           paste0(sample, "_ORL_posteriors.rds")))
}
```




# Model Diagnostics (_fit.rds) & Posteriors (_posteriors.rds)
```{r}
for(sample in samples){
  orl_fit = readRDS(here("1_TADS_long", "Data", "2_Fitted",
                        paste0(sample, "_", model_name, "_fit.rds")))
  orl_posteriors <- extract(orl_fit)
  stan_data = readRDS(here("1_TADS_long", "Data", "1_Preprocessed",
                           paste0(sample, "_stanReady.RDS")))
  orl_posteriors[["ID_num"]] <- stan_data[["ID_num"]]
  saveRDS(orl_posteriors, here("1_TADS_long", "Data", "2_Fitted",
                        paste0(sample, "_", model_name, "_posteriors.rds")))
}
    
```




## Rhat
```{r, eval = T}
for(sample in samples){
  orl_fit = readRDS(here("1_TADS_long", "Data", "2_Fitted",
                           paste0(sample, "_ORL_fit.rds")))
  rhats = rhat(orl_fit, pars = focal_parameters) %>%
  data.frame() %>% mutate(parameter = rownames(.))
  saveRDS(rhats, here("1_TADS_long", "Data", "2_Fitted",
                           paste0(sample, "_ORL_rhats.rds")))
}



##check the rhats
for(sample in samples){
rhat_dat <- readRDS(here("1_TADS_long", "Data", "2_Fitted",
                           paste0(sample, "_ORL_rhats.rds")))
print(sample)
print(rhat_dat[,])
}
```



## Traceplots
```{r, eval = T}

for(sample in samples){
  orl_fit = readRDS(here("1_TADS_long", "Data", "2_Fitted",
                           paste0(sample, "_ORL_fit.rds")))
  trace <- traceplot(
    orl_fit,
    pars = group_parameters)
  ggsave((here("1_TADS_long","Figs_Tables", "Traceplots", paste0(sample, "_ORL_traceplot.png"))), trace)
}
  

dev.off()

```



# Parsplots
```{r, eval = T}

for(sample in samples){
  orl_fit = readRDS(here("1_TADS_long", "Data", "2_Fitted",
                           paste0(sample, "_ORL_fit.rds")))
  pars_plot <- plot(orl_fit, pars = group_parameters)
  ggsave((here("1_TADS_long","Figs_Tables", paste0(sample, "_ORL_parsplot.png"))), pars_plot)
}


dev.off()
```






# Make .csv files for ind posterior means at each time point
```{r, eval = T}
for(sample in samples){
   orl_posteriors = readRDS(here("1_TADS_long", "Data", "2_Fitted",
                        paste0(sample, "_", model_name, "_posteriors.rds")))
   df <- data.frame(ID = orl_posteriors$ID_num,
          Arew = colMeans(orl_posteriors$Arew[,,1]), # posterior means for Arew
          Apun = colMeans(orl_posteriors$Apun[,,1]),
          betaF = colMeans(orl_posteriors$betaF[,,1]),
          betaP = colMeans(orl_posteriors$betaP[,,1]),
          K = colMeans(orl_posteriors$K[,,1]))
   var_name <- paste0(sample, "_ind_posterior_means")   
   assign(var_name, df)
   #save the posterior_means dataframe as a .csv
   write.csv(df,(here("1_TADS_long", "Data", "2_Fitted",
                        paste0(sample, "_", model_name, "_ind_posterior_means.csv"))))
}
      
```






## I HAVEN'T USED ANY CODE BELOW HERE
# THIS IS NOT FINISHED
## Posterior Distributions
```{r, eval = F}
tiff(here("Figs_Tables",
          model_name,
          paste(sample, model_name, "posterior_distributions.tiff", sep = "_")),
     width = length(group_parameters), height = length(group_parameters),
     units = "cm", res = 300)
  par(mfrow = c(5, 5))
  # Mus & Sigmas
  for(s in 1:stan_data$S){
    for(i in grep("mu|sigma", group_parameters, value = T)){
      plot(density(orl_posteriors[[i]][,s]), main = paste(i, s))
      abline(v = mean(orl_posteriors[[i]][,s]))
    }
  }
dev.off()
```



# -------------------------------------------
# Results
## PPC Plot
```{r, eval = F}
choice_proportions = calculate_proportions(orl_posteriors, stan_data,
                                           data_type = "data.frame"
                                           # data_type = "list_of_matrices"
                                           )
saveRDS(choice_proportions,
        here("Data", "2_Fitted",
             model_name,
             paste(sample, model_name, "ppcs.rds", sep = "_")))
```



```{r, eval = F}
choice_proportions = readRDS(here("Data", "2_Fitted",
                                  model_name,
                                  paste(sample, model_name, "ppcs.rds", sep = "_")))
```



```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "ORL_playfic_playupdate_modifiedK_simplified",
          "ORL_playfic_playupdate_modifiedK_simplified_PPC.tiff"),
     width = 15, height = 8, units = "cm", res = 300)

  # simplify data
  choice_proportions %>% 
    group_by(trial, deck, session) %>% 
    summarise(observed = mean(observed), mu = mean(mu),
              lower50 = mean(lower50), upper50 = mean(upper50),
              lower95 = mean(lower95), upper95 = mean(upper95)) %>%
    # plotting
    ggplot(aes(x = trial,
               group = trial)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95),
                   linewidth = .35, color = "goldenrod3", alpha = .35) +
    geom_linerange(aes(ymin = lower50, ymax = upper50),
                   linewidth = .35, color = "goldenrod3") +
    geom_point(aes(y = mu), shape = 21,
               color = "goldenrod3", fill = "white",
               size = .75) +
    geom_point(aes(y = observed), size = .75) +
    scale_y_continuous(limits = c(0,1), expand = c(0,0),
                       breaks = seq(0,1,.25)) +
    labs(x = "Trial", y = "Proportion Play") +
    theme_classic() +
    theme(axis.text = element_text(color = "black"),
          strip.background = element_blank(),
          panel.spacing.x = unit(-.5,"lines"),
          panel.spacing.y = unit(0,"lines")) +
    facet_rep_grid(session~deck,
                   labeller = labeller(session = c("1" = "Session 1", "2" = "Session 2"),
                                       deck = c("A" = "Deck A", "B" = "Deck B",
                                                "C" = "Deck C", "D" = "Deck D")))
dev.off()
```


## THIS CODE IS FOR THE JOINT MODEL
## Reliability
```{r, eval = F}
tiff(here("1_IGT_PP", "Figs_Tables", "ORL_playfic_playupdate_modifiedK_simplified",
          "reliability_coefficients.tiff"),
     width = 15, height = 6.25, units = "cm", res = 300)
  bind_rows(data.frame(parameter = "Arew", r = orl_posteriors$R_Arew[,2,1]),
            data.frame(parameter = "Apun", r = orl_posteriors$R_Apun[,2,1]),
            data.frame(parameter = "betaF", r = orl_posteriors$R_betaF[,2,1]),
            data.frame(parameter = "betaP", r = orl_posteriors$R_betaP[,2,1]),
            data.frame(parameter = "K", r = orl_posteriors$R_K[,2,1])) %>% 
    mutate(parameter = factor(parameter,
                              levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                              labels = c(expression(paste(italic(A),"+",sep="")),
                                         expression(paste(italic(A),"-",sep="")),
                                         expression(paste("\u03B2",italic(f),sep="")),
                                         expression(paste("\u03B2",italic(p),sep="")),
                                         expression(italic(K))))) %>% 
    group_by(parameter) %>% 
    mutate(mu_r = mean(r), lower = HDIofMCMC(r)[1], upper = HDIofMCMC(r)[2],
           mu_r_lab = paste(ifelse(sign(round(mu_r,2))==1," ","-"),
                            stri_pad_right(str_remove(abs(round(mu_r,2)), "^0+"),
                                           width = 3, pad = "0"),sep=""), 
           lower = as.numeric(str_remove(lower, "\\(")),
           upper = as.numeric(str_remove(upper, "\\(")),
           
           lower_lab = paste(ifelse(sign(round(lower,2))==1,"","-"),
                             stri_pad_right(str_remove(abs(round(lower,2)), "^0+"),
                                            width = 3, pad = "0"),sep=""), 
           upper_lab = paste(ifelse(sign(round(upper,2))==1,"","-"),
                             stri_pad_right(str_remove(abs(round(upper,2)), "^0+"),
                                            width = 3, pad = "0"),sep=""),
           upper_lab = case_when(round(upper,2) == 1 ~ "1.00", T ~ upper_lab),
           mu_rCI = paste("=",mu_r_lab," (",lower_lab,",",upper_lab,")",sep="")) %>% 
    ggplot(aes(x = r)) +
      # geoms
      geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                     linewidth = .1, bins = 50) +
      geom_text_npc(aes(npcx = "left", npcy = "top"), label = expression(italic(r)),
                    size = 2, hjust = -3, vjust = -1.425) +
      geom_text_npc(aes(npcx = "middle", npcy = "top",
                        label = mu_rCI), size = 2, vjust = -1) +
      geom_hline(yintercept = 0) +
      geom_vline(aes(xintercept = mu_r), color = "red2") +
      # scales
      scale_x_continuous(limits = c(-1,1), expand = c(0,0), breaks = seq(-1,1,.5),
                         labels = c("-1","-.5","0",".5", "1")) +
      scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
      # themes
      labs(x = "Reliability Coefficient", y = "Density") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black"),
            axis.text.y = element_text(color = "black"),
            axis.ticks = element_line(color = "black"),
            axis.line.x = element_line(color = "transparent"),
            plot.margin = unit(c(.3, .3, .3, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            strip.text.x = element_text(size = 12, vjust = 1.5),
            strip.text.y = element_blank(),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent"),
            aspect.ratio = 1) +
      facet_rep_grid(.~parameter, scales = "free",
                     labeller = label_parsed) +
      geom_segment(aes(x = lower, xend = upper, y = .025, yend = .025),
                   size = 1, color = "red2", linewidth = .5)
dev.off()
```











