---
title: "PreprocessData_for_MLM"
output: html_document
date: "2024-05-08"
---



# load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("haven")
library(haven)
library(dplyr)
library(tidyverse) 
#install.packages("here")
library(here)

# Note:  here() starts at /Users/tuo09169/Dropbox/1_Comp_Modelling/1_IGT_PlayPass/IGT_PP_Shared
```



# import data and add it to lists for each time point
```{r}
demodat <- read_sav("/Users/tuo09169/Dropbox/1_Comp_Modelling/1_IGT_PlayPass/IGT_PP_Shared/1_TADS_long/Data/1_Preprocessed/FINALIZED_Demoinfo_7.1.22_KD.sav")


samples = c("T1", "T2", "T3", "T4", "T5")
n_samp <- length(samples)
labels = c("T1_bias_dat", "T2_bias_dat", "T3_bias_dat", "T4_bias_dat", "T5_bias_dat")
  IGT_dat_list <- lapply(labels, function(label) data.frame())
  names(IGT_dat_list) <- labels
datafile_name = "_IGT_child_ORL_woK_ind_posterior_means"


# pull each timepoint's posterior means (from the Bias (w/o K) model) into IGT_dat_list 
for (i in 1:n_samp) {
  cur_dat <- read.csv(here("1_TADS_long", "Data", "2_Fitted",
                        paste0(samples[i], datafile_name, ".csv")))
  colnames(cur_dat)[1] <- "id"
  

  # add a variable called time 
  cur_dat["time"] <- samples[i]
  
  
  # add a variable called T where time is (t - 1)
  cur_dat["T"] <- (i - 1)
  
  
  
  # read in age data for the given timepoint
  age <- demodat[c("id", (paste0(samples[i], "_IGT_Age_Child")))]
  colnames(age)[2] <- "age"
  
  # the age data had a few duplicate rows. In the loop below, I am looking for duplicate id numbers,     
  # and checking whether the age value is the same for both. If age is the same, then delete duplicate row; 
  # if age is not the same print the rows (no rows were printed)
      # Find duplicated 'id' values
      dup_ids <- age$id[duplicated(age$id)]

      # Loop through duplicated ids
      for (id in dup_ids) {
        # Subset the dataframe for the current id
        subset_df <- age[age$id == id, ]
        
        # Check if all 'age' values are the same
        if (length(unique(subset_df$age)) == 1) {
          # If age values are the same, delete one of the rows
          age <- age[!duplicated(age), ]
          } else {
            # If age values are different, print the rows
            print(subset_df)
          }
        }
  
  # merge the age data into cur_dat.  left_join() function ensures that all rows from cur_dat are retained,   # and matching rows from demodat are added based on the "id" variable.
  cur_dat <- left_join(cur_dat, age %>% select(id, age), by = "id")
  
    # make a dataframe of baseline ages
    if (i == 1) {
      base_age <- as.data.frame(cbind(cur_dat$id, cur_dat$age))
      names(base_age) <- c("id", "baseline_age")
    }
  
  
  cur_dat <- left_join(cur_dat, base_age %>% select(id, baseline_age), by = "id")
  

  # NOTE: the n's for each timepoint list are the same before & after I merge in the age data, so removing    the duplicate id row in the age dataframes worked as intended
  
  
  # import sex (character values M & F)
  # NOTE:  DO NOT use variable Sex_T1Child from     */Users/tuo09169/Dropbox/1_Comp_Modelling/1_IGT_PlayPass/IGT_PP_Shared/1_TADS_long/Data/1_Preprocessed/FINALIZED_Demoinfo_7.1.22_KD.sav*
  
  # The issue is explained more fully here https://osf.io/zdmj8/wiki/Preprocessing%20Play%20or%20Pass%20Data/
  sex <- read_csv("/Users/tuo09169/Dropbox/1_Comp_Modelling/1_IGT_PlayPass/IGT_PP_Shared/1_TADS_long/Data/1_Preprocessed/TADS_Child_Sex (use this)/TADS Participant Sex Check - 10.10.22.csv")
  
  names(sex)[2] <- "child_sex"
  
  # recode sex 1 = female; 0 = male
  sex <- mutate(sex, child_sex = recode(child_sex, 'M'= 0, 'F' = 1))

  
  # merge the sex data into cur_dat.  left_join() function ensures that all rows from cur_dat are retained,   
  # and matching rows from sex are added based on the "id" variable.
  cur_dat <- left_join(cur_dat, sex %>% select(id, child_sex), by = "id")

  
  # read in mat hx of depression data
  matdat <- read_sav("/Users/tuo09169/Dropbox/1._Olino_Lab/TADS_behav_data/2_T1_Mom_Data/MomSCIDT1_diagnosesandsymptoms.sav")
  
  # check how many mom's report any lifetime prevalence of alcohol use disorder or substance use disorder
  sum(matdat$lalc)
  sum(matdat$lsub)
  
  mat_hx <- as.data.frame(cbind(matdat$ID, matdat$deptype_l, matdat$lalc, matdat$lsub, matdat$lpot))
  names(mat_hx) <- c("id", "MatHxDepress", "MatHxAlc", "MatHxSub", "MatHxPot") 
  length(mat_hx)
  mat_hx$MatHxAlc_or_Sub <- ifelse(mat_hx$MatHxAlc == 1 | mat_hx$MatHxSub == 1, 1, 0)
  mat_hx$MatHxAlc_Sub_or_Pot <- ifelse(mat_hx$MatHxAlc == 1 | mat_hx$MatHxSub == 1 | mat_hx$MatHxPot == 1, 1, 0)
  
  # recode MatHxDepress to a binary variable
  depress <- which(mat_hx$MatHxDepress>=1)
  length(depress)
  mat_hx$MatHxDepress[depress] <- 1
  

  # merge the sex data into cur_dat.  left_join() function ensures that all rows from cur_dat are       retained, and matching rows from mat_hx are added based on the "id" variable.
  cur_dat <- left_join(cur_dat, mat_hx %>% select(id, MatHxDepress, MatHxAlc, MatHxSub, MatHxPot, MatHxAlc_or_Sub, MatHxAlc_Sub_or_Pot), by = "id")
  
  
  # center age by subtracting the avg baseline age from age at each timepoint
  cur_dat$age_centered <- cur_dat$age - 9.9
  

  # Initialize an empty dataframe with the dimensions of cur_dat
  IGT_dat_list[[i]] <- as.data.frame(matrix(NA, nrow = nrow(cur_dat), ncol = ncol(cur_dat)))
  # Assign the data from cur_dat to IGT_dat_list[i]
  IGT_dat_list[[i]] <- cur_dat
}

```



# get avg baseline age 
# This code gave me avg age at baseline (9.9) 
# but I used this value in the loop above to center age by avg baseline age
```{r}
baseline_age <- as.data.frame(IGT_dat_list[["T1_bias_dat"]][["age"]])
avg_T1_age <- mean(baseline_age[1,])

```

# visually check baseline_age variable
```{r}
IGT_dat_list[["T1_bias_dat"]][["id"]]
IGT_dat_list[["T1_bias_dat"]][["baseline_age"]]
IGT_dat_list[["T2_bias_dat"]][["baseline_age"]]
IGT_dat_list[["T2_bias_dat"]][["id"]]
```



# pull all the lists into long format data & save as .csv
```{r}
# Create a dataframe from the first list
TADS_child_long_IGT <- as.data.frame(IGT_dat_list[[1]])

# Loop through the remaining lists and bind them row-wise
for (i in 2:length(IGT_dat_list)) {
  TADS_child_long_IGT <- bind_rows(TADS_child_long_IGT, as.data.frame(IGT_dat_list[[i]]))
}



### save the long format data as a .csv
path_out = here("1_TADS_long", "Data", "3_LongFormat")
filename <- paste0(path_out, "/", "TADS_child_long_IGT.csv")

# save output
write.csv(TADS_child_long_IGT,filename) 

```










# Some code Tom gave me...dosen't play well with my code above
```{r}
library("plyr")

IGT_dat_list_df <- plyr::rbind.fill(IGT_dat_list)


child_IGT_age_long <- child_IGT_age %>% pivot_longer(cols = T1_IGT_Age_Child:T5_IGT_Age_Child,
                                           names_to = c("time", "drop"),
                                           names_sep = c(2, 14))


full_df <- merge(IGT_dat_list_df, child_IGT_age_long, by = c("id", "time"), all.x = T)



```

  



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
