---
title: "IGT Preprocessing"
output: html_document
author: "Jeremy Haynes"
---



# --------------------------------------
# Setup
## Load Packages
```{r}
library(tidyverse)
library(rprime)
library(car)
library(dplyr)
library(here)
```



## Load Data
```{r}
T1_IGT_child = readRDS(here("1_TADS_long", "Data", "0_Raw", "T1_IGT_child.RDS"))
T2_IGT_child = readRDS(here("1_TADS_long", "Data", "0_Raw", "T2_IGT_child.RDS"))
T3_IGT_child = readRDS(here("1_TADS_long", "Data", "0_Raw", "T3_IGT_child.RDS"))
T4_IGT_child = readRDS(here("1_TADS_long", "Data", "0_Raw", "T4_IGT_child.RDS"))
T5_IGT_child = readRDS(here("1_TADS_long", "Data", "0_Raw", "T5_IGT_child.RDS"))

```


## Check number of trials
## For any subject <120 trials, this will print (1) the sub id and (2) the number of trials 
```{r}

#Enter the name of the data you want to check below
curr_dat <- T5_IGT_child

subj_ids <- unique(curr_dat$id)
n_subj <- length(t(unique(curr_dat["id"])))
for (i in 1:n_subj) {
  # Subset out current subject
   tmp <- subset(curr_dat, id==subj_ids[i])
   x <- length(tmp[,1])
   if (x != 120) {
     print(tmp[1,"id"])
     print(length(tmp[,"trial"]))
   }
}

#  Can also visually check the subj_ids to make sure they are TADS ids 
subj_ids
```

### From running the above code for T1_IGT_child & T2_IGT_child:

### T1_IGT_child, sub 5083 only had 55 trials & 5119 only had 68 trials
### also, there is a subject 9995, which is not a TADS subject number

### T2_IGT_child, sub 5040 had 50 trials & 5083 had 75 trials

### T3_IGT_child, sub 5040 had 40 trials

### Remove these subjects from the respective datasets

```{r}
T1_IGT_child <- subset(T1_IGT_child, id!= 5083 & id!= 5119 & id!= 9995)
T2_IGT_child <- subset(T2_IGT_child, id!= 5040 & id!= 5083)
T3_IGT_child <- subset(T3_IGT_child, id!= 5040)

```


# --------------------------------------
# Make Stan Data
## Function
```{r}
make_stan = function(data){
  # # create variable to denote separate people for a given ID x participant combo & then another
  # #   new variable that gives consecutive numbers for those combos
  # data = dplyr::mutate(dplyr::group_by(tidyr::unite(data, col = "id_part", c(id, participant), remove = F),
  #                                      id_part),
  #                      id_part_order = dplyr::cur_group_id())
  # # create ID variable that gives consecutive numbers for IDs (note that ID references both child & parent)
  # data = dplyr::mutate(dplyr::group_by(data, id), id_order = dplyr::cur_group_id())
  # # create ID variable that assigns child = 1, mom = 2, & dad = 3
  # data = dplyr::mutate(dplyr::group_by(data, participant),
  #                      part_order = match(participant, c("child", "mom", "dad")[1:3]))
  
  ##################################################################
  # NOTE: id_part_order != id_order + part_order
  ##################################################################
  
  # setup stan variables
  ID = unique(data$id)                 # vector of unique ID 
  N = length(ID)                       # number of unique IDs
  sessions = unique(data$time)         # vector of unique sessions
  S = length(sessions)                 # number of unique sessions
  Tr = max(data$trial)                 # max number of trials across participants
  

  ID_num = rep(-1, N)                           # ID
  #participant = rep(-1, N)                     # child (1), mom (2), or dad (3)?
  Tsubj = array(data = 0, dim = c(N,S))         # number of trials by participant
  card = array(data = -1, dim = c(N,Tr,S))      # cards
  choice = array(data = -1, dim = c(N,Tr,S))    # choices made by participant
  outcome = array(data = -999, dim = c(N,Tr,S)) # outcome of choice
  sign = array(data = -999, dim = c(N,Tr,S))    # sign of choice outcome
  
  for(i in 1:N){
    cur_id = dplyr::filter(data, id == ID[i])
    #ID_num[i] = mean(cur_id$id)
    ID_num[i] <- cur_id$id[1]
    #participant[i] = mean(cur_id_part$part_order)
    for(s in 1:S){
      cur_session = dplyr::filter(cur_id, time == sessions[s])
      if(nrow(cur_session) > 0){
        Tsubj[i,s] = max(cur_session$trial)
        for(t in 1:Tsubj[i,s]){
          cur_trial = dplyr::filter(cur_session, trial == t)
          card[i,t,s] = match(stringr::str_remove(cur_trial$AB_card, "AB_"), LETTERS[1:4])
          choice[i,t,s] = ifelse(cur_trial$card_play == 0, 2, cur_trial$card_play)
          outcome[i,t,s] = ifelse(is.na(cur_trial$outcome), 0, cur_trial$outcome / 100)
          sign[i,t,s] = sign(outcome[i,t,s])
        }
      }
    }
  }
  
  stan = list(ID_num = ID_num,
              #as.numeric(gsub("T", "", sessions)),
              #participant = participant,
              N = N,
              S = S,
              T = Tr,
              card = card,
              Tsubj = Tsubj,
              choice = choice,
              outcome = outcome,
              sign = sign)
}
```


## Make individual stan-ready data for each timepoint of child data
```{r}

dat_list <- list(T1_IGT_child, T2_IGT_child, T3_IGT_child, T4_IGT_child, T5_IGT_child)
dat_names <- c("T1_IGT_child", "T2_IGT_child", "T3_IGT_child", "T4_IGT_child", "T5_IGT_child")


for (i in 1:5) {
  data <- dat_list[[i]]
  stanReady <- paste(dat_names[i], "_stanReady", sep = '') 
  stanReady <- make_stan(data)
  saveRDS(stanReady, here("1_TADS_long", "Data", "1_Preprocessed", (paste(dat_names[i], "_stanReady.RDS", sep = ''))))
}

```




## Make joint stan-ready data for all timepoints of child data
```{r}
child_stan <- make_stan(bind_rows(T1_IGT_child,T2_IGT_child,T3_IGT_child,T4_IGT_child,T5_IGT_child))
saveRDS(child_stan, here("1_TADS_long", "Data", "1_Preprocessed", "child_IGT_5_timepoints.RDS"))


#read in 5 timepoint data
#child_dat <- readRDS(here("1_TADS_long", "Data", "1_Preprocessed", "child_IGT_5_timepoints.RDS"))

```



## NOTE:  I haven't used anything below here
## Make Parent Data
```{r}
parent_stan = make_stan(bind_rows(T1_IGT_mom, T1_IGT_dad,
                                  T2_IGT_mom, T2_IGT_dad#,
                                  # T3_IGT_mom, T3_IGT_dad,
                                  # T4_IGT_mom, T4_IGT_dad,
                                  # T5_IGT_mom, T5_IGT_dad
                                  ))
saveRDS(parent_stan, here("Data", "1_Stan", "parent_IGT.RDS"))
```



```{r, eval = F}
for(i in names(parent_stan)){
  View(data.frame(parent_stan[[i]]), title = i)
}
```



## Make Combined Data
```{r}
full_stan = make_stan(full)
saveRDS(full_stan, here("Data", "1_Stan", "full_IGT.RDS"))
```



# --------------------------------------
```{r}

```






























