---
title: "Evaluating Group-Based Covariate Model"
output: html_document
date: "2023-03-07"
---



# -------------------------------------------
# Setup
## Load Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rstan)
library(hBayesDM)
library(bayesplot)
library(here)
library(miscTools)
library(cmdstanr)
library(stringi)
library(ggpp)
library(lemon)
library(grid)
library(zoo)
```



## RMD Setup
```{r}
groups = c("SU", "Dep", "Anx")
model_name = "Covariate_Joint_ORL_Bias"
sample = "T12_parent_SU_Dep_Anx"

stan_data = readRDS(here("1_TADS_Parents_PP", "Data", "1_Stan",
                         paste("design", sample, "IGT.RDS", sep = "_")))

focal_parameters = c(
  "mu_Arew", "mu_Apun", "mu_betaF", "mu_betaB", 
  "sigma_Arew", "sigma_Apun", "sigma_betaF", "sigma_betaB", 
  "Arew", "Apun", "betaF", "betaB", 
  "beta_Arew", "beta_Apun", "beta_betaF", "beta_betaB", 
  "R_Arew", "R_Apun", "R_betaF", "R_betaB"
)


group_parameters <- grep("mu|sigma|R|beta_", focal_parameters, value=TRUE)
person_parameters <- grep("mu|sigma|R|beta_", focal_parameters, value=TRUE, invert=TRUE)
```



## Load Data
```{r}
orl_fit = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                       model_name,
                       paste(sample, model_name, "short_fit.rds", sep = "_")))


orl_posteriors = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                              model_name,
                              paste(sample, model_name, "short_posteriors.rds", sep = "_")))


orl_rhats = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                         model_name,
                         paste(sample, model_name, "short_rhats.rds", sep = "_")))
```



# -------------------------------------------
# Model Diagnostics
## Traceplots
```{r, eval = F}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name, 
          # sample,
          paste0(sample, "_short"),
          "group_traceplots.tiff"),
     width = 35, height = 25, units = "cm", res = 300)
  traceplot(
    orl_fit,
    pars = group_parameters
)
dev.off()


for(i in person_parameters){
  tiff(here("1_TADS_Parents_PP", "Figs_Tables",
            model_name,
            # sample,
            paste0(sample, "_short"),
            paste(i, "traceplots.tiff")),
       width = 100, height = 100, units = "cm", res = 300)
    traceplot(orl_fit,
              pars = i
              ) %>% print()
    dev.off()
}
```



## PPC Plots
### Prep Data
```{r, eval = T}
source(here("1_TADS_Parents_PP", "Code", "R", "3_other", "helpful_functions.R"))

PPC_data = data.frame()

for(x in c(2:(length(groups)+1)))
  for(g in c(0,1)){
    PPC_data = calculate_PPCs(cards = stan_data$card[stan_data$X[,x,]==g,,],
                              trials = stan_data$Tsubj[stan_data$X[,x,]==g],
                              predicted_choices = orl_posteriors$choice_pred[,stan_data$X[,x,]==g,,], 
                              observed_choices = stan_data$choice[stan_data$X[,x,]==g,,],
                              data_type = "data.frame") %>%
      mutate(comparison = paste0("Con~", groups[x-1]),
             group = case_when(g == 0 ~ "Con", T ~ groups[x-1])) %>% 
      bind_rows(PPC_data)
  }
PPC_data = PPC_data %>% 
  mutate(group = factor(group, levels = c("Con", groups[1], groups[2],
                                          groups[3]), ordered = T))

saveRDS(PPC_data,
        here("1_TADS_Parents_PP", "Data", "2_Fitted",
             model_name,
             paste(sample, model_name, "PPC_data.rds", sep = "_")))
```



```{r}
PPC_data = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                        model_name,
                        paste(sample, model_name, "PPC_data.rds", sep = "_")))
```



### Between-Group PPC Plot
```{r, eval = T}
for(x in groups){
  tiff(here("1_TADS_Parents_PP", "Figs_Tables",
            model_name, sample,
            paste(x, sample, "Between-Group PPC.tiff")),
       width = 7, height = 7, units = "cm", res = 300)
  
    # simplify data
    PPC_plot = PPC_data %>% 
      filter(str_detect(comparison, x)) %>% 
      
      # bins
      group_by(trial, deck, group) %>% 
      # summarise(observed = mean(observed), mu = mean(mu),
      #           lower50 = mean(lower50), upper50 = mean(upper50),
      #           lower95 = mean(lower95), upper95 = mean(upper95)) %>%
      summarise(observed = median(observed), mu = median(predicted),
                lower50 = HDIofMCMC(predicted, credMass = .5)[1],
                upper50 = HDIofMCMC(predicted, credMass = .5)[2],
                lower95 = HDIofMCMC(predicted)[1],
                upper95 = HDIofMCMC(predicted)[2]) %>%
      mutate(block = ceiling(trial / 10)) %>% 
      ungroup() %>% group_by(deck, group) %>% 
      mutate(observed = rollapply(observed, width = 5, FUN = mean,
                                  na.rm = TRUE, fill = NA, partial = T),
             mu = rollapply(mu, width = 5, FUN = mean,
                            na.rm = TRUE, fill = NA, partial = T),
             lower50 = rollapply(lower50, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper50 = rollapply(upper50, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             lower95 = rollapply(lower95, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper95 = rollapply(upper95, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T)) %>% 
      ggplot(aes(x = trial, color = group, group = block)) +
      
      # calculate summary statistics by trials
      # summarise(observed = mean(observed), mu = mean(mu),
      #           lower50 = mean(lower50), upper50 = mean(upper50),
      #           lower95 = mean(lower95), upper95 = mean(upper95)) %>%
      # ggplot(aes(x = trial, color = group)) +
      
      # geoms
      geom_linerange(aes(ymin = lower95, ymax = upper95),
                     linewidth = .35, alpha = .35) +
      geom_linerange(aes(ymin = lower50, ymax = upper50),
                     linewidth = .35) +
      geom_point(aes(y = mu),
                 shape = 16, size = .75) +
      geom_line(aes(y = mu)) +
      geom_point(aes(y = observed),
                 shape = 21, size = .75, fill = "white") +
      geom_vline(xintercept = c(10.5, 20.5), linewidth = .25, linetype = "dashed") +
      # scales
      scale_y_continuous(limits = c(.25,1),
                         breaks = seq(0,1,.25)) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.background = element_rect(fill = "white", colour = "transparent"),
            legend.position = c(.84,.59), 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.key.size = unit(.25, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      guides(color = guide_legend(override.aes = list(size = 1.25))) +
      facet_rep_wrap(deck~.)
      
    print(PPC_plot)
  dev.off()
}
```



### Within-Group PPC Plot
```{r, eval = T}
for(x in groups){
  tiff(here("1_TADS_Parents_PP", "Figs_Tables",
            model_name, sample,
            paste(x, sample, "Within-Group PPC.tiff")),
       width = 5, height = 7, units = "cm", res = 300)
  
    # simplify data
    PPC_plot = PPC_data %>% 
      filter(str_detect(comparison, x)) %>% 
      
      # bins
      group_by(trial, deck, group) %>% 
      summarise(observed = mean(observed), mu = mean(mu),
                lower50 = mean(lower50), upper50 = mean(upper50),
                lower95 = mean(lower95), upper95 = mean(upper95)) %>%
      mutate(block = ceiling(trial / 10)) %>% 
      ungroup() %>% group_by(deck, group) %>% 
      mutate(observed = rollapply(observed, width = 5, FUN = mean,
                                  na.rm = TRUE, fill = NA, partial = T),
             mu = rollapply(mu, width = 5, FUN = mean,
                            na.rm = TRUE, fill = NA, partial = T),
             lower50 = rollapply(lower50, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper50 = rollapply(upper50, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             lower95 = rollapply(lower95, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper95 = rollapply(upper95, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T)) %>% 
      ggplot(aes(x = trial, color = deck)) +
      
      # calculate summary statistics by trials
      # summarise(observed = mean(observed), mu = mean(mu),
      #           lower50 = mean(lower50), upper50 = mean(upper50),
      #           lower95 = mean(lower95), upper95 = mean(upper95)) %>%
      # ggplot(aes(x = trial, color = deck)) +
      
      # geoms
      geom_ribbon(aes(ymin = lower95, ymax = upper95, fill = deck), color = "transparent",
                  alpha = .25) +
      geom_ribbon(aes(ymin = lower50, ymax = upper50, fill = deck), color = "transparent",
                  alpha = .5) +
      geom_line(aes(y = mu), linewidth = .25) +
      geom_point(aes(y = observed, fill = deck), color = "black",
                 shape = 21, size = .75) +
      geom_vline(xintercept = c(10.5, 20.5), linewidth = .25, linetype = "dashed") +
      # scales
      scale_y_continuous(limits = c(0,1),
                         breaks = seq(0,1,.25)) +
      scale_color_manual(values = c("#999999", "#E69F00", "#56B4E9", "#009E73")) +
      scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9", "#009E73")) +
      # theme
      labs(x = "Trial", y = "Proportion Play",
           color = expression(underline("Deck")), fill = expression(underline("Deck"))) +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.title = element_text(vjust = 4.4, hjust = .5, size = 8),
            legend.background = element_rect(fill = "white", colour = "black"),
            legend.position = c(.19,.625), 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            legend.margin = margin(t = .25, b = .01, r = .01, unit = 'cm'),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.key.size = unit(.25, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      guides(color = guide_legend(override.aes = list(size = 1.25), nrow = 2)) +
      facet_rep_grid(group~.)
      
    print(PPC_plot)
  dev.off()
}
```



### Between-/Within-Group PPC Plot
```{r, eval = T}
for(x in groups){
  tiff(here("1_TADS_Parents_PP", "Figs_Tables",
            model_name, sample,
            paste(x, sample, "Between-Within-Group PPC.tiff")),
       width = 15, height = 7, units = "cm", res = 300)
  
    # simplify data
    PPC_plot = PPC_data %>% 
      filter(str_detect(comparison, x)) %>% 
      
      # bins
      group_by(trial, deck, group) %>% 
      summarise(observed = mean(observed), mu = mean(mu),
                lower50 = mean(lower50), upper50 = mean(upper50),
                lower95 = mean(lower95), upper95 = mean(upper95)) %>%
      mutate(block = ceiling(trial / 10)) %>% 
      ungroup() %>% group_by(deck, group) %>% 
      mutate(observed = rollapply(observed, width = 5, FUN = mean,
                                  na.rm = TRUE, fill = NA, partial = T),
             mu = rollapply(mu, width = 5, FUN = mean,
                            na.rm = TRUE, fill = NA, partial = T),
             lower50 = rollapply(lower50, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper50 = rollapply(upper50, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             lower95 = rollapply(lower95, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper95 = rollapply(upper95, width = 5, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T)) %>% 
      ggplot(aes(x = trial, group = trial)) +
      
      # calculate summary statistics by trials
      # summarise(observed = mean(observed), mu = mean(mu),
      #           lower50 = mean(lower50), upper50 = mean(upper50),
      #           lower95 = mean(lower95), upper95 = mean(upper95)) %>%
      # ggplot(aes(x = trial,
      #            group = trial)) +
      
      # geoms
      geom_linerange(aes(ymin = lower95, ymax = upper95),
                     linewidth = .35, color = "goldenrod3", alpha = .35) +
      geom_linerange(aes(ymin = lower50, ymax = upper50),
                     linewidth = .35, color = "goldenrod3") +
      geom_point(aes(y = mu, color = "Predicted", fill = "Predicted"),
                 shape = 21, size = .75) +
      geom_point(aes(y = observed, color = "Observed", fill = "Observed"),
                 shape = 21, size = .75) +
      geom_vline(xintercept = c(10.5, 20.5), linewidth = .25, linetype = "dashed") +
      # scales
      scale_y_continuous(limits = c(0,1),
                         breaks = seq(0,1,.25)) +
      scale_color_manual(name = "hello", values = c("Observed" = "black", "Predicted" = "goldenrod3")) +
      scale_fill_manual(name = "hello", values = c("Observed" = "black", "Predicted" = "white")) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.title = element_blank(),
            legend.background = element_rect(fill = "white", colour = "transparent"),
            legend.position = c(.84,.59), 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.key.size = unit(.25, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      guides(color = guide_legend(override.aes = list(size = 1.25))) +
      facet_rep_grid(group~deck,
                     labeller = labeller(deck = c("A" = "Deck A", "B" = "Deck B",
                                                  "C" = "Deck C", "D" = "Deck D")))
      
    print(PPC_plot)
  dev.off()
}
```



# -------------------------------------------
# Mu Posterior Distributions
## Prep Data
```{r, eval = T}
mu_parameters = bind_rows(data.frame(parameter = "Arew", group = orl_posteriors$mu_Arew),
                          data.frame(parameter = "Apun", group = orl_posteriors$mu_Apun),
                          data.frame(parameter = "betaF", group = orl_posteriors$mu_betaF),
                          data.frame(parameter = "betaP", group = orl_posteriors$mu_betaP)) %>% 
  select(group.Con = group.1.1, 
         group.SU = group.1.2, 
         group.Dep = group.1.3, 
         group.Anx = group.1.4, 
         everything()) %>% 
  mutate(group.Con.SU = group.SU - group.Con,
         group.Con.Dep = group.Dep - group.Con,
         group.Con.Anx = group.Anx - group.Con) %>% 
  pivot_longer(starts_with("group"),
               names_to = "group", values_to = "estimate", names_prefix = "group.") %>% 
  group_by(parameter, group) %>% 
  mutate(mu = mean(estimate),
         lower50 = HDIofMCMC(estimate, credMass = .5)[1],
         upper50 = HDIofMCMC(estimate, credMass = .5)[2],
         lower95 = HDIofMCMC(estimate)[1],
         upper95 = HDIofMCMC(estimate)[2],
         parameter = factor(parameter, ordered = T,
                            levels = c("Arew", "Apun", "betaF", "betaP")),
         parameter_lab = factor(parameter,
                                levels = c("Arew", "Apun", "betaF", "betaP"),
                                labels = c(expression(paste(italic(A),"+",sep="")),
                                           expression(paste(italic(A),"-",sep="")),
                                           expression(paste("\u03B2",italic(f),sep="")),
                                           expression(paste("\u03B2",italic(p),sep="")))),
         parameter_lab = case_when(str_detect(group, ".Con") ~ parameter_lab, T ~ NA))
```



## Build Plot
```{r, eval = T}
mu_parameter_plot = mu_parameters %>% 
  mutate(group = factor(group,
                        levels = c("Con",
                                   groups[1],
                                   groups[2],
                                   groups[3],
                                   "Con.SU",
                                   "Con.Dep",
                                   "Con.Anx"), ordered = T)) %>% 
  ggplot(aes(x = estimate)) +
    # geoms
    geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                   linewidth = .1, bins = 50) +
    geom_vline(xintercept = 0, color = "transparent") +
    geom_hline(yintercept = 0) +
    geom_vline(aes(xintercept = mu), color = "red2", linewidth = .25) +
    geom_vline(aes(xintercept = lower95), color = "red", linetype = "dashed", linewidth = .25) +
    geom_vline(aes(xintercept = upper95), color = "red", linetype = "dashed", linewidth = .25) +
    # themes
    scale_x_continuous(breaks = 0) +
    scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.margin = unit(c(.5, .5, .3, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(0, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(parameter~group, scales = "free",
                   nrow = 5, ncol = 7)
```



## Save Plot
```{r, eval = T}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name, sample,
          paste("Mus", sample, "Posterior Distributions.tiff", sep = " ")),
     width = 16, height = 10, units = "cm", res = 300)

  grid.newpage()
  pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
  grid.draw(mu_parameter_plot)
  
  # text
  grid.text(c("Con", groups[1], groups[2], groups[3],
              paste(groups[1], "Con", sep = "-"),
              paste(groups[2], "Con", sep = "-"),
              paste(groups[3], "Con", sep = "-")),
            x = c(.10, .235, .37, .51, .64, .7725, .918), y = .98,
            gp = gpar(fontsize = 9.5))
  grid.text(c(expression(paste(italic(A),"+",sep="")),
              expression(paste(italic(A),"-",sep="")),
              expression(paste("\u03B2",italic(f),sep="")),
              expression(paste("\u03B2",italic(p),sep="")),
              expression(italic(K))),
            x = rep(.965, 5), y = c(.89, .725, .55, .37, .195),
            gp = gpar(fontsize = 9.5))
  
dev.off()
```



# -------------------------------------------
# Beta Posterior Distributions
## Prep Data
```{r, eval = T}
beta_parameters = bind_rows(
  data.frame(parameter = "Arew", group = orl_posteriors$beta_Arew),
  data.frame(parameter = "Apun", group = orl_posteriors$beta_Apun),
  data.frame(parameter = "betaF", group = orl_posteriors$beta_betaF),
  data.frame(parameter = "betaB", group = orl_posteriors$beta_betaB)) %>% 
  select(parameter,
         beta.SU = group.3, 
         beta.Dep = group.4, 
         beta.Anx = group.5) %>% 
  pivot_longer(starts_with("beta"),
               names_to = "beta", values_to = "estimate", names_prefix = "beta.") %>% 
  group_by(parameter, beta) %>% 
  mutate(mu = mean(estimate),
         lower50 = HDIofMCMC(estimate, credMass = .5)[1],
         upper50 = HDIofMCMC(estimate, credMass = .5)[2],
         lower95 = HDIofMCMC(estimate)[1],
         upper95 = HDIofMCMC(estimate)[2],
         parameter = factor(parameter, ordered = T,
                            levels = c("Arew", "Apun", "betaF", "betaB")),
         parameter_lab = factor(parameter,
                                levels = c("Arew", "Apun", "betaF", "betaB"),
                                labels = c(expression(paste(italic(A),"+",sep="")),
                                           expression(paste(italic(A),"-",sep="")),
                                           expression(paste("\u03B2",italic(f),sep="")),
                                           expression(paste("\u03B2",italic(p),sep="")))),
         parameter_lab = case_when(str_detect(beta, "Anx") ~ parameter_lab, T ~ NA))
```



## Build Plot
```{r, eval = T}
beta_parameter_plot = beta_parameters %>% 
  mutate(beta = factor(beta,
                       levels = c(groups[1],
                                  groups[2],
                                  groups[3]), ordered = T)) %>% 
  ggplot(aes(x = estimate)) +
    # geoms
    geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                   linewidth = .1, bins = 50) +
    geom_vline(xintercept = 0, color = "transparent") +
    geom_hline(yintercept = 0) +
    geom_vline(aes(xintercept = mu), color = "red2", linewidth = .25) +
    geom_vline(aes(xintercept = lower95), color = "red", linetype = "dashed", linewidth = .25) +
    geom_vline(aes(xintercept = upper95), color = "red", linetype = "dashed", linewidth = .25) +
    # themes
    scale_x_continuous(breaks = 0) +
    scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.margin = unit(c(.5, .5, .3, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(0, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(parameter~beta, scales = "free",
                   nrow = 4, ncol = 3)
```



## Save Plot
```{r, eval = T}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name,
          sample,
          # paste0(sample, "_short"),
          paste("Betas", sample, "Posterior Distributions.tiff", sep = " ")),
     width = 7, height = 10, units = "cm", res = 300)

  grid.newpage()
  pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
  grid.draw(beta_parameter_plot)
  
  # text
  grid.text(c(groups[1], groups[2], groups[3]),
            x = c(.2, .515, .81), y = .98,
            gp = gpar(fontsize = 9.5))
  grid.text(c(expression(paste(italic(A),"+",sep="")),
              expression(paste(italic(A),"-",sep="")),
              expression(paste("\u03B2",italic(f),sep="")),
              expression(paste("\u03B2",italic(b),sep=""))),
            x = rep(.93, 5), y = c(.87, .655, .43, .22),
            gp = gpar(fontsize = 9.5))
  
dev.off()
```



# -------------------------------------------
# Choice Proportion Distributions
```{r}
# subset participant to exclude
sub_keep = stan_data$ID_participant[stan_data$X[,1,1] == 0]

orl_posteriors$choice_pred[,stan_data$ID_participant != sub_keep,,]

stan_data$card %>% data.frame() %>% View()

# build plot
deck_mu_diffs_plot = deck_grp_diffs %>% 
  filter(comparison == "Group Mean") %>% 
  mutate(group = factor(group, levels = c("Con", "SU", "Dep", "Anx"), ordered = T)) %>% 
  ggplot(aes(x = diff, fill = group)) +
  # geoms
  geom_text_npc(data = data.frame(group = factor(rep("Con", 4),
                                                 levels = c("Con", "SU", "Dep", "Anx"), ordered = T),
                                  deck = factor(c("A", "B", "C", "D"),
                                                levels = c("A", "B", "C", "D"),
                                                ordered = T),
                                  lab_ = c("A", "B", "C", "D")),
                aes(label = lab_), npcx = 0, npcy = 1.1, size = 4, vjust = 1) +
  geom_density(alpha = .5, linewidth = .25) +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0, linewidth = .25) +
  # scales
  scale_x_continuous(limits = c(-.3, .3), expand = c(0, 0), breaks = c(-.25, 0, .25),
                     labels = c("-.25", "0", ".25")) +
  scale_y_continuous(limits = c(0,NA), expand = expansion(mult = c(0, .05)), n.breaks = 3) +
  scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9", "#009E73"),
                    limits = c("Con", "SU", "Dep", "Anx")) +
  # themes
  labs(x = "Mu Estimate (Block 2-Block 1)", y = "Density") +
  coord_cartesian(clip = "off") +
  theme_classic() +
  theme(axis.text.x = element_text(color = "black"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.line.y = element_blank(),
        legend.text = element_text(size = 6),
        legend.key.size = unit(.5, "lines"), legend.spacing.y = unit(.05, "lines"),
        legend.position = "none",
        legend.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.title = element_blank(),
        plot.margin = unit(c(.1, .4, 0, .2), "cm"),
        panel.spacing.x = unit(.375, "cm"),
        panel.spacing.y = unit(.1, "cm"),
        strip.text = element_blank(),
        strip.background = element_rect(fill = "transparent", colour = "transparent"),
        panel.background = element_rect(fill = "transparent", colour = "transparent"),
        plot.background = element_rect(fill = "transparent", color = "transparent")) +
  facet_rep_wrap(group~deck, scales = "free",
                 nrow = 4, ncol = 4)


tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name,
          paste(sample, "Mu Diffs Distribution Plots.tiff", sep = " ")),
     width = 7, height = 7, units = "cm", res = 300)

  grid.newpage()
  # main plot
  pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
  grid.draw(deck_mu_diffs_plot)

  # text
  grid.text(c("Con", "SU", "Dep", "Anx"),
            x = .98, y = c(.9, .675, .445, .2), rot = 270,
            gp = gpar(fontsize = 9.5))

dev.off()
```



# Beta Posterior Distributions
## Prep Data
```{r, eval = T}
beta_parameters = bind_rows(data.frame(parameter = "Arew", group = orl_posteriors$beta_Arew),
                            data.frame(parameter = "Apun", group = orl_posteriors$beta_Apun),
                            data.frame(parameter = "betaF", group = orl_posteriors$beta_betaF),
                            data.frame(parameter = "betaP", group = orl_posteriors$beta_betaP)) %>% 
  select(parameter,
         beta.SU = group.2, 
         beta.Dep = group.3, 
         beta.Anx = group.4) %>% 
  pivot_longer(starts_with("beta"),
               names_to = "beta", values_to = "estimate", names_prefix = "beta.") %>% 
  group_by(parameter, beta) %>% 
  mutate(mu = mean(estimate),
         lower50 = HDIofMCMC(estimate, credMass = .5)[1],
         upper50 = HDIofMCMC(estimate, credMass = .5)[2],
         lower95 = HDIofMCMC(estimate)[1],
         upper95 = HDIofMCMC(estimate)[2],
         parameter = factor(parameter, ordered = T,
                            levels = c("Arew", "Apun", "betaF", "betaP", "K")),
         parameter_lab = factor(parameter,
                                levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                                labels = c(expression(paste(italic(A),"+",sep="")),
                                           expression(paste(italic(A),"-",sep="")),
                                           expression(paste("\u03B2",italic(f),sep="")),
                                           expression(paste("\u03B2",italic(p),sep="")))),
         parameter_lab = case_when(str_detect(beta, "Anx") ~ parameter_lab, T ~ NA))
```



## Build Plot
```{r, eval = T}
beta_parameter_plot = beta_parameters %>% 
  mutate(beta = factor(beta,
                       levels = c(groups[1],
                                  groups[2],
                                  groups[3]), ordered = T)) %>% 
  ggplot(aes(x = estimate)) +
    # geoms
    geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                   linewidth = .1, bins = 50) +
    geom_vline(xintercept = 0, color = "transparent") +
    geom_hline(yintercept = 0) +
    geom_vline(aes(xintercept = mu), color = "red2", linewidth = .25) +
    geom_vline(aes(xintercept = lower95), color = "red", linetype = "dashed", linewidth = .25) +
    geom_vline(aes(xintercept = upper95), color = "red", linetype = "dashed", linewidth = .25) +
    # themes
    scale_x_continuous(breaks = 0) +
    scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.margin = unit(c(.5, .5, .3, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(0, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(parameter~beta, scales = "free",
                   nrow = 4, ncol = 3)
```



## Save Plot
```{r, eval = T}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name, sample,
          paste("Betas", sample, "Posterior Distributions.tiff", sep = " ")),
     width = 7, height = 10, units = "cm", res = 300)

  grid.newpage()
  pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
  grid.draw(beta_parameter_plot)
  
  # text
  grid.text(c(groups[1], groups[2], groups[3]),
            x = c(.2, .515, .81), y = .98,
            gp = gpar(fontsize = 9.5))
  grid.text(c(expression(paste(italic(A),"+",sep="")),
              expression(paste(italic(A),"-",sep="")),
              expression(paste("\u03B2",italic(f),sep="")),
              expression(paste("\u03B2",italic(p),sep=""))),
            x = rep(.93, 5), y = c(.89, .725, .55, .37, .195),
            gp = gpar(fontsize = 9.5))
  
dev.off()
```



# -------------------------------------------



















