---
title: "Evaluating Group-Based Covariate Model"
output: html_document
date: "2023-03-07"
---



# -------------------------------------------
# Setup
## Load Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rstan)
library(hBayesDM)
library(bayesplot)
library(here)
library(miscTools)
library(cmdstanr)
library(stringi)
library(ggpp)
library(lemon)
library(grid)
library(zoo)
```



## RMD Setup
```{r}
groups = c("SU", "Dep", "Anx")
model_name = "Covariate_Joint_ORL"
sample = "T1_parent_SU_Dep_Anx"

# sample = "T1_parent_non_diag"
# sample = "T1_parent_SU"
# sample = "T1_parent_Dep"
sample = "T1_parent_Anx"

stan_data = readRDS(here("1_TADS_Parents_PP", "Data", "1_Stan",
                         paste("design", sample, "IGT.RDS", sep = "_")))

focal_parameters = c(
  "mu_Arew", "mu_Apun", "mu_K", "mu_betaF", "mu_betaP", 
  "sigma_Arew", "sigma_Apun", "sigma_K", "sigma_betaF", "sigma_betaP", 
  "Arew", "Apun", "K", "betaF", "betaP", 
  "R_Arew", "R_Apun", "R_K", "R_betaF", "R_betaP"
)


group_parameters <- grep("mu|sigma|R", focal_parameters, value=TRUE)
person_parameters <- grep("mu|sigma|R", focal_parameters, value=TRUE, invert=TRUE)
```



## Load Data
```{r}
orl_fit = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                       model_name,
                       paste(sample, model_name, "fit.rds", sep = "_")))


orl_posteriors = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                              model_name,
                              paste(sample, model_name, "posteriors.rds", sep = "_")))


orl_rhats = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                         model_name,
                         paste(sample, model_name, "rhats.rds", sep = "_")))
```



# -------------------------------------------
# Model Diagnostics
## Traceplots
```{r, eval = T}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name, sample,
          "group_traceplots.tiff"),
     width = 35, height = 25, units = "cm", res = 300)
  traceplot(
    orl_fit,
    pars = group_parameters
)
dev.off()


for(i in person_parameters){
  tiff(here("1_TADS_Parents_PP", "Figs_Tables",
            model_name, sample,
            paste(i, "traceplots.tiff")),
       width = 100, height = 100, units = "cm", res = 300)
    traceplot(orl_fit,
              pars = i
              ) %>% print()
    dev.off()
}
```



## Pairs Plots
```{r}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name, sample,
          paste("Group-Level", sample, "Pairs Plot.tiff", sep = " ")),
     width = 50, height = 50, units = "cm", res = 300)
  pairs(orl_fit, pars = c("mu_Arew", "mu_Apun", "mu_betaF", "mu_betaP", "mu_K",
                          "sigma_Arew", "sigma_Apun", "sigma_betaF", "sigma_betaP", "sigma_K")) %>% 
    print()
dev.off()
```



## PPC Plots
### Prep Data
```{r, eval = T}
source(here("1_TADS_Parents_PP", "Code", "R", "3_other", "helpful_functions.R"))

PPC_data = data.frame()

for(x in c(2:(length(groups)+1)))
  for(g in c(0,1)){
    PPC_data = calculate_PPCs(cards = stan_data$card[stan_data$X[,x,]==g,,],
                              trials = stan_data$Tsubj[stan_data$X[,x,]==g],
                              predicted_choices = orl_posteriors$choice_pred[,stan_data$X[,x,]==g,,], 
                              observed_choices = stan_data$choice[stan_data$X[,x,]==g,,],
                              data_type = "data.frame") %>%
      mutate(comparison = paste0("Con~", groups[x-1]),
             group = case_when(g == 0 ~ "Con", T ~ groups[x-1])) %>% 
      bind_rows(PPC_data)
  }
PPC_data = PPC_data %>% 
  mutate(group = factor(group, levels = c("Con", groups[1], groups[2],
                                          groups[3]), ordered = T))

saveRDS(PPC_data,
        here("1_TADS_Parents_PP", "Data", "2_Fitted",
             model_name,
             paste(sample, model_name, "PPC_data.rds", sep = "_")))
```



```{r}
PPC_data = readRDS(here("1_TADS_Parents_PP", "Data", "2_Fitted",
                        model_name,
                        paste(sample, model_name, "PPC_data.rds", sep = "_")))
```



### Between-Group PPC Plot
```{r, eval = T}
avg_width = 3

for(x in groups){
  tiff(here("1_TADS_Parents_PP", "Figs_Tables",
            model_name, sample,
            paste(x, sample, "Between-Group PPC.tiff")),
       width = 7, height = 7, units = "cm", res = 300)
  
    # simplify data
    PPC_plot = PPC_data %>% 
      filter(str_detect(comparison, x)) %>% 
      
      # bins
      group_by(trial, deck, group) %>% 
      summarise(observed = mean(observed), mu = mean(mu),
                lower50 = mean(lower50), upper50 = mean(upper50),
                lower95 = mean(lower95), upper95 = mean(upper95)) %>%
      mutate(block = ceiling(trial / 10)) %>% 
      ungroup() %>% group_by(deck, group) %>% 
      mutate(observed = rollapply(observed, width = avg_width, FUN = mean,
                                  na.rm = TRUE, fill = NA, partial = T),
             mu = rollapply(mu, width = 5, FUN = mean,
                            na.rm = TRUE, fill = NA, partial = T),
             lower50 = rollapply(lower50, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper50 = rollapply(upper50, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             lower95 = rollapply(lower95, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper95 = rollapply(upper95, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T)) %>% 
      ggplot(aes(x = trial, color = group, group = block)) +
      
      # calculate summary statistics by trials
      # summarise(observed = mean(observed), mu = mean(mu),
      #           lower50 = mean(lower50), upper50 = mean(upper50),
      #           lower95 = mean(lower95), upper95 = mean(upper95)) %>%
      # ggplot(aes(x = trial, color = group)) +
      
      # geoms
      geom_linerange(aes(ymin = lower95, ymax = upper95),
                     linewidth = .35, alpha = .35) +
      geom_linerange(aes(ymin = lower50, ymax = upper50),
                     linewidth = .35) +
      geom_point(aes(y = mu),
                 shape = 16, size = .75) +
      geom_line(aes(y = mu)) +
      geom_point(aes(y = observed),
                 shape = 21, size = .75, fill = "white") +
      geom_vline(xintercept = c(10.5, 20.5), linewidth = .25, linetype = "dashed") +
      # scales
      scale_y_continuous(limits = c(.5,1),
                         breaks = seq(0,1,.25)) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.background = element_rect(fill = "white", colour = "transparent"),
            legend.position = c(.84,.59), 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.key.size = unit(.25, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      guides(color = guide_legend(override.aes = list(size = 1.25))) +
      facet_rep_wrap(deck~.)
      
    print(PPC_plot)
  dev.off()
}
```



### Within-Group PPC Plot
```{r, eval = T}
avg_width = 3
for(x in groups){
  tiff(here("1_TADS_Parents_PP", "Figs_Tables",
            model_name, sample,
            paste(x, sample, "Within-Group PPC.tiff")),
       width = 5, height = 7, units = "cm", res = 300)
  
    # simplify data
    PPC_plot = PPC_data %>% 
      filter(str_detect(comparison, x)) %>% 
      
      # bins
      group_by(trial, deck, group) %>% 
      summarise(observed = mean(observed), mu = mean(mu),
                lower50 = mean(lower50),
                upper50 = mean(upper50),
                lower95 = mean(lower95),
                upper95 = mean(upper95)) %>%
      mutate(block = ceiling(trial / 10)) %>% 
      ungroup() %>% group_by(deck, group) %>% 
      mutate(observed = rollapply(observed, width = avg_width, FUN = mean,
                                  na.rm = TRUE, fill = NA, partial = T),
             mu = rollapply(mu, width = 5, FUN = mean,
                            na.rm = TRUE, fill = NA, partial = T),
             lower50 = rollapply(lower50, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper50 = rollapply(upper50, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             lower95 = rollapply(lower95, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper95 = rollapply(upper95, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             lower50 = case_when(lower50 < .5 ~ .5, T ~ lower50),
             lower95 = case_when(lower95 < .5 ~ .5, T ~ lower95)) %>% 
      ggplot(aes(x = trial, color = deck)) +
      
      # calculate summary statistics by trials
      # summarise(observed = mean(observed), mu = mean(mu),
      #           lower50 = mean(lower50), upper50 = mean(upper50),
      #           lower95 = mean(lower95), upper95 = mean(upper95)) %>%
      # ggplot(aes(x = trial, color = deck)) +
      
      # geoms
      geom_ribbon(aes(ymin = lower95, ymax = upper95, fill = deck), color = "transparent",
                  alpha = .25) +
      geom_ribbon(aes(ymin = lower50, ymax = upper50, fill = deck), color = "transparent",
                  alpha = .5) +
      geom_line(aes(y = mu), linewidth = .25) +
      geom_point(aes(y = observed, fill = deck), color = "black",
                 shape = 21, size = .75) +
      geom_vline(xintercept = c(10.5, 20.5), linewidth = .25, linetype = "dashed") +
      # scales
      scale_y_continuous(limits = c(.5,1),
                         breaks = seq(0,1,.25)) +
      scale_color_manual(values = c("#999999", "#E69F00", "#56B4E9", "#009E73")) +
      scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9", "#009E73")) +
      # theme
      labs(x = "Trial", y = "Proportion Play",
           color = expression(underline("Deck")), fill = expression(underline("Deck"))) +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.title = element_text(vjust = 4.4, hjust = .5, size = 8),
            legend.background = element_rect(fill = "white", colour = "black"),
            legend.position = c(.19,.94), 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            legend.margin = margin(t = .25, b = .01, r = .01, unit = 'cm'),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.key.size = unit(.25, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      guides(color = guide_legend(override.aes = list(size = 1.25), nrow = 2)) +
      facet_rep_grid(group~.)
      
    print(PPC_plot)
  dev.off()
}
```



### Between-/Within-Group PPC Plot
```{r, eval = T}
avg_width = 3

for(x in groups){
  tiff(here("1_TADS_Parents_PP", "Figs_Tables",
            model_name, sample,
            paste(x, sample, "Between-Within-Group PPC.tiff")),
       width = 15, height = 7, units = "cm", res = 300)
  
    # simplify data
    PPC_plot = PPC_data %>% 
      filter(str_detect(comparison, x)) %>% 
      
      # bins
      group_by(trial, deck, group) %>% 
      summarise(observed = mean(observed), mu = mean(mu),
                lower50 = mean(lower50), upper50 = mean(upper50),
                lower95 = mean(lower95), upper95 = mean(upper95)) %>%
      mutate(block = ceiling(trial / 10)) %>% 
      ungroup() %>% group_by(deck, group) %>% 
      mutate(observed = rollapply(observed, width = 5, FUN = mean,
                                  na.rm = TRUE, fill = NA, partial = T),
             mu = rollapply(mu, width = 5, FUN = mean,
                            na.rm = TRUE, fill = NA, partial = T),
             lower50 = rollapply(lower50, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper50 = rollapply(upper50, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             lower95 = rollapply(lower95, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T),
             upper95 = rollapply(upper95, width = avg_width, FUN = mean,
                                 na.rm = TRUE, fill = NA, partial = T)) %>% 
      ggplot(aes(x = trial, group = trial)) +
      
      # calculate summary statistics by trials
      # summarise(observed = mean(observed), mu = mean(mu),
      #           lower50 = mean(lower50), upper50 = mean(upper50),
      #           lower95 = mean(lower95), upper95 = mean(upper95)) %>%
      # ggplot(aes(x = trial,
      #            group = trial)) +
      
      # geoms
      geom_linerange(aes(ymin = lower95, ymax = upper95),
                     linewidth = .35, color = "goldenrod3", alpha = .35) +
      geom_linerange(aes(ymin = lower50, ymax = upper50),
                     linewidth = .35, color = "goldenrod3") +
      geom_point(aes(y = mu, color = "Predicted", fill = "Predicted"),
                 shape = 21, size = .75) +
      geom_point(aes(y = observed, color = "Observed", fill = "Observed"),
                 shape = 21, size = .75) +
      geom_vline(xintercept = c(10.5, 20.5), linewidth = .25, linetype = "dashed") +
      # scales
      scale_y_continuous(limits = c(.5,1),
                         breaks = seq(0,1,.25)) +
      scale_color_manual(name = "hello", values = c("Observed" = "black", "Predicted" = "goldenrod3")) +
      scale_fill_manual(name = "hello", values = c("Observed" = "black", "Predicted" = "white")) +
      # theme
      labs(x = "Trial", y = "Proportion Play") +
      theme_classic() +
      theme(axis.text = element_text(color = "black"),
            legend.title = element_blank(),
            legend.background = element_rect(fill = "white", colour = "transparent"),
            legend.position = c(.84,.59), 
            legend.spacing.x = unit(0, 'cm'),
            legend.spacing.y = unit(-.25, 'cm'),
            legend.text = element_text(size = 8),
            strip.background = element_blank(),
            panel.spacing.x = unit(-.5,"lines"),
            legend.key.size = unit(.25, "cm"),
            panel.spacing.y = unit(0,"lines")) +
      guides(color = guide_legend(override.aes = list(size = 1.25))) +
      facet_rep_grid(group~deck,
                     labeller = labeller(deck = c("A" = "Deck A", "B" = "Deck B",
                                                  "C" = "Deck C", "D" = "Deck D")))
      
    print(PPC_plot)
  dev.off()
}
```



# -------------------------------------------
# Mu Posterior Distributions
## Prep Data
```{r, eval = T}
mu_parameters = bind_rows(data.frame(parameter = "Arew", group = orl_posteriors$mu_Arew),
                          data.frame(parameter = "Apun", group = orl_posteriors$mu_Apun),
                          data.frame(parameter = "betaF", group = orl_posteriors$mu_betaF),
                          data.frame(parameter = "betaP", group = orl_posteriors$mu_betaP),
                          data.frame(parameter = "K", group = orl_posteriors$mu_K)) %>% 
  select(group.Con = group.1.1, 
         group.SU = group.1.2, 
         group.Dep = group.1.3, 
         group.Anx = group.1.4, 
         everything()) %>% 
  mutate(group.Con.SU = group.SU - group.Con,
         group.Con.Dep = group.Dep - group.Con,
         group.Con.Anx = group.Anx - group.Con) %>% 
  pivot_longer(starts_with("group"),
               names_to = "group", values_to = "estimate", names_prefix = "group.") %>% 
  group_by(parameter, group) %>% 
  mutate(mu = mean(estimate),
         lower50 = HDIofMCMC(estimate, credMass = .5)[1],
         upper50 = HDIofMCMC(estimate, credMass = .5)[2],
         lower95 = HDIofMCMC(estimate)[1],
         upper95 = HDIofMCMC(estimate)[2],
         parameter = factor(parameter, ordered = T,
                            levels = c("Arew", "Apun", "betaF", "betaP", "K")),
         parameter_lab = factor(parameter,
                                levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                                labels = c(expression(paste(italic(A),"+",sep="")),
                                           expression(paste(italic(A),"-",sep="")),
                                           expression(paste("\u03B2",italic(f),sep="")),
                                           expression(paste("\u03B2",italic(p),sep="")),
                                           expression(italic(K)))),
         parameter_lab = case_when(str_detect(group, ".Con") ~ parameter_lab, T ~ NA))
```



## Build Plot
```{r, eval = T}
mu_parameter_plot = mu_parameters %>% 
  mutate(group = factor(group,
                        levels = c("Con",
                                   groups[1],
                                   groups[2],
                                   groups[3],
                                   "Con.SU",
                                   "Con.Dep",
                                   "Con.Anx"), ordered = T)) %>% 
  ggplot(aes(x = estimate)) +
    # geoms
    geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                   linewidth = .1, bins = 50) +
    geom_vline(xintercept = 0, color = "transparent") +
    geom_hline(yintercept = 0) +
    geom_vline(aes(xintercept = mu), color = "red2", linewidth = .25) +
    geom_vline(aes(xintercept = lower95), color = "red", linetype = "dashed", linewidth = .25) +
    geom_vline(aes(xintercept = upper95), color = "red", linetype = "dashed", linewidth = .25) +
    # themes
    scale_x_continuous(breaks = 0) +
    scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.margin = unit(c(.5, .5, .3, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(0, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(parameter~group, scales = "free",
                   nrow = 5, ncol = 7)
```



## Save Plot
```{r, eval = T}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name, sample,
          paste("Mus", sample, "Posterior Distributions.tiff", sep = " ")),
     width = 16, height = 10, units = "cm", res = 300)

  grid.newpage()
  pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
  grid.draw(mu_parameter_plot)
  
  # text
  grid.text(c("Con", groups[1], groups[2], groups[3],
              paste(groups[1], "Con", sep = "-"),
              paste(groups[2], "Con", sep = "-"),
              paste(groups[3], "Con", sep = "-")),
            x = c(.10, .235, .37, .51, .64, .7725, .918), y = .98,
            gp = gpar(fontsize = 9.5))
  grid.text(c(expression(paste(italic(A),"+",sep="")),
              expression(paste(italic(A),"-",sep="")),
              expression(paste("\u03B2",italic(f),sep="")),
              expression(paste("\u03B2",italic(p),sep="")),
              expression(italic(K))),
            x = rep(.965, 5), y = c(.89, .725, .55, .37, .195),
            gp = gpar(fontsize = 9.5))
  
dev.off()
```



# -------------------------------------------
# Beta Posterior Distributions
## Prep Data
```{r, eval = T}
beta_parameters = bind_rows(data.frame(parameter = "Arew", group = orl_posteriors$beta_Arew),
                            data.frame(parameter = "Apun", group = orl_posteriors$beta_Apun),
                            data.frame(parameter = "betaF", group = orl_posteriors$beta_betaF),
                            data.frame(parameter = "betaP", group = orl_posteriors$beta_betaP),
                            data.frame(parameter = "K", group = orl_posteriors$beta_K)) %>% 
  select(parameter,
         beta.SU = group.2, 
         beta.Dep = group.3, 
         beta.Anx = group.4) %>% 
  pivot_longer(starts_with("beta"),
               names_to = "beta", values_to = "estimate", names_prefix = "beta.") %>% 
  group_by(parameter, beta) %>% 
  mutate(mu = mean(estimate),
         lower50 = HDIofMCMC(estimate, credMass = .5)[1],
         upper50 = HDIofMCMC(estimate, credMass = .5)[2],
         lower95 = HDIofMCMC(estimate)[1],
         upper95 = HDIofMCMC(estimate)[2],
         parameter = factor(parameter, ordered = T,
                            levels = c("Arew", "Apun", "betaF", "betaP", "K")),
         parameter_lab = factor(parameter,
                                levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                                labels = c(expression(paste(italic(A),"+",sep="")),
                                           expression(paste(italic(A),"-",sep="")),
                                           expression(paste("\u03B2",italic(f),sep="")),
                                           expression(paste("\u03B2",italic(p),sep="")),
                                           expression(italic(K)))),
         parameter_lab = case_when(str_detect(beta, "Anx") ~ parameter_lab, T ~ NA))
```



## Build Plot
```{r, eval = T}
beta_parameter_plot = beta_parameters %>% 
  mutate(beta = factor(beta,
                       levels = c(groups[1],
                                  groups[2],
                                  groups[3]), ordered = T)) %>% 
  ggplot(aes(x = estimate)) +
    # geoms
    geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                   linewidth = .1, bins = 50) +
    geom_vline(xintercept = 0, color = "transparent") +
    geom_hline(yintercept = 0) +
    geom_vline(aes(xintercept = mu), color = "red2", linewidth = .25) +
    geom_vline(aes(xintercept = lower95), color = "red", linetype = "dashed", linewidth = .25) +
    geom_vline(aes(xintercept = upper95), color = "red", linetype = "dashed", linewidth = .25) +
    # themes
    scale_x_continuous(breaks = 0) +
    scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
    labs(x = "Estimate", y = "Density") +
    coord_cartesian(clip = "off") +
    theme_classic() +
    theme(axis.text.x = element_text(color = "black"),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.margin = unit(c(.5, .5, .3, .1), "cm"),
          panel.spacing.x = unit(.5, "cm"),
          panel.spacing.y = unit(0, "cm"),
          strip.background = element_rect(fill = "transparent", colour = "transparent"),
          strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent")) +
    facet_rep_wrap(parameter~beta, scales = "free",
                   nrow = 5, ncol = 3)
```



## Save Plot
```{r, eval = T}
tiff(here("1_TADS_Parents_PP", "Figs_Tables",
          model_name, sample,
          paste("Betas", sample, "Posterior Distributions.tiff", sep = " ")),
     width = 7, height = 10, units = "cm", res = 300)

  grid.newpage()
  pushViewport(viewport(x = .5, y = .5, width = 1, height = 1))
  grid.draw(beta_parameter_plot)
  
  # text
  grid.text(c(groups[1], groups[2], groups[3]),
            x = c(.2, .515, .81), y = .98,
            gp = gpar(fontsize = 9.5))
  grid.text(c(expression(paste(italic(A),"+",sep="")),
              expression(paste(italic(A),"-",sep="")),
              expression(paste("\u03B2",italic(f),sep="")),
              expression(paste("\u03B2",italic(p),sep="")),
              expression(italic(K))),
            x = rep(.93, 5), y = c(.89, .725, .55, .37, .195),
            gp = gpar(fontsize = 9.5))
  
dev.off()
```



# -------------------------------------------
# Single-Subject Data
## Prep Data
```{r, eval = T}
ind_parameters = bind_cols(data.frame(Arew = apply(orl_posteriors$Arew, 2, mean)),
                           data.frame(Apun = apply(orl_posteriors$Apun, 2, mean)),
                           data.frame(betaF = apply(orl_posteriors$betaF, 2, mean)),
                           data.frame(betaP = apply(orl_posteriors$betaP, 2, mean)),
                           data.frame(K = apply(orl_posteriors$K, 2, mean))) %>% 
  bind_cols(data.frame(ID_participant = stan_data$ID_participant,
                       ID_OG = stan_data$ID_OG,
                       ID_number = stan_data$ID_number,
                       participant_number = stan_data$participant_number,
                       SU = stan_data$X[,2,1],
                       dep = stan_data$X[,3,1],
                       anx = stan_data$X[,4,1])) %>% 
  pivot_longer(c("Arew", "Apun", "betaF", "betaP", "K"),
               names_to = "parameter", values_to = "estimate")

grp_parameters = bind_rows(data.frame(parameter = "Arew", group = orl_posteriors$mu_Arew),
                           data.frame(parameter = "Apun", group = orl_posteriors$mu_Apun),
                           data.frame(parameter = "betaF", group = orl_posteriors$mu_betaF),
                           data.frame(parameter = "betaP", group = orl_posteriors$mu_betaP),
                           data.frame(parameter = "K", group = orl_posteriors$mu_K)) %>% 
  select(group.Con = group.1.1, 
         group.SU = group.1.2, 
         group.Dep = group.1.3, 
         group.Anx = group.1.4, 
         everything()) %>% 
  pivot_longer(starts_with("group"),
               names_to = "group", values_to = "estimate", names_prefix = "group.") %>% 
  group_by(parameter, group) %>% 
  reframe(mu = mean(estimate)) %>% 
  mutate(parameter = factor(parameter, ordered = T,
                            levels = c("Arew", "Apun", "betaF", "betaP", "K"))) %>% 
  pivot_wider(names_from = "group", values_from = "mu", names_prefix = "mu_")

ind_grp_parameters = left_join(ind_parameters, grp_parameters)
```



## Anx Inds
```{r}
subset_Con_Anx = ind_grp_parameters %>% 
  mutate(diff = case_when(anx == 0 ~ (estimate - mu_Con)^2,
                          anx == 1 ~ (estimate - mu_Anx)^2)) %>% 
  group_by(parameter) %>% 
  mutate(diff = ((diff - mean(diff)) / sd(diff))^2) %>% 
  group_by(ID_participant, anx) %>% 
  reframe(SSE = sum(diff)) %>% 
  group_by(anx) %>% 
  arrange(SSE, .by_group = T) %>% 
  top_n(-3)

choice_obs = bind_cols(data.frame(ID_participant = stan_data$ID_participant,
                                  ID_OG = stan_data$ID_OG,
                                  ID_number = stan_data$ID_number,
                                  participant_number = stan_data$participant_number,
                                  SU = stan_data$X[,2,1],
                                  dep = stan_data$X[,3,1],
                                  anx = stan_data$X[,4,1],
                                  card = stan_data$card[],
                                  choice = stan_data$choice)) %>% 
  pivot_longer(c(starts_with("choice"), starts_with("card")),
               names_to = c("variable", "trial"), names_sep = "\\.",
               names_transform = list(trial = as.numeric)) %>% 
  pivot_wider(names_from = "variable", values_from = "value") %>% 
  filter(ID_participant %in% unique(subset_Con_Anx$ID_participant)) %>% 
  mutate(choice = case_when(choice == 2 ~ 0, T ~ choice)) %>% 
  group_by(ID_participant, card) %>% 
  arrange(trial) %>% 
  mutate(prop = rollapply(choice, width = 5, FUN = mean,
                          na.rm = TRUE, fill = NA, partial = T))

ggplot(choice_obs, aes(x = trial, y = prop, color = factor(anx), group = ID_participant)) +
  geom_line() +
  theme_classic() +
  facet_rep_grid(card~factor(anx))
```



# -------------------------------------------
# Inspecting Parameter Characteristics
## Learning Rates
* Do participants with Arew > Apun show more sensitivity to gains whereas participants with Apun > Arew show more sensitivity to losses?

### Calculate Play Proportions
```{r}
choice_proportions = bind_cols(data.frame(ID_participant = stan_data$ID_participant,
                                          ID_OG = stan_data$ID_OG,
                                          ID_number = stan_data$ID_number,
                                          participant_number = stan_data$participant_number,
                                          SU = stan_data$X[,2,1],
                                          dep = stan_data$X[,3,1],
                                          anx = stan_data$X[,4,1],
                                          card = stan_data$card,
                                          choice = stan_data$choice)) %>% 
  pivot_longer(c(starts_with("choice"), starts_with("card")),
               names_to = c("variable", "trial"), names_sep = "\\.",
               names_transform = list(trial = as.numeric)) %>% 
  pivot_wider(names_from = "variable", values_from = "value") %>% 
  mutate(choice = case_when(choice == 2 ~ 0, T ~ choice),
         block = case_when(trial <= 40 ~ 1, trial <= 80 ~ 2, T ~ 3)) %>% 
  group_by(ID_participant, anx, block, card) %>% # by block
  filter(block == 3) %>% 
  # group_by(ID_participant, dep, card) %>% # session-wide
  reframe(prop = mean(choice, na.rm = T)) %>% 
  left_join(pivot_wider(ind_parameters, names_from = "parameter", values_from = "estimate")) %>% 
  filter(ID_participant != 22) %>% 
  mutate(diff_A = Arew - Apun,
         dom = case_when(diff_A > 0 ~ "Arew", diff_A <= 0 ~ "Apun"))
```



### Play Proportion Plot
```{r}
choice_proportions %>% 
  ggplot(aes(x = dom, y = prop)) +
    geom_violin(trim = F) +
    # stat
    theme_classic() + 
    # stat_summary(fun.data = mean_sdl, mult = 1, 
    #              geom = "pointrange", color = "red") +
    geom_boxplot(width = 0.1) +
    facet_rep_grid(anx~card)
```



```{r}
card_play_cors = list()

for(c in c("A", "B", "C", "D")) {
  cor_data = filter(choice_proportions, card == c)
  card_play_cors[[c]] = wBoot::boot.cor.bca(choice_proportions$prop, choice_proportions$diff_A)
}
```



# -------------------------------------------
# Depressed Individuals
## BetaF: Win-Frequency Sensitivity
* Do participants with higher win-frequency sensitivities choose Decks C & D more?
* To test this, examine whether
  + Do depressed individuals (who had higher estimates of BetaF) show a greater proportion of plays on Decks C & D than non-depressed individuals (who had lower estimates of BetaF)?
  + Are estimates of BetaF correlated with the proportion of plays on Decks C & D with depressed and non-depressed individuals?


### Calculate AC/BD Play Proportions
```{r}
pair_proportions = bind_cols(data.frame(ID_participant = stan_data$ID_participant,
                                        ID_OG = stan_data$ID_OG,
                                        ID_number = stan_data$ID_number,
                                        participant_number = stan_data$participant_number,
                                        SU = stan_data$X[,2,1],
                                        dep = stan_data$X[,3,1],
                                        anx = stan_data$X[,4,1],
                                        card = stan_data$card[],
                                        choice = stan_data$choice)) %>% 
  pivot_longer(c(starts_with("choice"), starts_with("card")),
               names_to = c("variable", "trial"), names_sep = "\\.",
               names_transform = list(trial = as.numeric)) %>% 
  pivot_wider(names_from = "variable", values_from = "value") %>% 
  mutate(choice = case_when(choice == 2 ~ 0, T ~ choice),
         pair = case_when(card == 2 | card == 4 ~ "BD", T ~ "AC"),
         block = case_when(trial <= 40 ~ 1, trial <= 80 ~ 2, T ~ 3)) %>% 
  # group_by(ID_participant, dep, pair, block) %>% # by block
  group_by(ID_participant, dep, pair) %>% # session-wide
  reframe(prop = mean(choice, na.rm = T)) %>% 
  left_join(filter(ind_parameters, parameter == "K")) %>% 
  filter(ID_participant != 22)
```



### AC/BD Play Proportion Plot
```{r}
pair_proportions %>% 
  group_by(dep, pair) %>% # session-wide
  ggplot(aes(x = factor(dep), y = prop)) +
    geom_violin(trim = F) +
    # stat
    theme_classic() + 
    # stat_summary(fun.data = mean_sdl, mult = 1, 
    #              geom = "pointrange", color = "red") +
    geom_boxplot(width = 0.1) +
    facet_rep_grid(.~pair)
```



### BD Correlations
```{r}
grp_BD_proportions = pair_proportions %>% 
  filter(pair == "BD")
  # filter(block == 3, pair == "BD")
BD_cor = wBoot::boot.cor.bca(grp_BD_proportions$prop, grp_BD_proportions$estimate)
BD_cor


nondep_BD_proportions = pair_proportions %>% 
  filter(dep == 0, pair == "BD")
  # filter(dep == 0 & block == 3, pair == "BD")
BD_nondep_cor = wBoot::boot.cor.bca(nondep_BD_proportions$prop,
                                    nondep_BD_proportions$estimate)
BD_nondep_cor


dep_BD_proportions = pair_proportions %>% 
  filter(dep == 1, pair == "BD")
  # filter(dep == 1 & block == 3)
BD_dep_cor = wBoot::boot.cor.bca(dep_BD_proportions$prop,
                                 dep_BD_proportions$estimate)
BD_dep_cor
```



### AC Correlations
```{r}
grp_AC_proportions = pair_proportions %>% 
  filter(pair == "AC")
  # filter(block == 3, pair == "BD")
AC_cor = wBoot::boot.cor.bca(grp_AC_proportions$prop, grp_AC_proportions$estimate)
AC_cor


nondep_AC_proportions = pair_proportions %>% 
  filter(dep == 0, pair == "AC")
  # filter(dep == 0 & block == 3, pair == "BD")
AC_nondep_cor = wBoot::boot.cor.bca(nondep_AC_proportions$prop,
                                    nondep_AC_proportions$estimate)
AC_nondep_cor


dep_AC_proportions = pair_proportions %>% 
  filter(dep == 1, pair == "AC")
  # filter(dep == 1 & block == 3)
AC_dep_cor = wBoot::boot.cor.bca(dep_AC_proportions$prop,
                                 dep_AC_proportions$estimate)
AC_dep_cor
```



# -------------------------------------------
```{r}

```














