---
title: "Fitting Joint Test-Retest ORL"
output: html_document
date: "2023-03-07"
---



# -------------------------------------------
# Setup
## Load Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rstan)
library(hBayesDM)
library(bayesplot)
library(here)
library(miscTools)
library(wBoot)
library(cmdstanr)
library(stringi)
library(ggpp)
library(lemon)
source(here("1_IGT_PP", "Code", "R", "3_other", "helpful_functions.R"))
```



## Load Data
```{r}
stan_data = readRDS(here("1_IGT_PP", "Data", "1_Preprocessed", "stan_ready_ORL_IGT.rds"))
```



# -------------------------------------------
# Check Model
```{r, eval = T}
model_code = cmdstan_model(here("1_IGT_PP", "Code", "Stan", 
                                "igt_orl_joint_playfic_playupdate_modifiedK_simplified.stan"), compile = F)

model_code$check_syntax(quiet = T)
```



# Fit Model
```{r, eval = T}
# Compile model
orl_model = stan_model(here("1_IGT_PP", "Code", "Stan", "igt_orl_joint_playfic_playupdate_modifiedK_simplified.stan"))


# Fit model
orl_fit = sampling(orl_model, 
                   data   = stan_data, 
                   iter   = 5000, 
                   warmup = 1000, 
                   chains = 4, 
                   cores  = 4,
                   seed   = 43210)


#save the fitted model as an .rds file
saveRDS(orl_fit, here("1_IGT_PP", "Data", "2_Fitted", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
                      "orl_pp_joint_playfic_playupdate_modifiedK_simplified_fit.rds"))
```



```{r}
orl_fit = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
                       "orl_pp_joint_playfic_playupdate_modifiedK_simplified_fit.rds"))

iterations = orl_fit@sim$chains * (orl_fit@sim$iter - orl_fit@sim$warmup)
```



# -------------------------------------------
# Model Diagnostics
```{r, eval = T}
orl_posteriors <- extract(orl_fit)
saveRDS(orl_posteriors, here("1_IGT_PP", "Data", "2_Fitted", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
                             "orl_pp_joint_playfic_playupdate_modifiedK_simplified_posteriors.rds"))
```



```{r}
orl_posteriors = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
                              "orl_pp_joint_playfic_playupdate_modifiedK_simplified_posteriors.rds"))


focal_parameters <- c(
  "mu_Arew", "mu_Apun", "mu_K", "mu_betaF", "mu_betaP", 
  "sigma_Arew", "sigma_Apun", "sigma_K", "sigma_betaF", "sigma_betaP", 
  "Arew", "Apun", "K", "betaF", "betaP",
  "R_Arew[1,2]", "R_Apun[1,2]", "R_K[1,2]", "R_betaF[1,2]", "R_betaP[1,2]"
)

group_parameters <- grep("mu|sigma|R_", focal_parameters, value=TRUE)
person_parameters <- grep("mu|sigma|R_", focal_parameters, value=TRUE, invert=TRUE)
```



## Rhat
```{r, eval = T}
rhats = rhat(orl_fit, pars = focal_parameters) %>%
  data.frame() %>% mutate(parameter = rownames(.))
saveRDS(rhats, here("1_IGT_PP", "Data", "2_Fitted", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
                    "orl_pp_joint_playfic_playupdate_modifiedK_simplified_rhats.rds"))
```



```{r}
rhats = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
                     "orl_pp_joint_playfic_playupdate_modifiedK_simplified_rhats.rds"))
```



## Traceplots
```{r, eval = T}
tiff(here("1_IGT_PP", "Figs_Tables", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
          "orl_pp_joint_playfic_playupdate_modifiedK_simplified_group_traceplots.tiff"),
     width = 35, height = 25, units = "cm", res = 300)
  traceplot(
    orl_fit,
    pars = group_parameters
)
dev.off()


for(i in person_parameters){
  tiff(here("1_IGT_PP", "Figs_Tables", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
            paste("orl_pp_joint_playfic_playupdate_modifiedK_simplified_", i, "_traceplots.tiff", sep = "")),
       width = 35, height = 25, units = "cm", res = 300)
    traceplot(orl_fit,
              pars = i
              ) %>% print()
    dev.off()
}
```



# -------------------------------------------
# Inspect Parameters
## Means +/- PI
```{r, eval = T}
tiff(here("1_IGT_PP", "Figs_Tables", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
          "orl_pp_joint_playfic_playupdate_modifiedK_simplified_posterior_means.tiff"),
     width = 35, height = 25, units = "cm", res = 300)
  plot(orl_fit, pars = group_parameters)
dev.off()
```



## Posterior Distributions
```{r}
tiff(here("1_IGT_PP", "Figs_Tables", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
          "orl_pp_joint_playfic_playupdate_modifiedK_simplified_posterior_distributions.tiff"),
     width = 30, height = 20, units = "cm", res = 300)
  par(mfrow = c(5, 5))
  # Mus & Sigmas
  for(s in 1:2){
    for(i in grep("mu|sigma", group_parameters, value = T)){
      plot(density(orl_posteriors[[i]][,s]), main = paste(i, s))
      abline(v = mean(orl_posteriors[[i]][,s]))
    }
  }
  
  for(i in grep("R_", group_parameters, value = T)){
    plot(density(orl_posteriors[[str_remove(i, "\\[1,2\\]")]][,2,1]), main = i)
    abline(v = mean(orl_posteriors[[i]][,2,1]))
  }
dev.off()
```



# -------------------------------------------
# Results
## PPC Plot
```{r}
choice_proportions = calculate_proportions(orl_posteriors, stan_data,
                                           data_type = "data.frame"
                                           # data_type = "list_of_matrices"
                                           )
saveRDS(choice_proportions,
        here("1_IGT_PP", "Data", "2_Fitted", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
             "orl_pp_joint_playfic_playupdate_modifiedK_simplified_ppcs.rds"))

choice_proportions = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
                                  "orl_pp_joint_playfic_playupdate_modifiedK_simplified_ppcs.rds"))
```



```{r}
tiff(here("1_IGT_PP", "Figs_Tables", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
          "ORL_joint_playfic_playupdate_modifiedK_simplified_PPC.tiff"),
     width = 15, height = 8, units = "cm", res = 300)

  # simplify data
  choice_proportions %>% 
    group_by(trial, deck, session) %>% 
    summarise(observed = mean(observed), mu = mean(mu),
              lower50 = mean(lower50), upper50 = mean(upper50),
              lower95 = mean(lower95), upper95 = mean(upper95)) %>%
    # plotting
    ggplot(aes(x = trial,
               group = trial)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95),
                   linewidth = .35, color = "goldenrod3", alpha = .35) +
    geom_linerange(aes(ymin = lower50, ymax = upper50),
                   linewidth = .35, color = "goldenrod3") +
    geom_point(aes(y = mu), shape = 21,
               color = "goldenrod3", fill = "white",
               size = .75) +
    geom_point(aes(y = observed), size = .75) +
    scale_y_continuous(limits = c(0,1), expand = c(0,0),
                       breaks = seq(0,1,.25)) +
    labs(x = "Trial", y = "Proportion Play") +
    theme_classic() +
    theme(axis.text = element_text(color = "black"),
          strip.background = element_blank(),
          panel.spacing.x = unit(-.5,"lines"),
          panel.spacing.y = unit(0,"lines")) +
    facet_rep_grid(session~deck,
                   labeller = labeller(session = c("1" = "Session 1", "2" = "Session 2"),
                                       deck = c("A" = "Deck A", "B" = "Deck B",
                                                "C" = "Deck C", "D" = "Deck D")))
dev.off()
```



## Reliability
```{r}
tiff(here("1_IGT_PP", "Figs_Tables", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
          "reliability_coefficients.tiff"),
     width = 15, height = 6.25, units = "cm", res = 300)
  bind_rows(data.frame(parameter = "Arew", r = orl_posteriors$R_Arew[,2,1]),
            data.frame(parameter = "Apun", r = orl_posteriors$R_Apun[,2,1]),
            data.frame(parameter = "betaF", r = orl_posteriors$R_betaF[,2,1]),
            data.frame(parameter = "betaP", r = orl_posteriors$R_betaP[,2,1]),
            data.frame(parameter = "K", r = orl_posteriors$R_K[,2,1])) %>% 
    mutate(parameter = factor(parameter,
                              levels = c("Arew", "Apun", "betaF", "betaP", "K"),
                              labels = c(expression(paste(italic(A),"+",sep="")),
                                         expression(paste(italic(A),"-",sep="")),
                                         expression(paste("\u03B2",italic(f),sep="")),
                                         expression(paste("\u03B2",italic(p),sep="")),
                                         expression(italic(K))))) %>% 
    group_by(parameter) %>% 
    mutate(mu_r = mean(r), lower = HDIofMCMC(r)[1], upper = HDIofMCMC(r)[2],
           mu_r_lab = paste(ifelse(sign(round(mu_r,2))==1," ","-"),
                            stri_pad_right(str_remove(abs(round(mu_r,2)), "^0+"),
                                           width = 3, pad = "0"),sep=""), 
           lower = as.numeric(str_remove(lower, "\\(")),
           upper = as.numeric(str_remove(upper, "\\(")),
           
           lower_lab = paste(ifelse(sign(round(lower,2))==1,"","-"),
                             stri_pad_right(str_remove(abs(round(lower,2)), "^0+"),
                                            width = 3, pad = "0"),sep=""), 
           upper_lab = paste(ifelse(sign(round(upper,2))==1,"","-"),
                             stri_pad_right(str_remove(abs(round(upper,2)), "^0+"),
                                            width = 3, pad = "0"),sep=""),
           upper_lab = case_when(round(upper,2) == 1 ~ "1.00", T ~ upper_lab),
           mu_rCI = paste("=",mu_r_lab," (",lower_lab,",",upper_lab,")",sep="")) %>% 
    ggplot(aes(x = r)) +
      # geoms
      geom_histogram(aes(y = ..density..), color = "black", fill = "gray45",
                     linewidth = .1, bins = 50) +
      geom_text_npc(aes(npcx = "left", npcy = "top"), label = expression(italic(r)),
                    size = 2, hjust = -3, vjust = -1.425) +
      geom_text_npc(aes(npcx = "middle", npcy = "top",
                        label = mu_rCI), size = 2, vjust = -1) +
      geom_hline(yintercept = 0) +
      geom_vline(aes(xintercept = mu_r), color = "red2") +
      # scales
      scale_x_continuous(limits = c(-1,1), expand = c(0,0), breaks = seq(-1,1,.5),
                         labels = c("-1","-.5","0",".5", "1")) +
      scale_y_continuous(limits = c(0,NA), expand = c(0,0), n.breaks = 3) +
      # themes
      labs(x = "Reliability Coefficient", y = "Density") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(axis.text.x = element_text(color = "black"),
            axis.text.y = element_text(color = "black"),
            axis.ticks = element_line(color = "black"),
            axis.line.x = element_line(color = "transparent"),
            plot.margin = unit(c(.3, .3, .3, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            strip.text.x = element_text(size = 12, vjust = 1.5),
            strip.text.y = element_blank(),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent"),
            aspect.ratio = 1) +
      facet_rep_grid(.~parameter, scales = "free",
                     labeller = label_parsed) +
      geom_segment(aes(x = lower, xend = upper, y = .025, yend = .025),
                   size = 1, color = "red2", linewidth = .5)
dev.off()
```



## Self-Report Correlations
```{r}
selfreport_models = readRDS(here("1_IGT_PP", "Data", "2_Fitted", "binomial_selfreport_indMu_fits.rds"))
selfreport = readRDS(here("1_IGT_PP", "Data", "1_Preprocessed", "stan_ready_binomial_selfreport.rds"))
```



```{r}
# Check that orl and self-report IDs are in same order between data fed to models
for(scale in names(selfreport)){
  data.frame(orl_IDs = stan_data$subjIDs,
             selfreport_IDs = as.numeric(selfreport[[scale]]$IDs)) %>% 
    mutate(not_equal = ifelse(orl_IDs == selfreport_IDs, 0, 1)) %>% 
    reframe(ID_Check = ifelse(sum(not_equal) == 0, "EQUAL", "NOT EQUAL")) %>% 
    print()
}
```



```{r}
scales = c(# Session 1 only
           "prdep_tot", "masqGDA", "masqAA", "masqGDD",
           # "masqAD", # Removed
           # Both Sessions
           "bastot", "basdrive", "basfunsk", "basrewres",
           "bis", "panas_pa", "panas_na", "shaps_tot")


selfreport_posteriors = list()
sr_posterior_means = list()

for(scale in scales){
  dimensions = c(2,3)
  if(length(dim(selfreport_posteriors[[scale]]$theta)) == 2) dimensions = 2
  
  selfreport_posteriors[[scale]] = extract(selfreport_models[[scale]], par = "theta")
  sr_posterior_means[[scale]] = apply(selfreport_posteriors[[scale]]$theta*selfreport[[scale]]$M, 2, mean)
}

overall_orl_posterior_means = list()

for(parameter in person_parameters){
  overall_orl_posterior_means[[parameter]] = apply(orl_posteriors[[parameter]], 2, mean)
}

overall_orl_posterior_means[["RewPun_ratio"]] =
  apply(log(apply(orl_posteriors$Arew, c(1,2), mean)/apply(orl_posteriors$Apun, c(1,2), mean)), 2, mean)


session_orl_posterior_means = list()

for(parameter in person_parameters){
  session_orl_posterior_means[[parameter]] = apply(orl_posteriors[[parameter]], c(2,3), mean)
}

session_orl_posterior_means[["RewPun_ratio"]] =
  matrix(c(apply(log(orl_posteriors$Arew[,,1]/orl_posteriors$Apun[,,1]), 2, mean),
         apply(log(orl_posteriors$Arew[,,2]/orl_posteriors$Apun[,,2]), 2, mean)),
         nrow = 49, ncol = 2, byrow = F)
```



```{r}
correlations = data.frame()

for(parameter in c(person_parameters,"RewPun_ratio")){
  for(scale in scales){
    for(s in 1:ncol(selfreport[[scale]]$score)){
        
      orl = session_orl_posterior_means[[parameter]][,s][selfreport[[scale]]$score[,s] != -999]
      sr = selfreport[[scale]]$score[,s][selfreport[[scale]]$score[,s] != -999]
      
        correlation = boot.cor.bca(x = orl,
                                   y = sr,
                                   null.hyp = NULL,
                                   alternative = c("two.sided", "less", "greater"),
                                   conf.level = 0.95, type = NULL, R = 9999)
        
        correlations = data.frame(parameter = parameter,
                                  scale = scale,
                                  type = "sum-score",
                                  session = s,
                                  r = correlation$Observed,
                                  CI = correlation$Confidence.interval) %>%
          bind_rows(correlations)
    }
  }
}
correlations %>% 
  separate(col = "CI", into = c("lower", "upper"), sep = ",") %>% 
  mutate(lower = as.numeric(str_remove(lower, "\\(")), upper = as.numeric(str_remove(upper, "\\)"))) %>% 
  write.csv(here("1_IGT_PP", "Figs_Tables", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
                 "session_orl_sr_correlations.csv"))

correlations = data.frame()

for(parameter in c(person_parameters,"RewPun_ratio")){
  for(scale in scales){
    orl = overall_orl_posterior_means[[parameter]]
    
    temp_sr = selfreport[[scale]]
    temp_sr$score[temp_sr$score==-999] = NA
    sr = apply(temp_sr$score, 1, mean, na.rm = T)

      correlation = boot.cor.bca(x = orl,
                                 y = sr,
                                 null.hyp = NULL,
                                 alternative = c("two.sided", "less", "greater"),
                                 conf.level = 0.95, type = NULL, R = 9999)

      correlations = data.frame(parameter = parameter,
                                scale = scale,
                                type = "predicted score",
                                session = s,
                                r = correlation$Observed,
                                CI = correlation$Confidence.interval) %>%
        bind_rows(correlations)
  }
}
correlations %>% 
  separate(col = "CI", into = c("lower", "upper"), sep = ",") %>% 
  mutate(lower = as.numeric(str_remove(lower, "\\(")), upper = as.numeric(str_remove(upper, "\\)"))) %>% 
write.csv(here("1_IGT_PP", "Figs_Tables", "ORL_Joint_playfic_playupdate_modifiedK_simplified",
               "overall_orl_playfic_playupdate_modifiedK_simplified_sr_correlations.csv"))
```



```{r}
session_correlations = data.frame()

for(parameter in c(person_parameters,"RewPun_ratio")){
  for(scale in scales){
    for(s in 1:ncol(selfreport[[scale]]$score)){
        
        correlation = boot.cor.bca(x = session_orl_posterior_means[[parameter]][,s],
                                   y = selfreport[[scale]]$score[,s],
                                   null.hyp = NULL,
                                   alternative = c("two.sided", "less", "greater"),
                                   conf.level = 0.95, type = NULL, R = 9999)
        
        session_correlations = data.frame(parameter = parameter,
                                          scale = scale,
                                          type = "sum-score",
                                          session = s,
                                          r = correlation$Observed,
                                          CI = correlation$Confidence.interval) %>%
          bind_rows(session_correlations)
    }
  }
}
```



## Correlations B/w Arew & Apun
```{r}
overall_pcor = data.frame()
overall_Arew = apply(orl_posteriors$Arew, c(1,2), mean)
overall_Apun = apply(orl_posteriors$Apun, c(1,2), mean)
for(i in 1:iterations){
  overall_pcor = data.frame(r = cor(overall_Arew[i,], overall_Apun[i,])) %>% 
    bind_rows(overall_pcor)
}
session1_pcor = data.frame()
for(i in 1:iterations){
  session1_pcor = data.frame(r = cor(orl_posteriors$Arew[i,,1], orl_posteriors$Apun[i,,1])) %>% 
    bind_rows(session1_pcor)
}
session2_pcor = data.frame()
for(i in 1:iterations){
  session2_pcor = data.frame(r = cor(orl_posteriors$Arew[i,,2], orl_posteriors$Apun[i,,2])) %>% 
    bind_rows(session2_pcor)
}

hist(overall_pcor$r, main = paste0("overall: r = ", round(mean(overall_pcor$r),2)))
abline(v = mean(overall_pcor$r))
hist(session1_pcor$r, main = paste0("overall: r = ", round(mean(session1_pcor$r),2)))
abline(v =mean(session1_pcor$r))
hist(session2_pcor$r, main = paste0("overall: r = ", round(mean(session2_pcor$r),2)))
abline(v =mean(session2_pcor$r))

HDIofMCMC(overall_pcor$r)
HDIofMCMC(session1_pcor$r)
HDIofMCMC(session2_pcor$r)
```



## Relations to Behavior
### Calculate Choice Proportions
```{r}
choice = ifelse(stan_data$choice == 1, 1, ifelse(stan_data$choice == 2, 0, NA))

card_proportions = array(data = NA, dim = c(49, 4, 2))
good_proportions = matrix(data = NA, nrow = 49, ncol = 2)
play_proportions = matrix(data = NA, nrow = 49, ncol = 2)

for(i in 1:49){
  for(s in 1:2){
    good_proportions[i,s] = mean(choice[i,,s][stan_data$card[i,,s] == 3 | stan_data$card[i,,s] == 4], na.rm = T)
    play_proportions[i,s] = mean(choice[i,,s] == 1, na.rm = T)
    for(c in 1:4){
      card_proportions[i,c,s] = mean(choice[i,,s][stan_data$card[i,,s] == c], na.rm = T)
    }
  }
}
```



### Correlations w/Card Proportions
```{r}
for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
    print(paste(" ", parameter))
    for(c in 1:4){
      card = ifelse(c == 1, "    Net = -750, Win Freq = 15, Lose Freq = 15",
                    ifelse(c == 2, "    Net = -750, Win Freq = 27, Lose Freq = 3",
                           ifelse(c == 3, "    Net = +600, Win Freq = 15, Lose Freq = 6",
                                  "    Net = +750, Win Freq = 27, Lose Freq = 3")))
      print(paste(card, ": r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], card_proportions[,c,s],
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
    }
  }
}
```



### Correlations w/Good Proportions
```{r}
for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
      print(paste("  ", parameter, " vs Proportion Good Cards: r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], good_proportions[,s],
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
  }
}
```



### Correlations w/Play Proportions
```{r}
for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
      print(paste("  ", parameter, " vs Proportion Played: r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], abs(play_proportions[,s]-.5),
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
  }
}
```



### Correlations w/Net Gain
```{r}
net_gains = apply(stan_data$outcome, c(1,3), sum)

for(s in 1:2){
  print(paste("Session", s))
  for(parameter in person_parameters){
      print(paste("  ", parameter, " vs Net Gain: r = ",
                  round(cor(session_orl_posterior_means[[parameter]][,s], net_gains[,s],
                            use = "pairwise.complete.obs"), 2),
                  sep = ""))
  }
}
print("Change in Gain")
for(parameter in person_parameters){
    print(paste("  ", parameter, " vs Delta Net Gain: r = ",
                round(cor(apply(orl_posteriors[[parameter]], 2, mean), (net_gains[,2]-net_gains[,1]),
                          use = "pairwise.complete.obs"), 2),
                sep = ""))
}
```



# -------------------------------------------



















